### 2023-10-09 Paper/latex/paper.tex
Create the latex version of the paper.

%%
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
%%
%% For submission and review of your manuscript please change the
%% command to \documentclass[manuscript, screen, review]{acmart}.
%%
%% When submitting camera ready or to TAPS, please change the command
%% to \documentclass[sigconf]{acmart} or whichever template is required
%% for your publication.
%%
%%
\documentclass[sigconf,screen,review,anonymous]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{XXXXXXX.XXXXXXX}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Conference acronym 'XX]{Make sure to enter the correct
  conference title from your rights confirmation emai}{June 03--05,
  2018}{Woodstock, NY}
%%
%%  Uncomment \acmBooktitle if the title of the proceedings is different
%%  from ``Proceedings of ...''!
%%
\acmBooktitle{Proceedings of the 32nd ACM Symposium on the Foundations of Software Engineering (FSE '24), November 15--19, 2024, Porto de Galinhas, Brazil}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% For managing citations, it is recommended to use bibliography
%% files in BibTeX format.
%%
%% You can then either use BibTeX with the ACM-Reference-Format style,
%% or BibLaTeX with the acmnumeric or acmauthoryear sytles, that include
%% support for advanced citation of software artefact from the
%% biblatex-software package, also separately available on CTAN.
%%
%% Look at the sample-*-biblatex.tex files for templates showcasing
%% the biblatex styles.
%%

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{RAX: A porting complexity evaluation tool for RISC-V}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ben Trovato}
\authornote{Both authors contributed equally to this research.}
\email{trovato@corporation.com}
\orcid{1234-5678-9012}
\author{G.K.M. Tobin}
\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin}
  \state{Ohio}
  \country{USA}
  \postcode{43017-6221}
}

\author{Lars Th{\o}rv{\"a}ld}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{larst@affiliation.org}

\author{Valerie B\'eranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}

\author{Aparna Patel}
\affiliation{%
 \institution{Rajiv Gandhi University}
 \streetaddress{Rono-Hills}
 \city{Doimukh}
 \state{Arunachal Pradesh}
 \country{India}}

\author{Huifen Chan}
\affiliation{%
  \institution{Tsinghua University}
  \streetaddress{30 Shuangqing Rd}
  \city{Haidian Qu}
  \state{Beijing Shi}
  \country{China}}

\author{Charles Palmer}
\affiliation{%
  \institution{Palmer Research Laboratories}
  \streetaddress{8600 Datapoint Drive}
  \city{San Antonio}
  \state{Texas}
  \country{USA}
  \postcode{78229}}
\email{cpalmer@prl.com}

\author{John Smith}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{jsmith@affiliation.org}

\author{Julius P. Kumquat}
\affiliation{%
  \institution{The Kumquat Consortium}
  \city{New York}
  \country{USA}}
\email{jpkumquat@consortium.net}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
In recent years, RISC-V instruction set architecture(ISA) has attracted the attention of the information technology industry due to its open source, modular design, and simplicity.
However, there is a lack of standardized metrics and methods to measure software architecture portability, which helps to establish a mature software ecosystem in RISC-V.
A theoretical framework is urgently needed as a guide to summarize important porting-related factors and design an automated RISC-V-oriented porting complexity evaluation tool to solve the problem.
We propose RAX, it will help recommend software with varying degrees of porting complexity to development teams.
RAX first retrieves porting modification information of the adapted project according to the Git version control tool, classifies it through manual analysis, and selects the most important porting factors to design the code positioning mode.
Additionally, it incorporates Cyclomatic Complexity, which is from code evaluation domain, to enhance assessment accuracy and measure the overall complexity of the software.
We establish a high-quality data set of software porting complexity, and select random forest machine learning model as the final classifier through multi-model comparison.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>00000000.0000000.0000000</concept_id>
  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>00000000.00000000.00000000</concept_id>
  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>00000000.00000000.00000000</concept_id>
  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>00000000.00000000.00000000</concept_id>
  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
\ccsdesc[300]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
\ccsdesc{Do Not Use This Code~Generate the Correct Terms for Your Paper}
\ccsdesc[100]{Do Not Use This Code~Generate the Correct Terms for Your Paper}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Do, Not, Us, This, Code, Put, the, Correct, Terms, for,
  Your, Paper}
%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
%% \begin{teaserfigure}
%%  \includegraphics[width=\textwidth]{sampleteaser}
%%  \caption{Seattle Mariners at Spring Training, 2010.}
%%  \Description{Enjoying the baseball game from the third-base
%%  seats. Ichiro Suzuki preparing to bat.}
%%  \label{fig:teaser}
%% \end{teaserfigure}

%% \received{20 February 2007}
%% \received[revised]{12 March 2009}
%% \received[accepted]{5 June 2009}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
RISC-V is an emerging open-source and reduced ISA which avoids potential risks such as intellectual property issues.
Compared to traditional architectures, RISC-V has a simpler design, which lowers R\&D threshold.
Its modularization and scalability allows developers to customize the architecture flexibly to adapt to different application scenarios.

Although RISC-V has already made initial progress in having a relatively complete tool chain, it still requires the support of a large number of application software.
However, establishing a mature software ecosystem still face challenges.
Currently, there is a lack of standardized metrics to measure software architecture portability,and porting planning relies on domain expertise.
Du Jiman et al. have developed a basic statistical evaluation plan for CPU architecture code in project,however,their work lacks a thorough validity analysis and comparison of factors,and fails to consider the complexity associated with the software operation and maintenance process.
It is difficult for developers to estimate the complexity of the porting project and accurately allocate the necessary resources,and there are also challenges related to variations in task difficulty and developer proficiency.
In order to solve this problem,one of the methods is to make analogies with adapted projects to gain porting experience,but it is difficult to extract factors by manual sorting;Even if developers have sensitivity to architecture-related modules, it is still challenging to accurately obtain the workload.
RAX can provide developers with accurate evaluation, recommend software with different levels of porting difficulty based on their skill levels.
The contributions of this paper are as follows:
\begin{enumerate}
  \item Firstly, we conducted analysis on selection of factors related the porting evaluation.
  We analyzed the modified content obtained from the Git Commit tool, selecting important factors that are suitable for automatic detection and collection.
  Simultaneously,we investigated the significance of code complexity metrics in the context of porting work and incorporated Cyclomatic Complexity as a factor to assess the overall complexity of  the project.
  \item We implemented RAX porting complexity evaluation tool.
  Projects were obtained from openEuler and GitHub.
  Based on porting-related factors, we designed a scanning tool to collect porting complexity vectors.
  Through a comprehensive evaluation method,we established a high-quality data set and ultimately selected random forest machine learning model as the classifier for RAX.
  \item Evaluate the effectiveness of RAX.
  We expanded the dataset by nearly double and verified the effectiveness of 100 expanded projects through their respective communities or forums.
  We received 50 responses, out of which 30 were considered valid responses.
  In comparison to Du Jiman's tool,RAX demonstrated  improvements.
\end{enumerate}

\section{RAX}
The following is an introduction to the process of RAX construction.
During the analysis phase,architecture-related factors are obtained through the Commit tool for selection.
A scanning tool is built to get potential modification workload.
Finally,an appropriate machine learning model is selected as a classification.

\subsection{Motivation}
The section provides a validity analysis of porting-related factors on RAX.
First,we use code complexity metrics to evaluate porting work.
The software metrics of code Cyclomatic Complexity(CC) can help developers make macro judgments on software complexity and maintenance difficulty, evaluate potential and hidden porting difficulties, and help the tool improve accuracy.
At present, CC indicators are mostly used in project code quality assessment, defect inspection, code reconstruction, etc.
During the porting process, developers will target a large number of project source codes, scripts, assembly codes,and a macro understanding of the project is required in the early stage of porting.
This part of the work has a lot of overlap with the scope of code complexity.

\subsubsection{Factor 1: Cyclomatic Complex(CC)}
RAX tool uses the lizard CC detection tool and optimize its functions,we will introduce it in section 2.3.
This study analyzes the relationship between CC and software porting complexity using the Spearman Rank correlation coefficient analysis method.
We invited five Master's students who are engaged in research on porting auxiliary tools to score the porting complexity(score) of 131 software adapted for RISC-V,collected from the OpenEule list and GitHub.
According to the collection of Internet events, log analysis, source code dismantling, and similar project analogy,we form a scoring interval in the range of $[0~5]$.
We then calculated the Spearman correlation coefficient and conducted significance analysis between score and the CC factors.
The Spearman coefficient is 0.608, with a P-value of 1.39e-14, which is less than 0.01.
This indicates a significant correlation between the two variables.
The results suggest that CC has a moderate positive correlation with porting difficulty.
This is because developers need a holistic understanding of the project during the porting process, and CC can represent the overall complexity of the project, potentially reflecting porting barriers, as the picture shows:
Secondly,we focus on the code associated with architecture in the project,with the goal of predicting porting workload through these code.

\subsubsection{Factor2:Arch\_code}

First, extract all possible architecture-related factors.
Use the Git tool to split Commit into different files using git-diff and filter out the surrounding 20 lines of content containing architecture keywords for detailed analysis of the modifications.
The manually analyzed Commit generally includes the following parts: first, functional supplements, including lack of dependent package calls, performance optimization and test cases for architecture porting;second, detail adjustments for data type and Build script;finally, key function implementation, assembly code, built-in function, system call, etc.
Among these factors, we select more objective ones that can be automatically located through regular expression matching.

Arch\_code defines assembly code, conditional compilation and macro structure, Intrinsic functions, Builtin functions, architecture-related build scripts, and system calls.
We use an automated architecture binding code scanning module to obtain statistics on the number of lines and frequencies of Arch\_code.

Continue to collect other factors that may affect the evaluation of porting complexity,and select the following parameters through the Commit analyzer:architecture-related code lines, architecture-related files, and architecture keywords.
The number of architecture-related code lines and files is located using the keywords of X86, ARM, MIPS, RISCV, SPARC and other architectures.
Correlation comparison between Arch\_code and other factors acquired by Commit analyzer,as the picture shows:

The results indicate that Arch\_code has a higher correlation with score compared to other factors, and it also aligns with the significant results of the Spearman correlation test.
The use of only architecture keywords for statistics yields moderate effectiveness in evaluating tool because keywords can only be detected from comments and macro sections of Commit, while critical porting code may lack these keywords,but the keyword count can reflect the amount of porting modification from the side.
As shown in the figure 2, there may be great ambiguity in keyword positioning using different architectures.
So we only selected x86 for positioning, which represents the most fair workload.
In the end, the parameters of Arch\_code show a correlation of 0.43 to 0.75 with score, indicating a strong relationship.
However, using a single factor alone does not result in a significantly strong correlation, as the combined modifications of these factors make up the porting workload.

To design RAX that assists developers with porting work,the following research questions are proposed:

\textbf{Research Question 1:} Developers often struggle to make fine-grained differentiations in the complexity of porting projects.
How can we select architecture-relevant factors to design an automated tool that assesses the porting difficulty?
We analyzes the porting modifications obtained from developer Commit in the Git tool.
We conducts an effectiveness analysis of the selected factors and filters out strongly correlated ones that can be automatically identified using the Lines of Code (LOC) approach.
Additionally, we propose a CC assessment method to jointly establish a data set for porting complexity.

\textbf{Research question 2:} How to select a classifier to obtain effective classification results for the tool?
Using the processing method of unbalanced datasets, multiple machine learning models are compared to select the final classifier.

\subsection{Dateset}
We used the project upstream warehouse to build the data set,that projects are from the OpenEuler:Stage2 list and GitHub, and invited 5 postgraduate students who are engaged in the research of RISC-V porting auxiliary tools to participate in the experimental evaluation.
Specific evaluation methods include: collecting event information of architecture porting through the Internet;log analysis;manually dismantling architecture-related codes;analogy with similar projects.
The evaluation scores are divided into three categories: low, medium, and high.
Higher score requires more development time, more experienced porting developers, and more precise strategy.
In the end, RAX collected a total of 134 projects.

\subsection{Method}
The RAX combines the CC calculation module and the Arch\_code location module to obtain the porting vector,and the complexity vector and score together form the data set.

\subsection{Lizard CC calculation module}
Lizard's default computing method is basically consistent with McCabe's theory.
However, Lizard tool only detects defects at the function level and uses the average function CC for file-level statistics, which is not suitable for current porting complexity detection requirements.
This paper proposes a new method for evaluating CC specifically for porting assessment work:
\begin{enumerate}
  \item First, calculate the function-level CC for all files in the project using McCabe's method.
  \item Following Liu Huihui's mention of System Cyclomatic Complexity (SCC) in software evolution assessment techniques based on code change detection, we define SCC as the total sum of function-level values in the system.
  The advantage is that it can avoid the use of overly complex methods, which will cause deviations to affect the classification results.
  Additionally, it eliminates the problem of decreased detection performance caused by program transformation into syntax abstract trees and control flow graphs.
\end{enumerate}

\subsection{Arch\_code location module}
we form the Arch\_code dictionary:
\begin{enumerate}
  \item Conditional compilation and architecture macros are used as preprocessor macros to enable projects to select execution on different hardware architectures, thus demonstrating the additional workload of architecture porting.
  Use conditional compilation statements, such as ``if defined'', ``ifdef'', in conjunction with all possible architectur macros,``\_\_x86\_64\_\_''.
  We use a similar bracket matching algorithm to cover all the code within macros, avoiding the impact of nested layers.
  Additionally, we only collect the keyword dictionary for x86 architecture.
  This is because different architectures may reflect varying workloads and difficulties, while considering that multiple architectures blurs the classification performance in practical work.
  \item Assembly code Leverages the advantages of architecture-specific instructions to enhance performance.
  Considering that architecture changes inevitably require consideration of the assembly section, we use matching forms such as ``\_\_asm\_\_'' and ``\_\_volatile\_\_''.
  In future work,we will consider striving to achieve the currently unachievable architecture identification function of assembly code and identify assembly code in the form of instructions;In actual work, the assembly code of different architectures may represent different levels of difficulty.
  For example, the assembly code of ARM is relatively simple.
  At the same time,there are also situations where some assembly codes only need to serve a specific architecture and do not need to be fully modified when porting to RISC-V.
  This is why we cannot achieve Fine-grained evaluation,we simply count the number of lines.
  \item Intrinsic functions are interfaces provided by compilers that are closely related to the architecture.
  Calling Intrinsic functions can replace assembly code.
  We compile dictionaries of Intrinsic functions based on official documentation from X86[2].
  Builtin function also employ a similar approach;In the future,we may assign difficulty weights to them.
  Currently,we only perform frequency statistics on them.
  Additionally,we will continue to supplement the analysis of whether the functions already have corresponding implementation for RISC-V and whether they are truly needed in RISC-V.
  \item System calls are encapsulated by the operating system kernel to provide hardware calling.
  Considering glibc's support for system call encapsulation, reorganize the sys-call dictionary.
  The system calls that do not support RISC-V have been filtered out currently.
  \item In the porting process, adjustment of build scripts is necessary to ensure smooth compilation.
  We locate architecture keywords in the build scripts.
  In the future, architecture-related factors will consider even finer-grained classification.
  For instance,considering the impact of existing porting auxiliary tools, including intrinsic translation tools and assembly translation tools,on porting complexity assessment.
\end{enumerate}

\section{Result and analysis}

To answer research question 2, based on the work of Chen Xiang et al. [24], aiming at the status quo of unbalanced datasets and small sample datasets, we try to use ensemble learning methods, SMOTE [25],and random oversampling methods for data preprocessing.
Ultimately, we chose to train four models: Random Forest, Support Vector Machine, Adaboost, and Xgboost.
The experimental evaluation involved a cross-comparison of the aforementioned models based on metrics such as accuracy, macro-precision (Pmacro), macro-recall (Rmacro), and macro F1 score (F1macro).
Through the multi-model comparison, we select the Random Forest machine learning as the classifier.

We continued to expand 100 projects as a supplementary data set, of which 87 were able to predict correctly.
The prediction results were determined through comments from the community and forums.
Appendix presents a comparative assessment of the porting complexity evaluation tool developed by Du Jiman et al. across various projects.

After adding the code complexity factor and modifying the original tool design model, RAX's result prediction accuracy is improved.
This is because code complexity can effectively distinguish projects with low porting difficulty from projects with medium and high porting difficulty.
Motivation Chapters present the cause analysis.
Adding factors also makes RAX more robust and more friendly to projects with unbalanced complexity vectors.
For example, kernel-level projects, boot layers, hardware drivers and other projects may involve a large amount of assembly code,corresponding to larger porting complexity,but other factors of the original tool design are at low values,which is not conducive to distinguishing complexity.
Chibios,u-boot are facing such a situation.
Within this assessment, there are instances of inaccurate predictions.
An analysis of these discrepancies reveals that certain projects themselves are of substantial complexity,containing a significant amount of architecture-related code defined by Arch\_code.
However,in the actual porting process, there is support from various porting auxiliary tools as well as dependency packages adapted RISC-V,like the assembly code used for acceleration in the portmidi project has a simple C- equivalent available.
As a result,the expert assessors did not assign high difficulty scores to these projects.
At the same time,it is also due to the existence of a situation where the project is large but there is less Arch\_code,and adding CC cannot avoid it,like cgal project.
Sometimes developers design their work has generic code for unknown architecture and CPU architecture parts are well separated from the common code,that just need only to adjust the macro to recognize RISC-V,like nuttx.

\section{Related Work}
The development of the RISC-V ecosystem is rapidly progressing.
In the realm of scientific computing, Tine Blaise et al. [9] accomplished the porting of the OpenCL framework to RISC-V through a compiler framework, thereby expanding RISC-V's accessibility to a wider range of scientific computing applications.
In the context of architectural migration of foundational software and libraries, Cheng Yuanhu et al. [3] designed an embedded multi-instruction set processor,addressing the software ecosystem challenges present in the RISC-V embedded domain.
As a result, auxiliary efforts in porting are highlighted as valuable endeavors.
This tool approaches code complexity from the perspective of its evaluation role in software evolution and maintenance,considering its influence on porting complexity assessment.
Alvares et al. [11] proposed using the development team's "tolerance" for code complexity to infer team development capabilities and performance indicators for projects.
Vard et al. [12] emphasized that the internal quality of software impacts developers' capabilities and maintenance durations.
They conducted a comprehensive study on various existing code complexity metrics' validity and suggested incorporating empirically observed code features as complexity triggers.

\section{Conclusion}
We propose RAX, with the aim of recommending projects of varying porting difficulties to developers.
We incorporate the code complexity to reflect developers' actual workload.
Additionally, we conduct a correlation analysis of Arch\_code; Analyze the defects and improvements of factor statistical methods, and finally build a scanning tool.
Using a Random Forest machine learning model, we perform classification learning on 234 projects collected from the OpenEuler:Stage2 list and GitHub.
When compared to the previous version of the tool, our approach yields improved predictive performance.
Moreover, RAX provides developers with the functionality to locate target code segments.
Our next steps involve attempting text classification methods to categorize the text results of the scanning tool, designing more granular statistical methods for architecture-related factors.

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
% \bibliographystyle{ACM-Reference-Format}
% \bibliography{sample-base}

\end{document}

### 2023-10-09 Paper/latex/paper.tex
Add figures.

@@
 \section{RAX}
-The following is an introduction to the process of RAX construction.
+The following is an introduction to the process of RAX construction, as shown in Figure \ref{fig:flow-chart}.
 During the analysis phase,architecture-related factors are obtained through the Commit tool for selection.
@@
 Finally,an appropriate machine learning model is selected as a classification.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\linewidth]{flow-chart.pdf}
+  \caption{Flow chart for method to build RAX}
+  \label{fig:flow-chart}
+  \Description{Flow chart for method to build RAX}
+\end{figure}
 
@@
 The results suggest that CC has a moderate positive correlation with porting difficulty.
-This is because developers need a holistic understanding of the project during the porting process, and CC can represent the overall complexity of the project, potentially reflecting porting barriers, as the picture shows:
+This is because developers need a holistic understanding of the project during the porting process, and CC can represent the overall complexity of the project, potentially reflecting porting barriers, as shown in Figure \ref{fig:relationship}.
 Secondly,we focus on the code associated with architecture in the project,with the goal of predicting porting workload through these code.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\linewidth]{relationship.pdf}
+  \caption{The relationship between score and CC}
+  \label{fig:relationship}
+  \Description{The relationship between score and CC}
+\end{figure}
 
@@
 This tool approaches code complexity from the perspective of its evaluation role in software evolution and maintenance,considering its influence on porting complexity assessment.
-Alvares et al. [11] proposed using the development team's "tolerance" for code complexity to infer team development capabilities and performance indicators for projects.
+Alvares et al. [11] proposed using the development team's ``tolerance'' for code complexity to infer team development capabilities and performance indicators for projects.
 Vard et al. [12] emphasized that the internal quality of software impacts developers' capabilities and maintenance durations.

### 2023-10-09 Paper/latex/paper.tex
Add tables.

@@
 \documentclass[sigconf,screen,review,anonymous]{acmart}
+
+\usepackage{multirow}
 
@@
 
-\begin{figure}[h]
+\begin{figure}
   \centering
@@
 The number of architecture-related code lines and files is located using the keywords of X86, ARM, MIPS, RISCV, SPARC and other architectures.
-Correlation comparison between Arch\_code and other factors acquired by Commit analyzer,as the picture shows:
+Correlation comparison between Arch\_code and other factors acquired by Commit analyzer,as shown in Table \ref{tab:score}:
+
+\begin{table*}
+  \caption{The Spearman correlation coefficient of score and architecture-related factors}
+  \label{tab:score}
+  \begin{tabular}{cccccc}
+    \toprule
+    conditional compilation & Builtin & Intrinstic & syscall & asm & build\_scripts \\
+    \midrule
+    0.73 & 0.61 & 0.74 & 0.69 & 0.66 & 0.43 \\
+  \bottomrule
+\end{tabular}
+\begin{tabular}{ccccc}
+  \toprule
+  time & authors & lines of arch & files of arch & keyword count \\
+  \midrule
+  -0.16 & 0.43 & 0.16-0.40 & 0.34-0.41 & 0.17-0.43 \\
+\bottomrule
+\end{tabular}
+\end{table*}
 
@@
 
+\begin{table}
+  \caption{The Spearman correlation coefficient of score and architecture-related factors}
+  \label{tab:evaluation}
+  \begin{tabular}{ccccc}
+    \toprule
+     & Accuracy & Pmacro & Rmacro & F1macro \\
+    \midrule
+    Tool 1[26] & 0.838 & 0.802 & 0.880 & 0.823 \\
+    RAX & 0.857 & 0.817 & 0.873 & 0.836 \\
+  \bottomrule
+\end{tabular}
+\end{table}
+
 We continued to expand 100 projects as a supplementary data set, of which 87 were able to predict correctly.
@@
 Appendix presents a comparative assessment of the porting complexity evaluation tool developed by Du Jiman et al. across various projects.
+
+\begin{table}
+  \caption{Effectiveness comparison chart}
+  \label{tab:effectiveness}
+  \begin{tabular}{ccccc}
+    \toprule
+     & \multicolumn{2}{c}{Tool 1} & \multicolumn{2}{c}{RAX} \\
+     & TP & FN & TP & FN \\
+    \midrule
+    Low & 13 & 3 & 15 & 1 \\
+    Medium & 5 & 2 & 5 & 2 \\
+    High & 3 & 4 & 7 & 0 \\
+    Sum & 21 & 9 & 27 & 3 \\
+    project & \multicolumn{2}{c}{30} & \multicolumn{2}{c}{30} \\
+  \bottomrule
+\end{tabular}
+\end{table}
 

### 2023-10-10 Paper/latex/paper.tex
Update references.

@@
 %%
-\documentclass[sigconf,screen,review,anonymous]{acmart}
+\documentclass[sigconf,screen,review]{acmart}
 
@@
 %% used to denote shared contribution to the research.
-\author{Ben Trovato}
-\authornote{Both authors contributed equally to this research.}
-\email{trovato@corporation.com}
-\orcid{1234-5678-9012}
-\author{G.K.M. Tobin}
-\authornotemark[1]
-\email{webmaster@marysville-ohio.com}
+\author{Yuxuan Wang}
+\email{wangyuxuan22@otcaix.iscas.ac.cn}
 \affiliation{%
-  \institution{Institute for Clarity in Documentation}
-  \streetaddress{P.O. Box 1212}
-  \city{Dublin}
-  \state{Ohio}
-  \country{USA}
-  \postcode{43017-6221}
+  \institution{Institute of Software, Chinese Academy of Sciences}
+  \city{Haidian}
+  \state{Beijing}
+  \country{China}
 }
-
-\author{Lars Th{\o}rv{\"a}ld}
-\affiliation{%
-  \institution{The Th{\o}rv{\"a}ld Group}
-  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
-  \city{Hekla}
-  \country{Iceland}}
-\email{larst@affiliation.org}
-
-\author{Valerie B\'eranger}
-\affiliation{%
-  \institution{Inria Paris-Rocquencourt}
-  \city{Rocquencourt}
-  \country{France}
-}
-
-\author{Aparna Patel}
-\affiliation{%
- \institution{Rajiv Gandhi University}
- \streetaddress{Rono-Hills}
- \city{Doimukh}
- \state{Arunachal Pradesh}
- \country{India}}
-
-\author{Huifen Chan}
-\affiliation{%
-  \institution{Tsinghua University}
-  \streetaddress{30 Shuangqing Rd}
-  \city{Haidian Qu}
-  \state{Beijing Shi}
-  \country{China}}
-
-\author{Charles Palmer}
-\affiliation{%
-  \institution{Palmer Research Laboratories}
-  \streetaddress{8600 Datapoint Drive}
-  \city{San Antonio}
-  \state{Texas}
-  \country{USA}
-  \postcode{78229}}
-\email{cpalmer@prl.com}
-
-\author{John Smith}
-\affiliation{%
-  \institution{The Th{\o}rv{\"a}ld Group}
-  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
-  \city{Hekla}
-  \country{Iceland}}
-\email{jsmith@affiliation.org}
-
-\author{Julius P. Kumquat}
-\affiliation{%
-  \institution{The Kumquat Consortium}
-  \city{New York}
-  \country{USA}}
-\email{jpkumquat@consortium.net}
 
@@
 %% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Trovato et al.}
+\renewcommand{\shortauthors}{Yuxuan et al.}
 
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{Do, Not, Us, This, Code, Put, the, Correct, Terms, for,
-  Your, Paper}
+\keywords{ISA(Instruction set architecture), RISC-V, Porting Complexity Evaluation}
+
 %% A "teaser" image appears between the author and affiliation
@@
 \section{Introduction}
-RISC-V is an emerging open-source and reduced ISA which avoids potential risks such as intellectual property issues.
+RISC-V is an emerging open-source and reduced ISA which avoids potential risks such as intellectual property issues \cite{2014The}.
 Compared to traditional architectures, RISC-V has a simpler design, which lowers R\&D threshold.
-Its modularization and scalability allows developers to customize the architecture flexibly to adapt to different application scenarios.
+Its modularization and scalability allows developers to customize the architecture flexibly to adapt to different application scenarios \cite{osti_1560132}.
 
-Although RISC-V has already made initial progress in having a relatively complete tool chain, it still requires the support of a large number of application software.
+Although RISC-V has already made initial progress in having a relatively complete tool chain, it still requires the support of a large number of application software \cite{2019Notary}.
 However, establishing a mature software ecosystem still face challenges.
@@
 Du Jiman et al.
-have developed a basic statistical evaluation plan for CPU architecture code in project,however,their work lacks a thorough validity analysis and comparison of factors,and fails to consider the complexity associated with the software operation and maintenance process.
+have developed a basic statistical evaluation plan for CPU architecture code in project \cite{2023du}, however, their work lacks a thorough validity analysis and comparison of factors,and fails to consider the complexity associated with the software operation and maintenance process.
 It is difficult for developers to estimate the complexity of the porting project and accurately allocate the necessary resources,and there are also challenges related to variations in task difficulty and developer proficiency.
@@
 \begin{enumerate}
-  \item Firstly, we conducted analysis on selection of factors related the porting evaluation.
-  We analyzed the modified content obtained from the Git Commit tool, selecting important factors that are suitable for automatic detection and collection.
-  Simultaneously,we investigated the significance of code complexity metrics in the context of porting work and incorporated Cyclomatic Complexity as a factor to assess the overall complexity of  the project.
-  \item We implemented RAX porting complexity evaluation tool.
-  Projects were obtained from openEuler and GitHub.
-  Based on porting-related factors, we designed a scanning tool to collect porting complexity vectors.
-  Through a comprehensive evaluation method,we established a high-quality data set and ultimately selected random forest machine learning model as the classifier for RAX.
+  \item Firstly, we conducted analysis on selection of factors related the porting evaluation,investigated the significance of code complexity metrics in the context of porting work and incorporated Cyclomatic Complexity as a factor to assess the overall complexity of  the project.
+  \item Based on porting-related factors, we designed a scanning tool to collect porting complexity vectors and ultimately selected random forest machine learning model as the classifier for RAX.
   \item Evaluate the effectiveness of RAX.
@@
 First,we use code complexity metrics to evaluate porting work.
-The software metrics of code Cyclomatic Complexity(CC) can help developers make macro judgments on software complexity and maintenance difficulty, evaluate potential and hidden porting difficulties, and help the tool improve accuracy.
-At present, CC indicators are mostly used in project code quality assessment, defect inspection, code reconstruction, etc.
+The software metrics of code Cyclomatic Complexity(CC) can help developers make macro judgments on software complexity and maintenance difficulty, evaluate potential and hidden porting difficulties, and help the tool improve accuracy \cite{2005Exploring}.
+At present, CC indicators are mostly used in project code quality assessment, defect inspection, code reconstruction, etc \cite{1991Cyclomatic}.
 During the porting process, developers will target a large number of project source codes, scripts, assembly codes,and a macro understanding of the project is required in the early stage of porting.
@@
 We invited five Master's students who are engaged in research on porting auxiliary tools to score the porting complexity(score) of 131 software adapted for RISC-V,collected from the OpenEule list and GitHub.
-According to the collection of Internet events, log analysis, source code dismantling, and similar project analogy,we form a scoring interval in the range of $[0~5]$.
+According to the collection of Internet events, log analysis, source code dismantling, and similar project analogy \cite{liangguanyu2020}, we form a scoring interval in the range of $[0~5]$.
 We then calculated the Spearman correlation coefficient and conducted significance analysis between score and the CC factors.
@@
 \subsection{Lizard CC calculation module}
-Lizard's default computing method is basically consistent with McCabe's theory.
-However, Lizard tool only detects defects at the function level and uses the average function CC for file-level statistics, which is not suitable for current porting complexity detection requirements.
+Lizard's default computing method is basically consistent with McCabe's theory \cite{1702388}.
+However, Lizard tool only detects defects at the function level and uses the average function CC for file-level statistics, which is not suitable for current porting complexity detection requirements \cite{9402593}.
 This paper proposes a new method for evaluating CC specifically for porting assessment work:
@@
   \item First, calculate the function-level CC for all files in the project using McCabe's method.
-  \item Following Liu Huihui's mention of System Cyclomatic Complexity (SCC) in software evolution assessment techniques based on code change detection, we define SCC as the total sum of function-level values in the system.
+  \item Following Liu Huihui's mention of System Cyclomatic Complexity (SCC) in software evolution assessment techniques based on code change detection \cite{liuhuihui00}, we define SCC as the total sum of function-level values in the system.
   The advantage is that it can avoid the use of overly complex methods, which will cause deviations to affect the classification results.
@@
 To answer research question 2, based on the work of Chen Xiang et al.
-[24], aiming at the status quo of unbalanced datasets and small sample datasets, we try to use ensemble learning methods, SMOTE [25],and random oversampling methods for data preprocessing.
+\cite{5128907}, aiming at the status quo of unbalanced datasets and small sample datasets, we try to use ensemble learning methods \cite{6509481}, SMOTE \cite{4271036}, and random oversampling methods for data preprocessing.
 Ultimately, we chose to train four models: Random Forest, Support Vector Machine, Adaboost, and Xgboost.
-The experimental evaluation involved a cross-comparison of the aforementioned models based on metrics such as accuracy, macro-precision (Pmacro), macro-recall (Rmacro), and macro F1 score (F1macro).
-Through the multi-model comparison, we select the Random Forest machine learning as the classifier.
+By comparing multiple indicators, we select the Random Forest machine learning as the classifier.
 
@@
 In the realm of scientific computing, Tine Blaise et al.
-[9] accomplished the porting of the OpenCL framework to RISC-V through a compiler framework, thereby expanding RISC-V's accessibility to a wider range of scientific computing applications.
+\cite{osti_1830102} accomplished the porting of the OpenCL framework to RISC-V through a compiler framework, thereby expanding RISC-V's accessibility to a wider range of scientific computing applications.
 In the context of architectural migration of foundational software and libraries, Cheng Yuanhu et al.
-[3] designed an embedded multi-instruction set processor,addressing the software ecosystem challenges present in the RISC-V embedded domain.
+\cite{2017Slow} designed an embedded multi-instruction set processor,addressing the software ecosystem challenges present in the RISC-V embedded domain.
 As a result, auxiliary efforts in porting are highlighted as valuable endeavors.
-This tool approaches code complexity from the perspective of its evaluation role in software evolution and maintenance,considering its influence on porting complexity assessment.
-Alvares et al. [11] proposed using the development team's ``tolerance'' for code complexity to infer team development capabilities and performance indicators for projects.
-Vard et al. [12] emphasized that the internal quality of software impacts developers' capabilities and maintenance durations.
+This tool approaches code complexity from the perspective of its evaluation role in software evolution and maintenance,considering its influence on porting complexity assessment \cite{1993Software}.
+Alvares et al. \cite{7844689} proposed using the development team's ``tolerance'' for code complexity to infer team development capabilities and performance indicators for projects.
+Vard et al. \cite{2017Evaluating} emphasized that the internal quality of software impacts developers' capabilities and maintenance durations.
 They conducted a comprehensive study on various existing code complexity metrics' validity and suggested incorporating empirically observed code features as complexity triggers.
@@
 %% the bibliography file.
-% \bibliographystyle{ACM-Reference-Format}
-% \bibliography{sample-base}
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{paper}
 

### 2023-10-12 Paper/latex/paper.tex
Replace figures.

@@
 \usepackage{multirow}
+\usepackage{svg}
+\usepackage{xcolor}
+
+\newcommand{\todo}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
 
@@
 \subsubsection{Factor 1: Cyclomatic Complex(CC)}
-RAX tool uses the lizard CC detection tool and optimize its functions,we will introduce it in section 2.3.
+\label{sec:factor-1}
+RAX tool uses the lizard CC detection tool and optimize its functions,we will introduce it in Section \ref{sec:method}.
 This study analyzes the relationship between CC and software porting complexity using the Spearman Rank correlation coefficient analysis method.
@@
 \subsection{Dateset}
-We used the project upstream warehouse to build the data set,that projects are from the OpenEuler:Stage2 list and GitHub, and invited 5 postgraduate students who are engaged in the research of RISC-V porting auxiliary tools to participate in the experimental evaluation.
-Specific evaluation methods include: collecting event information of architecture porting through the Internet;log analysis;manually dismantling architecture-related codes;analogy with similar projects.
+We used the project upstream warehouse to build the data set,that projects mainly targeting C and C++ are from the OpenEuler:Stage2 list and GitHub,and invited 5 postgraduate students who are engaged in the research of RISC-V porting auxiliary tools to participate in the experimental evaluation.
+Specific evaluation methods can be found in Section \ref{sec:factor-1}.
 The evaluation scores are divided into three categories: low, medium, and high.
-Higher score requires more development time, more experienced porting developers, and more precise strategy.
 In the end, RAX collected a total of 134 projects.
@@
 \subsection{Method}
+\label{sec:method}
 The RAX combines the CC calculation module and the Arch\_code location module to obtain the porting vector,and the complexity vector and score together form the data set.
@@
   Calling Intrinsic functions can replace assembly code.
-  We compile dictionaries of Intrinsic functions based on official documentation from X86[2].
+  We compile dictionaries of Intrinsic functions based on official documentation from X86\todo{[2]}.
   Builtin function also employ a similar approach;In the future,we may assign difficulty weights to them.
@@
     \midrule
-    Tool 1[26] & 0.838 & 0.802 & 0.880 & 0.823 \\
+    Tool 1\todo{[26]} & 0.838 & 0.802 & 0.880 & 0.823 \\
     RAX & 0.857 & 0.817 & 0.873 & 0.836 \\
@@
     \midrule
-    Low & 13 & 3 & 15 & 1 \\
+    Low & 15 & 3 & 17 & 1 \\
     Medium & 5 & 2 & 5 & 2 \\
     High & 3 & 4 & 7 & 0 \\
-    Sum & 21 & 9 & 27 & 3 \\
-    project & \multicolumn{2}{c}{30} & \multicolumn{2}{c}{30} \\
+    Sum & 23 & 9 & 29 & 3 \\
+    project & \multicolumn{2}{c}{32} & \multicolumn{2}{c}{32} \\
   \bottomrule

### 2023-10-12 Paper/latex/paper.tex
Update CCS and acknowledgments

@@
 %% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Conference acronym 'XX]{Make sure to enter the correct
-  conference title from your rights confirmation emai}{June 03--05,
-  2018}{Woodstock, NY}
+\acmConference[FSE '24]{The 32nd ACM Symposium on the Foundations of Software Engineering}{November 15--19, 2024}{Porto de Galinhas, Brazil}
 %%
@@
      <concept>
-  <concept_id>00000000.0000000.0000000</concept_id>
-  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
+         <concept_id>10011007.10011006.10011072</concept_id>
+         <concept_desc>Software and its engineering~Software libraries and repositories</concept_desc>
          <concept_significance>500</concept_significance>
@@
      <concept>
-  <concept_id>00000000.00000000.00000000</concept_id>
-  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
+         <concept_id>10011007.10011074.10011111</concept_id>
+         <concept_desc>Software and its engineering~Software post-development issues</concept_desc>
          <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>00000000.00000000.00000000</concept_id>
-  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>00000000.00000000.00000000</concept_id>
-  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
-  <concept_significance>100</concept_significance>
          </concept>
@@
 
-\ccsdesc[500]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
-\ccsdesc[300]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
-\ccsdesc{Do Not Use This Code~Generate the Correct Terms for Your Paper}
-\ccsdesc[100]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
+\ccsdesc[500]{Software and its engineering~Software libraries and repositories}
+\ccsdesc[300]{Software and its engineering~Software post-development issues}
 
@@
 \begin{acks}
-To Robert, for the bagels and explaining CMYK and color spaces.
+  This work was supported by Youth Innovation Promotion Association, Chinese Academy
+  of Sciences (Grant No. 2023118).
 \end{acks}

### 2023-10-12 Paper/latex/paper.tex
Update table and ack.

@@
 
-\begin{table*}
+\begin{table}
   \caption{The Spearman correlation coefficient of score and architecture-related factors}
   \label{tab:score}
-  \begin{tabular}{cccccc}
+  \begin{tabular}{cc}
     \toprule
-    conditional compilation & Builtin & Intrinstic & syscall & asm & build\_scripts \\
+    Type & Score \\
     \midrule
-    0.73 & 0.61 & 0.74 & 0.69 & 0.66 & 0.43 \\
+    conditional compilation & 0.73 \\
+    Builtin & 0.61 \\
+    Intrinstic & 0.74 \\
+    syscall & 0.69 \\
+    asm & 0.66 \\
+    build\_scripts & 0.43 \\
+    time & -0.16 \\
+    authors & 0.43 \\
+    lines of arch & 0.16-0.40 \\
+    files of arch & 0.34-0.41 \\
+    keyword count & 0.17-0.43 \\
     \bottomrule
   \end{tabular}
-\begin{tabular}{ccccc}
-  \toprule
-  time & authors & lines of arch & files of arch & keyword count \\
-  \midrule
-  -0.16 & 0.43 & 0.16-0.40 & 0.34-0.41 & 0.17-0.43 \\
-\bottomrule
-\end{tabular}
-\end{table*}
+\end{table}
 
@@
   Calling Intrinsic functions can replace assembly code.
-  We compile dictionaries of Intrinsic functions based on official documentation from X86\todo{[2]}.
+  We compile dictionaries of Intrinsic functions based on official documentation from x86.
   Builtin function also employ a similar approach;In the future,we may assign difficulty weights to them.
@@
     \midrule
-    Tool 1\todo{[26]} & 0.838 & 0.802 & 0.880 & 0.823 \\
+    Tool 1 & 0.838 & 0.802 & 0.880 & 0.823 \\
     RAX & 0.857 & 0.817 & 0.873 & 0.836 \\
@@
 \begin{acks}
-  This work was supported by Youth Innovation Promotion Association, Chinese Academy
-  of Sciences (Grant No. 2023118).
+  This work was supported by the Strategic Priority Research Program of the Chinese Academy of Sciences (Grant No.
+XDA0320102) and Youth Innovation Promotion Association, Chinese Academy of Sciences (Grant No.
+2023118).
 \end{acks}

### 2024-01-24 Paper/latex/paper.tex
update

@@
 %%
-\documentclass[sigconf,screen,review]{acmart}
+\documentclass[sigconf,screen,review,anonymous]{acmart}
 
@@
 \setcopyright{acmcopyright}
-\copyrightyear{2018}
-\acmYear{2018}
+\copyrightyear{2024}
+\acmYear{2024}
 \acmDOI{XXXXXXX.XXXXXXX}
@@
 \acmISBN{978-1-4503-XXXX-X/18/06}
+
+\settopmatter{printacmref=false}
+\renewcommand\footnotetextcopyrightpermission[1]{}
 
@@
 \section{Introduction}
-RISC-V is an emerging open-source and reduced ISA which avoids potential risks such as intellectual property issues \cite{2014The}.
-Compared to traditional architectures, RISC-V has a simpler design, which lowers R\&D threshold.
-Its modularization and scalability allows developers to customize the architecture flexibly to adapt to different application scenarios \cite{osti_1560132}.
+RISC-V is an emerging open-source and reduced ISA which avoids potential risks such as intellectual property issues\cite{2014The}.RISC-V provides an alternative to traditional commercial instruction set architectures.
+OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\cite{osti_1560133}; openEuler has joined RISC-V International, and RISC-V has officially become openEuler's official support architecture.The RISC-V SIG took the lead in completing the mainline integration of openEuler RISC-V 23.09\cite{osti_1560132}.
 
@@
 However, establishing a mature software ecosystem still face challenges.
-Currently, there is a lack of standardized metrics to measure software architecture portability,and porting planning relies on domain expertise.
+Currently, there is a lack of standardized metrics to measure software architecture portability,and porting planning relies on domain expertise.The difficulty in estimating porting work leads to challenges in accurately allocating resources;In the context of varying levels of developers' skills in porting, there is an even greater need to efficiently assess the difficulty of software package porting and provide guidance to developers of all kinds.In order to solve these problems,one of the methods is to make analogies with adapted projects to gain porting experience,but it is difficult to extract factors by manual sorting;Even if developers have sensitivity to architecture-related modules, it is still challenging to accurately obtain the workload.
 Du Jiman et al.
 have developed a basic statistical evaluation plan for CPU architecture code in project \cite{2023du}, however, their work lacks a thorough validity analysis and comparison of factors,and fails to consider the complexity associated with the software operation and maintenance process.
-It is difficult for developers to estimate the complexity of the porting project and accurately allocate the necessary resources,and there are also challenges related to variations in task difficulty and developer proficiency.
-In order to solve this problem,one of the methods is to make analogies with adapted projects to gain porting experience,but it is difficult to extract factors by manual sorting;Even if developers have sensitivity to architecture-related modules, it is still challenging to accurately obtain the workload.
+
 RAX can provide developers with accurate evaluation, recommend software with different levels of porting difficulty based on their skill levels.
@@
   \item Evaluate the effectiveness of RAX.
-  We expanded the dataset by nearly double and verified the effectiveness of 100 expanded projects through their respective communities or forums.
-  We received 50 responses, out of which 30 were considered valid responses.
-  In comparison to Du Jiman's tool,RAX demonstrated  improvements.
+  We nearly doubled the dataset compared to Du Jiman's tool,and verified the effectiveness of the evaluation of 100 extension projects in real porting scenarios through their respective communities or forums.
+We received 50 valid responses.Our findings indicate that RAX outperforms the Du Jiman's tool, delivering substantial improvements in terms of performance and accuracy..
 \end{enumerate}
@@
 The number of architecture-related code lines and files is located using the keywords of X86, ARM, MIPS, RISCV, SPARC and other architectures.
-Correlation comparison between Arch\_code and other factors acquired by Commit analyzer,as shown in Table \ref{tab:score}:
+%Correlation comparison between Arch\_code and other factors acquired by Commit analyzer,as shown in Table \ref{tab:score}:
 
-\begin{table}
-  \caption{The Spearman correlation coefficient of score and architecture-related factors}
-  \label{tab:score}
-  \begin{tabular}{cc}
-    \toprule
-    Type & Score \\
-    \midrule
-    conditional compilation & 0.73 \\
-    Builtin & 0.61 \\
-    Intrinstic & 0.74 \\
-    syscall & 0.69 \\
-    asm & 0.66 \\
-    build\_scripts & 0.43 \\
-    time & -0.16 \\
-    authors & 0.43 \\
-    lines of arch & 0.16-0.40 \\
-    files of arch & 0.34-0.41 \\
-    keyword count & 0.17-0.43 \\
-    \bottomrule
-  \end{tabular}
-\end{table}
+%\begin{table}
+ % \caption{The Spearman correlation coefficient of score and architecture-related factors}
+  %\label{tab:score}
+  %\begin{tabular}{cc}
+   % \toprule
+    %Type & Score \\
+    %\midrule
+    %conditional compilation & 0.73 \\
+    %Builtin & 0.61 \\
+    %Intrinstic & 0.74 \\
+    %syscall & 0.69 \\
+    %asm & 0.66 \\
+    %build\_scripts & 0.43 \\
+    %time & -0.16 \\
+    %authors & 0.43 \\
+    %lines of arch & 0.16-0.40 \\
+    %files of arch & 0.34-0.41 \\
+    %keyword count & 0.17-0.43 \\
+   % \bottomrule
+  %\end{tabular}
+%\end{table}
+Correlation comparison between Arch\_code and other factors acquired by Commit analyzer,as shown in Figure \ref{fig:correlation}:
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{correlation.pdf}
+  \caption{The Correlation}
+  \label{fig:correlation}
+  \Description{The Correlation}
+\end{figure}
 
@@
 
-\subsection{Dateset}
-We used the project upstream warehouse to build the data set,that projects mainly targeting C and C++ are from the OpenEuler:Stage2 list and GitHub,and invited 5 postgraduate students who are engaged in the research of RISC-V porting auxiliary tools to participate in the experimental evaluation.
-Specific evaluation methods can be found in Section \ref{sec:factor-1}.
-The evaluation scores are divided into three categories: low, medium, and high.
-In the end, RAX collected a total of 134 projects.
+\subsection{Dataset}
+We used the project upstream warehouse to build the data set,that projects mainly targeting C and C++ are from the OpenEuler\citep{stage2023} list and GitHub,and invited 5 postgraduate students who are engaged in the research of RISC-V porting auxiliary tools to participate in the experimental evaluation.Specific evaluation methods can be found in 2.1.1.
+The evaluation scores are divided into three categories: low, medium, and high\citep{githuburl}.This includes 139 projects as training, testing, and validation datasets, while more than 80 additional projects were used as a tool evaluation dataset.
+To gather insights from developers, the community, forums, and emails were utilized, resulting in over 50 meaningful feedback responses.
+In order to address the issue of data imbalance caused by collecting datasets solely from the openEuler mailing list, where more than 80\% of the projects were initially evaluated as having low porting complexity, a greater emphasis was placed on projects that had higher numbers of likes on GitHub and were deemed more important and active.
+Additionally, efforts were made to collect projects from the bottom such as operating systems, kernel-level projects,mathematical computation libraries,and machine learning libraries.
 
@@
 
-\subsection{Lizard CC calculation module}
+\subsubsection{Lizard CC calculation module}
 Lizard's default computing method is basically consistent with McCabe's theory \cite{1702388}.
@@
 
-\subsection{Arch\_code location module}
+\subsubsection{Arch\_code location module}
 we form the Arch\_code dictionary:
@@
 \begin{table}
-  \caption{The Spearman correlation coefficient of score and architecture-related factors}
+  \caption{ Experimental results of models}
   \label{tab:evaluation}
@@
     \midrule
-    Tool 1 & 0.838 & 0.802 & 0.880 & 0.823 \\
-    RAX & 0.857 & 0.817 & 0.873 & 0.836 \\
+    Adaboost & 0.786 & 0.594 & 0.775 & 0.650 \\
+    Random Forest & 0.857 & 0.817 & 0.873 & 0.836 \\
   \bottomrule
@@
 The prediction results were determined through comments from the community and forums.
-Appendix presents a comparative assessment of the porting complexity evaluation tool developed by Du Jiman et al. across various projects.
+Appendix presents a comparative assessment of the porting complexity evaluation tool developed by Du Jiman et al.
+across various projects.Through real-world evaluations within the developer community, our tool has exhibited a significant improvement in accuracy, surpassing other comparable tools by a margin of 14\%.
+In the appendix, we provide a comprehensive compilation of the community's valuable feedback comments, accompanied by the relevant web links for further reference and validation.
 
@@
     \toprule
-     & \multicolumn{2}{c}{Tool 1} & \multicolumn{2}{c}{RAX} \\
+    Porting Complexity & \multicolumn{2}{c}{Du's Tool} & \multicolumn{2}{c}{RAX} \\
      & TP & FN & TP & FN \\
     \midrule
-    Low & 15 & 3 & 17 & 1 \\
-    Medium & 5 & 2 & 5 & 2 \\
-    High & 3 & 4 & 7 & 0 \\
-    Sum & 23 & 9 & 29 & 3 \\
-    project & \multicolumn{2}{c}{32} & \multicolumn{2}{c}{32} \\
+    Low &31/36 & 5/36 & 34/36 & 2/36 \\
+    Medium & 5/8 & 3/8 & 6/8 & 2/8 \\
+    High & 3/6 & 3/6 & 6/6 & 0/6 \\
+    \midrule
+    Total & \textcolor{red}{39/50} & 11/50& \textcolor{red}{46/50} & 4/50 \\
       \bottomrule
@@
 Within this assessment, there are instances of inaccurate predictions.
-An analysis of these discrepancies reveals that certain projects themselves are of substantial complexity,containing a significant amount of architecture-related code defined by Arch\_code.
-However,in the actual porting process, there is support from various porting auxiliary tools as well as dependency packages adapted RISC-V,like the assembly code used for acceleration in the portmidi project has a simple C- equivalent available.
-As a result,the expert assessors did not assign high difficulty scores to these projects.
-At the same time,it is also due to the existence of a situation where the project is large but there is less Arch\_code,and adding CC cannot avoid it,like cgal project.
-Sometimes developers design their work has generic code for unknown architecture and CPU architecture parts are well separated from the common code,that just need only to adjust the macro to recognize RISC-V,like nuttx.
+
+In-depth analysis of these variations reveals that certain projects exhibit inherent complexity, entailing a substantial presence of architecture-specific code defined by Arch\_code.
+Nevertheless, the practical porting process benefits from an array of auxiliary tools designed to support developers.
+In response to valuable suggestions from developers within the OpenEuler community, we conducted an evaluation of the porting difficulty for various versions of the Chromium.Initially, we were able to accurately assess the porting difficulty, yielding promising results.
+However, when it came to evaluating the work involved in iterative updates between versions, existing tools proved insufficient for precise estimation.Sometimes developers design their work has generic code for unknown architecture and CPU architecture parts are well separated from the common code,that just need only to adjust the macro to recognize RISC-V,like nuttx.
 

### 2024-01-25 Paper/latex/paper.tex
update

@@
 \section{Introduction}
-RISC-V is an emerging open-source and reduced ISA which avoids potential risks such as intellectual property issues\cite{2014The}.RISC-V provides an alternative to traditional commercial instruction set architectures.
-OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\cite{osti_1560133}; openEuler has joined RISC-V International, and RISC-V has officially become openEuler's official support architecture.The RISC-V SIG took the lead in completing the mainline integration of openEuler RISC-V 23.09\cite{osti_1560132}.
+RISC-V is an emerging open-source and reduced ISA \textcolor{red}{with the development of XXX.} \textcolor{blue}{which avoids potential risks such as intellectual property issues\cite{2014The}.RISC-V provides an alternative to traditional commercial instruction set architectures.} \textcolor{red}{[Add support for RV architecture from various operating system.
+For example, given a duration, provide the number of porting.]} OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\cite{osti_1560133}; \textcolor{red}{OpenEuler}\textcolor{blue}{openEuler} has joined RISC-V International \textcolor{red}{organization}, and RISC-V has officially become openEuler's official support architecture.\textcolor{red}{ The RISC-V SIG took the lead in completing the mainline integration of openEuler RISC-V 23.09\cite{osti_1560132}}.\textcolor{blue}{The mainline integraton of OpenEuler RISC-V 23.09\cite{osti_1560132} was finished by the RISC-V SIG.}
 
 Although RISC-V has already made initial progress in having a relatively complete tool chain, it still requires the support of a large number of application software \cite{2019Notary}.
-However, establishing a mature software ecosystem still face challenges.
+\textcolor{red}{Hence} \textcolor{blue}{However}, establishing a mature software ecosystem still face challenges.
+\textcolor{red}{To adapt to the RISC-V, efficient porting of RPM packages is greatly depending on domain expertise of programmers and is still time-consuming.}
 Currently, there is a lack of standardized metrics to measure software architecture portability,and porting planning relies on domain expertise.The difficulty in estimating porting work leads to challenges in accurately allocating resources;In the context of varying levels of developers' skills in porting, there is an even greater need to efficiently assess the difficulty of software package porting and provide guidance to developers of all kinds.In order to solve these problems,one of the methods is to make analogies with adapted projects to gain porting experience,but it is difficult to extract factors by manual sorting;Even if developers have sensitivity to architecture-related modules, it is still challenging to accurately obtain the workload.

### 2024-01-26 Paper/latex/paper-26.tex
Add files via upload

--- 2024-01-24 Paper/latex/paper.tex
@@
 \section{Introduction}
-RISC-V is an emerging open-source and reduced ISA which avoids potential risks such as intellectual property issues\cite{2014The}.RISC-V provides an alternative to traditional commercial instruction set architectures.
-OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\cite{osti_1560133}; openEuler has joined RISC-V International, and RISC-V has officially become openEuler's official support architecture.The RISC-V SIG took the lead in completing the mainline integration of openEuler RISC-V 23.09\cite{osti_1560132}.
+RISC-V is an emerging open-source and reduced ISA \textcolor{red}{with the development of XXX.} \textcolor{blue}{which avoids potential risks such as intellectual property issues\cite{2014The}.RISC-V provides an alternative to traditional commercial instruction set architectures.} \textcolor{red}{[Add support for RV architecture from various operating system.
+For example, given a duration, provide the number of porting.]} OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\cite{osti_1560133}; \textcolor{red}{OpenEuler}\textcolor{blue}{openEuler} has joined RISC-V International \textcolor{red}{organization}, and RISC-V has officially become openEuler's official support architecture.\textcolor{blue}{ The RISC-V SIG took the lead in completing the mainline integration of openEuler RISC-V 23.09\cite{osti_1560132}}.\textcolor{red}{The mainline integraton of OpenEuler RISC-V 23.09\cite{osti_1560132} was finished by the RISC-V SIG.}
+\textcolor{orange}{In recent years, the RISC-V Instruction Set Architecture (ISA) has garnered significant attention from academia, particularly the industry, due to its open-source and reduced design.\citep{2014The}.OpenEuler has joined RISC-V International organization, and RISC-V has officially become openEuler's official support architecture.The mainline integration of openEuler RISC-V 23.09 was finished by the RISC-V SIG.The main repository of openEuler 23.03 has successfully ported 4,244 software packages to the RISCV64,while the openEuler 23.09 main repository has currently completed the porting work of 5,694 software packages\citep{osti_1560132}.OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\citep{osti_1560133}.}
 
 Although RISC-V has already made initial progress in having a relatively complete tool chain, it still requires the support of a large number of application software \cite{2019Notary}.
-However, establishing a mature software ecosystem still face challenges.
+\textcolor{red}{Hence} \textcolor{blue}{However}, establishing a mature software ecosystem still face challenges.
+\textcolor{red}{To adapt to the RISC-V, efficient porting of RPM packages is greatly depending on domain expertise of programmers and is still time-consuming.}
 Currently, there is a lack of standardized metrics to measure software architecture portability,and porting planning relies on domain expertise.The difficulty in estimating porting work leads to challenges in accurately allocating resources;In the context of varying levels of developers' skills in porting, there is an even greater need to efficiently assess the difficulty of software package porting and provide guidance to developers of all kinds.In order to solve these problems,one of the methods is to make analogies with adapted projects to gain porting experience,but it is difficult to extract factors by manual sorting;Even if developers have sensitivity to architecture-related modules, it is still challenging to accurately obtain the workload.
+\textcolor{orange}{Despite the rapid development of the RISC-V ISA, which foundational software such as operating systems and compilers are relatively mature, there is still a significant demand for porting a large number of application software.\citep{2019Notary}.
+However, establishing a mature software ecosystem still face challenges.To adapt to the RISC-V,efficiently porting software package is greatly depending on domain expertise and is characterized by significant costs and resources.
+During the initial planning phase of porting, the lack of standardized evaluation criteria for software portability can lead to misallocation of resources in the development process.
+Even for developers who are well-versed in architecture code, accurately estimating the extent of modifications required in the project can be challenging.
+Therefore, it is desirable to propose a method that automates the assessment of porting complexity, converting expert knowledge into evaluation standards.
+This will enable different development teams to access software packages that are tailored to their proficiency levels, thus assisting distribution vendors in the porting of RISC-V architecture.}
 Du Jiman et al.
 have developed a basic statistical evaluation plan for CPU architecture code in project \cite{2023du}, however, their work lacks a thorough validity analysis and comparison of factors,and fails to consider the complexity associated with the software operation and maintenance process.
-
-RAX can provide developers with accurate evaluation, recommend software with different levels of porting difficulty based on their skill levels.
+\textcolor{orange}{Du et al.
+have developed a basic statistical evaluation plan for CPU architecture code in project\citep{2023du},however,their work lacks a thorough validity analysis of factors,and fails to consider the complexity associated with the software operation and maintenance process.}
+RRAX can provide developers with accurate evaluation, recommend software with different levels of porting difficulty based on their skill levels. The contributions of this paper are as follows:
 The contributions of this paper are as follows:
@@
   \item Evaluate the effectiveness of RAX.
-  We nearly doubled the dataset compared to Du Jiman's tool,and verified the effectiveness of the evaluation of 100 extension projects in real porting scenarios through their respective communities or forums.
-We received 50 valid responses.Our findings indicate that RAX outperforms the Du Jiman's tool, delivering substantial improvements in terms of performance and accuracy..
+ We nearly doubled the dataset compared to Du Jiman's tool,and verified the effectiveness of the evaluation of extension projects in real porting scenarios through their respective communities or forums.
+We received 50 valid responses.Our findings indicate that RAX outperforms the Du Jiman's tool, delivering substantial improvements in terms of performance and accuracy.
 \end{enumerate}
@@
 
-\textbf{Research Question 1:} Developers often struggle to make fine-grained differentiations in the complexity of porting projects.
-How can we select architecture-relevant factors to design an automated tool that assesses the porting difficulty?
-We analyzes the porting modifications obtained from developer Commit in the Git tool.
-We conducts an effectiveness analysis of the selected factors and filters out strongly correlated ones that can be automatically identified using the Lines of Code (LOC) approach.
-Additionally, we propose a CC assessment method to jointly establish a data set for porting complexity.
+\textbf{RQ 1:} How can we select architecture-relevant actors that is fine-grained to design an automated tool that assesses the porting difficulty?
 
-\textbf{Research question 2:} How to select a classifier to obtain effective classification results for the tool?
-Using the processing method of unbalanced datasets, multiple machine learning models are compared to select the final classifier.
+\textbf{RQ 2:} How to select a classifier to obtain effective classification results for the tool?
 

### 2024-01-26 Paper/latex/paper-1.tex
update

--- 2024-01-25 Paper/latex/paper.tex
@@
 RISC-V is an emerging open-source and reduced ISA \textcolor{red}{with the development of XXX.} \textcolor{blue}{which avoids potential risks such as intellectual property issues\cite{2014The}.RISC-V provides an alternative to traditional commercial instruction set architectures.} \textcolor{red}{[Add support for RV architecture from various operating system.
-For example, given a duration, provide the number of porting.]} OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\cite{osti_1560133}; \textcolor{red}{OpenEuler}\textcolor{blue}{openEuler} has joined RISC-V International \textcolor{red}{organization}, and RISC-V has officially become openEuler's official support architecture.\textcolor{red}{ The RISC-V SIG took the lead in completing the mainline integration of openEuler RISC-V 23.09\cite{osti_1560132}}.\textcolor{blue}{The mainline integraton of OpenEuler RISC-V 23.09\cite{osti_1560132} was finished by the RISC-V SIG.}
+For example, given a duration, provide the number of porting.]} OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\cite{osti_1560133}; \textcolor{red}{OpenEuler}\textcolor{blue}{openEuler} has joined RISC-V International \textcolor{red}{organization}, and RISC-V has officially become openEuler's official support architecture.\textcolor{blue}{ The RISC-V SIG took the lead in completing the mainline integration of openEuler RISC-V 23.09\cite{osti_1560132}}.\textcolor{red}{The mainline integraton of OpenEuler RISC-V 23.09\cite{osti_1560132} was finished by the RISC-V SIG.}
 

### 2024-01-26 Paper/latex/paper.tex
update

--- 2024-01-24 Paper/latex/paper.tex
@@
   \centering
-  \includegraphics[width=\linewidth]{correlation.pdf}
+  \includegraphics[width=\linewidth]{figure3.pdf}
   \caption{The Correlation}

### 2024-01-26 Paper/latex2/paper-26.tex
Add files via upload

--- 2024-01-26 Paper/latex/paper.tex
@@
 \begin{abstract}
-In recent years, RISC-V instruction set architecture(ISA) has attracted the attention of the information technology industry due to its open source, modular design, and simplicity.
-However, there is a lack of standardized metrics and methods to measure software architecture portability, which helps to establish a mature software ecosystem in RISC-V.
-A theoretical framework is urgently needed as a guide to summarize important porting-related factors and design an automated RISC-V-oriented porting complexity evaluation tool to solve the problem.
-We propose RAX, it will help recommend software with varying degrees of porting complexity to development teams.
-RAX first retrieves porting modification information of the adapted project according to the Git version control tool, classifies it through manual analysis, and selects the most important porting factors to design the code positioning mode.
-Additionally, it incorporates Cyclomatic Complexity, which is from code evaluation domain, to enhance assessment accuracy and measure the overall complexity of the software.
-We establish a high-quality data set of software porting complexity, and select random forest machine learning model as the final classifier through multi-model comparison.
+  Due to the lack of publicly available standards for assessing software portability, the software porting process for the RISC-V architecture has been predominantly reliant on expert experience, presenting obstacles.
+This paper introduces an automated tool, RAX, for assessing the porting complexity specifically for RISC-V by considering architecture-specific code and code Cyclomatic Complexity.RAX provides precise evaluation solutions and establishes a high-quality dataset for porting complexity assessment,enabling recommendations of suitable software difficulty levels for developers of varying skill levels.We continue to expand the dataset and conduct effective evaluations of the tool within the open-source community.We have gathered valuable feedback, including 47 positive responses, from 51 specific open-source projects.Interested users can explore the open-source implementation of RAX at (https://github.com/wangyuliu/R
+  AX-2024), or watch the RAX video demo at (https://github.com/wan
+  gyuliu/RAX-2024).
 \end{abstract}
@@
 \section{Introduction}
-RISC-V is an emerging open-source and reduced ISA \textcolor{red}{with the development of XXX.} \textcolor{blue}{which avoids potential risks such as intellectual property issues\cite{2014The}.RISC-V provides an alternative to traditional commercial instruction set architectures.} \textcolor{red}{[Add support for RV architecture from various operating system.
-For example, given a duration, provide the number of porting.]} OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\cite{osti_1560133}; \textcolor{red}{OpenEuler}\textcolor{blue}{openEuler} has joined RISC-V International \textcolor{red}{organization}, and RISC-V has officially become openEuler's official support architecture.\textcolor{blue}{ The RISC-V SIG took the lead in completing the mainline integration of openEuler RISC-V 23.09\cite{osti_1560132}}.\textcolor{red}{The mainline integraton of OpenEuler RISC-V 23.09\cite{osti_1560132} was finished by the RISC-V SIG.}
 \textcolor{orange}{In recent years, the RISC-V Instruction Set Architecture (ISA) has garnered significant attention from academia, particularly the industry, due to its open-source and reduced design.\citep{2014The}.OpenEuler has joined RISC-V International organization, and RISC-V has officially become openEuler's official support architecture.The mainline integration of openEuler RISC-V 23.09 was finished by the RISC-V SIG.The main repository of openEuler 23.03 has successfully ported 4,244 software packages to the RISCV64,while the openEuler 23.09 main repository has currently completed the porting work of 5,694 software packages\citep{osti_1560132}.OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\citep{osti_1560133}.}
 
-Although RISC-V has already made initial progress in having a relatively complete tool chain, it still requires the support of a large number of application software \cite{2019Notary}.
-\textcolor{red}{Hence} \textcolor{blue}{However}, establishing a mature software ecosystem still face challenges.
-\textcolor{red}{To adapt to the RISC-V, efficient porting of RPM packages is greatly depending on domain expertise of programmers and is still time-consuming.}
-Currently, there is a lack of standardized metrics to measure software architecture portability,and porting planning relies on domain expertise.The difficulty in estimating porting work leads to challenges in accurately allocating resources;In the context of varying levels of developers' skills in porting, there is an even greater need to efficiently assess the difficulty of software package porting and provide guidance to developers of all kinds.In order to solve these problems,one of the methods is to make analogies with adapted projects to gain porting experience,but it is difficult to extract factors by manual sorting;Even if developers have sensitivity to architecture-related modules, it is still challenging to accurately obtain the workload.
 \textcolor{orange}{Despite the rapid development of the RISC-V ISA, which foundational software such as operating systems and compilers are relatively mature, there is still a significant demand for porting a large number of application software.\citep{2019Notary}.
@@
 This will enable different development teams to access software packages that are tailored to their proficiency levels, thus assisting distribution vendors in the porting of RISC-V architecture.}
-Du Jiman et al.
-have developed a basic statistical evaluation plan for CPU architecture code in project \cite{2023du}, however, their work lacks a thorough validity analysis and comparison of factors,and fails to consider the complexity associated with the software operation and maintenance process.
+
 \textcolor{orange}{Du et al.
 have developed a basic statistical evaluation plan for CPU architecture code in project\citep{2023du},however,their work lacks a thorough validity analysis of factors,and fails to consider the complexity associated with the software operation and maintenance process.}
-RRAX can provide developers with accurate evaluation, recommend software with different levels of porting difficulty based on their skill levels. The contributions of this paper are as follows:
+RAX can provide developers with accurate evaluation, recommend software with different levels of porting difficulty based on their skill levels. The contributions of this paper are as follows:
 The contributions of this paper are as follows:
@@
   \item Evaluate the effectiveness of RAX.
- We nearly doubled the dataset compared to Du Jiman's tool,and verified the effectiveness of the evaluation of extension projects in real porting scenarios through their respective communities or forums.
-We received 50 valid responses.Our findings indicate that RAX outperforms the Du Jiman's tool, delivering substantial improvements in terms of performance and accuracy.
+ We nearly doubled the dataset compared to Du's tool,and verified the effectiveness of the evaluation of extension projects in real porting scenarios through their respective communities or forums.
+We received 51 valid responses.Our findings indicate that RAX outperforms previous work, delivering substantial improvements in terms of performance and accuracy.
 \end{enumerate}
@@
 \section{RAX}
-The following is an introduction to the process of RAX construction, as shown in Figure \ref{fig:flow-chart}.
-During the analysis phase,architecture-related factors are obtained through the Commit tool for selection.
+The following is an introduction to the process of RAX construction, as shown in Figure \ref{fig:figure1}.
+During the analysis phase,architecture-related factors are obtained through the Commit tool for selection while investigating the impact of code complexity metrics on porting.
 A scanning tool is built to get potential modification workload.
 Finally,an appropriate machine learning model is selected as a classification.
-
 \begin{figure}
   \centering
-  \includegraphics[width=\linewidth]{flow-chart.pdf}
+  \includegraphics[width=\linewidth]{figure1.pdf}
   \caption{Flow chart for method to build RAX}
-  \label{fig:flow-chart}
+  \label{fig:figure1}
   \Description{Flow chart for method to build RAX}
 \end{figure}
-
 \subsection{Motivation}
 The section provides a validity analysis of porting-related factors on RAX.
-First,we use code complexity metrics to evaluate porting work.
-The software metrics of code Cyclomatic Complexity(CC) can help developers make macro judgments on software complexity and maintenance difficulty, evaluate potential and hidden porting difficulties, and help the tool improve accuracy \cite{2005Exploring}.
+First,we try to use code complexity metrics to evaluate porting work.
+The software metrics of code Cyclomatic Complexity(CC) can help developers make macro judgments on software complexity and maintenance difficulty, evaluate potential and hidden porting difficulties,which help the tool improve accuracy \cite{2005Exploring}.
 At present, CC indicators are mostly used in project code quality assessment, defect inspection, code reconstruction, etc \cite{1991Cyclomatic}.
-During the porting process, developers will target a large number of project source codes, scripts, assembly codes,and a macro understanding of the project is required in the early stage of porting.
-This part of the work has a lot of overlap with the scope of code complexity.
+During the porting process, developers will target a large number of project source codes,build scripts,assembly codes,and a macro understanding of the project is required in the early stage of porting.
+This part of the work has a lot of overlap with the scope of code complexity.Through our survey of community, we have discovered that even though architectural code can be separated quite clearly from common code, when faced with complex and large-scale projects, we still require numerous iterative tests to uncover unknown architectural code.
+Building upon this, we delve into the quantification of the significance of cyclomatic complexity in porting work.
 
@@
 This study analyzes the relationship between CC and software porting complexity using the Spearman Rank correlation coefficient analysis method.
-We invited five Master's students who are engaged in research on porting auxiliary tools to score the porting complexity(score) of 131 software adapted for RISC-V,collected from the OpenEule list and GitHub.
+We invited five Master's students who are engaged in research on porting auxiliary tools to score the porting complexity(score) of 131 software adapted for RISC-V,collected from the OpenEule list\citep{stage2023} and GitHub.
 According to the collection of Internet events, log analysis, source code dismantling, and similar project analogy \cite{liangguanyu2020}, we form a scoring interval in the range of $[0~5]$.
-We then calculated the Spearman correlation coefficient and conducted significance analysis between score and the CC factors.
 The Spearman coefficient is 0.608, with a P-value of 1.39e-14, which is less than 0.01.
-This indicates a significant correlation between the two variables.
 The results suggest that CC has a moderate positive correlation with porting difficulty.
-This is because developers need a holistic understanding of the project during the porting process, and CC can represent the overall complexity of the project, potentially reflecting porting barriers, as shown in Figure \ref{fig:relationship}.
+This is because developers need a holistic understanding of the project during the porting process, and CC can represent the overall complexity of the project, potentially reflecting porting barriers, as shown in Figure \ref{fig:figure2}.
+
 Secondly,we focus on the code associated with architecture in the project,with the goal of predicting porting workload through these code.
-
 \begin{figure}
   \centering
-  \includegraphics[width=\linewidth]{relationship.pdf}
+  \includegraphics[width=\linewidth]{figure2.pdf}
   \caption{The relationship between score and CC}
-  \label{fig:relationship}
+  \label{fig:figure2}
   \Description{The relationship between score and CC}
 \end{figure}
-
 \subsubsection{Factor2:Arch\_code}
@@
 %\end{table}
-Correlation comparison between Arch\_code and other factors acquired by Commit analyzer,as shown in Figure \ref{fig:correlation}:
+Correlation comparison between Arch\_code and other factors acquired by Commit analyzer,as shown in Figure \ref{fig:figure3}:
 \begin{figure}
@@
   \caption{The Correlation}
-  \label{fig:correlation}
+  \label{fig:figure3}
   \Description{The Correlation}
 \end{figure}
-
-The results indicate that Arch\_code has a higher correlation with score compared to other factors, and it also aligns with the significant results of the Spearman correlation test.
+The results indicate that Arch\_code has a higher correlation with score compared to other factors, and it also aligns with the significant results of the Peason correlation test.
 The use of only architecture keywords for statistics yields moderate effectiveness in evaluating tool because keywords can only be detected from comments and macro sections of Commit, while critical porting code may lack these keywords,but the keyword count can reflect the amount of porting modification from the side.
@@
   \item Conditional compilation and architecture macros are used as preprocessor macros to enable projects to select execution on different hardware architectures, thus demonstrating the additional workload of architecture porting.
-  Use conditional compilation statements, such as ``if defined'', ``ifdef'', in conjunction with all possible architectur macros,``\_\_x86\_64\_\_''.
+  Use conditional compilation statements, such as ``if defined'', ``ifdef'', in conjunction with all possible architectur macros,
+  ``\_\_x86\_64\_\_''.
   We use a similar bracket matching algorithm to cover all the code within macros, avoiding the impact of nested layers.
@@
     Adaboost & 0.786 & 0.594 & 0.775 & 0.650 \\
-    Random Forest & 0.857 & 0.817 & 0.873 & 0.836 \\
+    Random Forest & \textcolor{red}{0.857} & 0.817 & 0.873 & 0.836 \\
   \bottomrule
@@
 Appendix presents a comparative assessment of the porting complexity evaluation tool developed by Du Jiman et al.
-across various projects.Through real-world evaluations within the developer community, our tool has exhibited a significant improvement in accuracy, surpassing other comparable tools by a margin of 14\%.
+across various projects.Through real-world evaluations within the developer community, our tool has exhibited a significant improvement in accuracy, surpassing other comparable tools by a margin of 15.6\%.
 In the appendix, we provide a comprehensive compilation of the community's valuable feedback comments, accompanied by the relevant web links for further reference and validation.
@@
     \midrule
-    Low &31/36 & 5/36 & 34/36 & 2/36 \\
+    Low &32/37 & 5/37 & 35/37 & 2/37 \\
     Medium & 5/8 & 3/8 & 6/8 & 2/8 \\
-    High & 3/6 & 3/6 & 6/6 & 0/6 \\
+    High & 2/6 & 4/6 & 6/6 & 0/6 \\
     \midrule
-    Total & \textcolor{red}{39/50} & 11/50& \textcolor{red}{46/50} & 4/50 \\
+    Total & \textcolor{red}{39/51} & 12/51& \textcolor{red}{47/51} & 4/51 \\
       \bottomrule
@@
 After adding the code complexity factor and modifying the original tool design model, RAX's result prediction accuracy is improved.
-This is because code complexity can effectively distinguish projects with low porting difficulty from projects with medium and high porting difficulty.
+This is because code complexity can effectively distinguish projects with low porting complexity from projects with medium and high porting complexity.
 Motivation Chapters present the cause analysis.
@@
 However, when it came to evaluating the work involved in iterative updates between versions, existing tools proved insufficient for precise estimation.Sometimes developers design their work has generic code for unknown architecture and CPU architecture parts are well separated from the common code,that just need only to adjust the macro to recognize RISC-V,like nuttx.
-
 \section{Related Work}
@@
 They conducted a comprehensive study on various existing code complexity metrics' validity and suggested incorporating empirically observed code features as complexity triggers.
-
 \section{Conclusion}
@@
 We incorporate the code complexity to reflect developers' actual workload.
-Additionally, we conduct a correlation analysis of Arch\_code; Analyze the defects and improvements of factor statistical methods, and finally build a scanning tool.
-Using a Random Forest machine learning model, we perform classification learning on 234 projects collected from the OpenEuler:Stage2 list and GitHub.
-When compared to the previous version of the tool, our approach yields improved predictive performance.
-Moreover, RAX provides developers with the functionality to locate target code segments.
-Our next steps involve attempting text classification methods to categorize the text results of the scanning tool, designing more granular statistical methods for architecture-related factors.
-
+We verified the effectiveness of the evaluation of 51 extension projects in real porting scenarios through their respective communities or forums.
+Observed significant performance improvements compared to previous tools.Moreover, RAX provides developers with the functionality to locate target code segments.Our next steps involve attempting text classification methods to categorize the text results of the scanning tool, designing more granular statistical methods for architecture-related factors.
 %%

### 2024-01-26 Paper/latex2/paper.tex
Add files via upload

--- 2024-01-26 Paper/latex2/paper-26.tex
@@
 \begin{abstract}
-  Due to the lack of publicly available standards for assessing software portability, the software porting process for the RISC-V architecture has been predominantly reliant on expert experience, presenting obstacles.
+  In recent years, the RISC-V’s open-source and reduced features have received active promotion of porting from the industry.Due to the lack of publicly available standards for assessing software portability, the software porting process for the RISC-V architecture has been predominantly reliant on expert experience, presenting obstacles.
 This paper introduces an automated tool, RAX, for assessing the porting complexity specifically for RISC-V by considering architecture-specific code and code Cyclomatic Complexity.RAX provides precise evaluation solutions and establishes a high-quality dataset for porting complexity assessment,enabling recommendations of suitable software difficulty levels for developers of varying skill levels.We continue to expand the dataset and conduct effective evaluations of the tool within the open-source community.We have gathered valuable feedback, including 47 positive responses, from 51 specific open-source projects.Interested users can explore the open-source implementation of RAX at (https://github.com/wangyuliu/R
@@
 
-\textcolor{orange}{Despite the rapid development of the RISC-V ISA, which foundational software such as operating systems and compilers are relatively mature, there is still a significant demand for porting a large number of application software.\citep{2019Notary}.
-However, establishing a mature software ecosystem still face challenges.To adapt to the RISC-V,efficiently porting software package is greatly depending on domain expertise and is characterized by significant costs and resources.
-During the initial planning phase of porting, the lack of standardized evaluation criteria for software portability can lead to misallocation of resources in the development process.
-Even for developers who are well-versed in architecture code, accurately estimating the extent of modifications required in the project can be challenging.
-Therefore, it is desirable to propose a method that automates the assessment of porting complexity, converting expert knowledge into evaluation standards.
-This will enable different development teams to access software packages that are tailored to their proficiency levels, thus assisting distribution vendors in the porting of RISC-V architecture.}
+\textcolor{orange}{Despite the rapid development of the RISC-V ISA, which foundational software such as operating systems and compilers are relatively mature, there is still a significant demand for porting a large number of application software.\citep{2019Notary}.To adapt to the RISC-V,efficiently porting software package is greatly depending on domain expertise.
+During the initial planning phase of porting, the lack of standardized evaluation criteria for software portability can lead to misallocation of resources in the development process.Therefore, it is desirable to propose a method that automates the assessment of porting complexity,this will enable different development teams to access software packages that are tailored to their proficiency levels, thus assisting distribution vendors in the porting of RISC-V architecture.}
 
@@
 have developed a basic statistical evaluation plan for CPU architecture code in project\citep{2023du},however,their work lacks a thorough validity analysis of factors,and fails to consider the complexity associated with the software operation and maintenance process.}
+
 RAX can provide developers with accurate evaluation, recommend software with different levels of porting difficulty based on their skill levels. The contributions of this paper are as follows:
@@
 \begin{enumerate}
-  \item Firstly, we conducted analysis on selection of factors related the porting evaluation,investigated the significance of code complexity metrics in the context of porting work and incorporated Cyclomatic Complexity as a factor to assess the overall complexity of  the project.
-  \item Based on porting-related factors, we designed a scanning tool to collect porting complexity vectors and ultimately selected random forest machine learning model as the classifier for RAX.
-  \item Evaluate the effectiveness of RAX.
- We nearly doubled the dataset compared to Du's tool,and verified the effectiveness of the evaluation of extension projects in real porting scenarios through their respective communities or forums.
-We received 51 valid responses.Our findings indicate that RAX outperforms previous work, delivering substantial improvements in terms of performance and accuracy.
+  \item In recent years, the RISC-V’s open-source and reduced features have received active promotion of porting from the industry.
+  \item Optimization Assessment Tool.Tuning machine learning models to address ambiguous identification of samples of medium and hard complexity.
+  \item We nearly doubled the dataset compared to other tool,and verified the effectiveness of the evaluation of 51 extension projects in real porting scenarios through their respective communities or forums.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of performance and accuracy.
 \end{enumerate}
@@
 \subsection{Motivation}
-The section provides a validity analysis of porting-related factors on RAX.
+To design RAX that assists developers with porting work,the following research questions are proposed:
+
+\textbf{RQ 1:} How can we select architecture-relevant actors that is fine-grained to design an automated tool that assesses the porting difficulty?
+
+\textbf{RQ 2:} How to select a classifier to obtain effective classification results for the tool?
+
+To answer research question 1,this section provides a validity analysis of porting-related factors on RAX.
 First,we try to use code complexity metrics to evaluate porting work.
@@
 \label{sec:factor-1}
-RAX tool uses the lizard CC detection tool and optimize its functions,we will introduce it in Section \ref{sec:method}.
+We uses the lizard CC detection tool and optimize its functions,and it will introduce it in Section \ref{sec:method}.
 This study analyzes the relationship between CC and software porting complexity using the Spearman Rank correlation coefficient analysis method.
@@
 According to the collection of Internet events, log analysis, source code dismantling, and similar project analogy \cite{liangguanyu2020}, we form a scoring interval in the range of $[0~5]$.
-The Spearman coefficient is 0.608, with a P-value of 1.39e-14, which is less than 0.01.
+The Spearman coefficient of CC and score is 0.608, with a P-value of 1.39e-14, which is less than 0.01.
 The results suggest that CC has a moderate positive correlation with porting difficulty.
@@
 
-Secondly,we focus on the code associated with architecture in the project,with the goal of predicting porting workload through these code.
+Second, we consider the effectiveness of the architecture binding code structure proposed by the other tool and conduct comparative experiments using more potential factors.
 \begin{figure}
@@
 
-First, extract all possible architecture-related factors.
-Use the Git tool to split Commit into different files using git-diff and filter out the surrounding 20 lines of content containing architecture keywords for detailed analysis of the modifications.
-The manually analyzed Commit generally includes the following parts: first, functional supplements, including lack of dependent package calls, performance optimization and test cases for architecture porting;second, detail adjustments for data type and Build script;finally, key function implementation, assembly code, built-in function, system call, etc.
-Among these factors, we select more objective ones that can be automatically located through regular expression matching.
-
-Arch\_code defines assembly code, conditional compilation and macro structure, Intrinsic functions, Builtin functions, architecture-related build scripts, and system calls.
-We use an automated architecture binding code scanning module to obtain statistics on the number of lines and frequencies of Arch\_code.
+Based on the analysis of previous evaluation tools, we selected factors with the greatest potential and that can be extracted through automated methods to define Arch\_code.
+Arch\_code includes assembly code, conditional compilation and macro structure, Intrinsic functions, Builtin functions, architecture-related build scripts, and system calls.
+We use an automated architecture binding code scanning tool to obtain statistics on the number of lines and frequencies of Arch\_code.
 
@@
   \includegraphics[width=\linewidth]{figure3.pdf}
-  \caption{The Correlation}
+  \caption{The heat map of pearson correlation}
   \label{fig:figure3}
@@
 The use of only architecture keywords for statistics yields moderate effectiveness in evaluating tool because keywords can only be detected from comments and macro sections of Commit, while critical porting code may lack these keywords,but the keyword count can reflect the amount of porting modification from the side.
-As shown in the figure 2, there may be great ambiguity in keyword positioning using different architectures.
-So we only selected x86 for positioning, which represents the most fair workload.
-In the end, the parameters of Arch\_code show a correlation of 0.43 to 0.75 with score, indicating a strong relationship.
+As shown in the figure 2,the parameters of Arch\_code show a correlation of 0.45 to 0.75 with score, indicating a strong relationship.
 However, using a single factor alone does not result in a significantly strong correlation, as the combined modifications of these factors make up the porting workload.
 
-To design RAX that assists developers with porting work,the following research questions are proposed:
+In the end,our tool selection was CC and the Arch\_code build scanning tool,as shown table 1.
 
-\textbf{RQ 1:} How can we select architecture-relevant actors that is fine-grained to design an automated tool that assesses the porting difficulty?
+% To design RAX that assists developers with porting work,the following research questions are proposed:
 
-\textbf{RQ 2:} How to select a classifier to obtain effective classification results for the tool?
+% \textbf{RQ 1:} How can we select architecture-relevant actors that is fine-grained to design an automated tool that assesses the porting difficulty?
+
+% \textbf{RQ 2:} How to select a classifier to obtain effective classification results for the tool?
+
+% \begin{table}
+%   \caption{Tool factors comparison table}
+%   \label{tab:comparisons}
+%   \begin{tabular}{ccccc}
+%     \toprule
+%     Porting Complexity & \multicolumn{2}{c}{Du's Tool} & \multicolumn{2}{c}{RAX} \\
+%      & TP & FN & TP & FN \\
+%     \midrule
+%     Low &32/37 & 5/37 & 35/37 & 2/37 \\
+%     Medium & 5/8 & 3/8 & 6/8 & 2/8 \\
+%     High & 2/6 & 4/6 & 6/6 & 0/6 \\
+%     \midrule
+%     Total & \textcolor{red}{39/51} & 12/51& \textcolor{red}{47/51} & 4/51 \\
+%       \bottomrule
+% \end{tabular}
+% \end{table}
+
+\begin{table}
+  \caption{Tool factors comparison}
+  \label{tab:Tool}
+  \begin{tabular}{ccccccc}
+    \toprule
+    & Asm & Intrinsic & Builtin & Conditional compilation and macro & Buildscripts & CC \\
+    \midrule
+    Toolone & 1 & 1 & 1 & 1 & 1 & 0\\
+    RAX & 1 & 1 & 1 & 1 & 1 & 1 \\
+  \bottomrule
+\end{tabular}
+\end{table}
+
+% \begin{table}
+%   \caption{Tool factors comparison}
+%   \label{tab:comparisont}
+%   \begin{tabular}{ccccc}
+%     \toprule
+%      & Accuracy & Pmacro & Rmacro & F1macro \\
+%     \midrule
+%     Adaboost & 0.786 & 0.594 & 0.775 & 0.650 \\
+%     Random Forest & \textcolor{red}{0.857} & 0.817 & 0.873 & 0.836 \\
+%   \bottomrule
+% \end{tabular}
+% \end{table}
 
@@
 The evaluation scores are divided into three categories: low, medium, and high\citep{githuburl}.This includes 139 projects as training, testing, and validation datasets, while more than 80 additional projects were used as a tool evaluation dataset.
-To gather insights from developers, the community, forums, and emails were utilized, resulting in over 50 meaningful feedback responses.
+To gather insights from developers, the community, forums, and emails were utilized, resulting in over 51 meaningful feedback responses.
 In order to address the issue of data imbalance caused by collecting datasets solely from the openEuler mailing list, where more than 80\% of the projects were initially evaluated as having low porting complexity, a greater emphasis was placed on projects that had higher numbers of likes on GitHub and were deemed more important and active.
@@
 
-\subsubsection{Lizard CC calculation module}
+\subsubsection{Lizard CC calculation scan function}
 Lizard's default computing method is basically consistent with McCabe's theory \cite{1702388}.
@@
   \item First, calculate the function-level CC for all files in the project using McCabe's method.
-  \item Following Liu Huihui's mention of System Cyclomatic Complexity (SCC) in software evolution assessment techniques based on code change detection \cite{liuhuihui00}, we define SCC as the total sum of function-level values in the system.
+  \item Following Liu's mention of System Cyclomatic Complexity (SCC) in software evolution assessment techniques based on code change detection \cite{liuhuihui00}, we define SCC as the total sum of function-level values in the system.
   The advantage is that it can avoid the use of overly complex methods, which will cause deviations to affect the classification results.
-  Additionally, it eliminates the problem of decreased detection performance caused by program transformation into syntax abstract trees and control flow graphs.
+  Additionally,due to the system's complexity being calculated based on a single function,it eliminates the problem of decreased detection performance caused by the conversion of such a large code structure of all modules into into syntax abstract trees and control flow graphs.
 \end{enumerate}

### 2024-01-27 Paper/latex1-27/paper.tex
Add files via upload

--- 2024-01-26 Paper/latex2/paper.tex
@@
   \item In recent years, the RISC-V’s open-source and reduced features have received active promotion of porting from the industry.
-  \item Optimization Assessment Tool.Tuning machine learning models to address ambiguous identification of samples of medium and hard complexity.
+  \item We explore building high-quality datasets that can cover various porting scenarios to solve the problem of imbalanced datasets of previous tools.Tuning machine learning models to address ambiguous identification of samples of medium and hard complexity.
   \item We nearly doubled the dataset compared to other tool,and verified the effectiveness of the evaluation of 51 extension projects in real porting scenarios through their respective communities or forums.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of performance and accuracy.
@@
 
-\textbf{RQ 2:} How to select a classifier to obtain effective classification results for the tool?
+\textbf{RQ 2:} How to solve the problem of vague classification of projects with medium and high porting difficulty in previous tools?
 
@@
 Continue to collect other factors that may affect the evaluation of porting complexity,and select the following parameters through the Commit analyzer:architecture-related code lines, architecture-related files, and architecture keywords.
-The number of architecture-related code lines and files is located using the keywords of X86, ARM, MIPS, RISCV, SPARC and other architectures.
+The number of architecture-related code lines and files is located using the keywords of the RISC-V architecture, such as riscv, rv32, rv64, RISC-V, RISCV and so on.
 %Correlation comparison between Arch\_code and other factors acquired by Commit analyzer,as shown in Table \ref{tab:score}:
@@
 %\end{table}
+
+\begin{table*}
+  \caption{Tool factors comparison}
+  \label{tab:Tool}
+  \begin{tabular}{ccccccccc}
+    \toprule
+    & Full Assembly & Inline Assembly & Intrinsic & Builtin & System Call & Conditional compilation and macro & Buildscripts & CC \\
+    \midrule
+    Other tool & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \\
+    RAX & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\
+  \bottomrule
+\end{tabular}
+\end{table*}
+
 Correlation comparison between Arch\_code and other factors acquired by Commit analyzer,as shown in Figure \ref{fig:figure3}:
@@
 The use of only architecture keywords for statistics yields moderate effectiveness in evaluating tool because keywords can only be detected from comments and macro sections of Commit, while critical porting code may lack these keywords,but the keyword count can reflect the amount of porting modification from the side.
-As shown in the figure 2,the parameters of Arch\_code show a correlation of 0.45 to 0.75 with score, indicating a strong relationship.
+As shown in the Figure \ref{fig:figure3},the parameters of Arch\_code show a correlation of 0.45 to 0.75 with score, indicating a strong relationship.
 However, using a single factor alone does not result in a significantly strong correlation, as the combined modifications of these factors make up the porting workload.
 
-In the end,our tool selection was CC and the Arch\_code build scanning tool,as shown table 1.
+In the end,our tool selection was CC and the Arch\_code build scanning tool,as shown in Table \ref{tab:score}.
 
@@
 % \end{table}
+% \documentclass{article}
+% \usepackage{pifont} % 加载pifont宏包
 
-\begin{table}
-  \caption{Tool factors comparison}
-  \label{tab:Tool}
-  \begin{tabular}{ccccccc}
-    \toprule
-    & Asm & Intrinsic & Builtin & Conditional compilation and macro & Buildscripts & CC \\
-    \midrule
-    Toolone & 1 & 1 & 1 & 1 & 1 & 0\\
-    RAX & 1 & 1 & 1 & 1 & 1 & 1 \\
-  \bottomrule
-\end{tabular}
-\end{table}
+% \begin{table*}
+%   \caption{Tool factors comparison}
+%   \label{tab:Tool}
+%   \begin{tabular}{ccccccccc}
+%     \toprule
+%     & Full Assembly & Inline Assembly & Intrinsic & Builtin & System Call & Conditional compilation and macro & Buildscripts & CC \\
+%     \midrule
+%     Toolone & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \\
+%     RAX & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\
+%   \bottomrule
+% \end{tabular}
+% \end{table*}
+
+% \begin{table*}
+%   \caption{The Spearman correlation coefficient of score and architecture-related factors}
+%   \label{tab:score}
+%   \begin{tabular}{cccccc}
+%     \toprule
+%     conditional compilation & Builtin & Intrinstic & syscall & asm & build\_scripts \\
+%     \midrule
+%     0.73 & 0.61 & 0.74 & 0.69 & 0.66 & 0.43 \\
+%   \bottomrule
+% \end{tabular}
+% \begin{tabular}{ccccc}
+%   \toprule
+%   time & authors & lines of arch & files of arch & keyword count \\
+%   \midrule
+%   -0.16 & 0.43 & 0.16-0.40 & 0.34-0.41 & 0.17-0.43 \\
+% \bottomrule
+% \end{tabular}
+% \end{table*}
 
@@
   Additionally,due to the system's complexity being calculated based on a single function,it eliminates the problem of decreased detection performance caused by the conversion of such a large code structure of all modules into into syntax abstract trees and control flow graphs.
+  Our CC calculation approach is expressed by the following equation,where lowercase cc represents the cyclomatic complexity at the function or file level.The uppercase CC represents the overall cyclomatic complexity of the software package,serving as a crucial factor in our tool.Here, |E| denotes the number of edges in the function control flow graph,and |N| represents the number of nodes.The function control flow graph is constructed based on branching structures such as if, while, and switch statements.
+
+  \begin{equation}
+    \mathrm{cc}(\mathrm{function}) = \lvert E \rvert - \lvert N \rvert + 2
+    % \sum_{i=1}^{n} x_i
+    \end{equation}
+    \begin{equation}
+      \mathrm{cc}(\mathrm{file}) =  \sum_{i=1}^{n} \mathrm{cc}(\mathrm{function})
+      \end{equation}
+      \begin{equation}
+        \mathrm{CC} =  \sum_{i=1}^{k} \mathrm{cc}(\mathrm{file})
+        \end{equation}
+
 \end{enumerate}
 
-\subsubsection{Arch\_code location module}
+\subsubsection{Arch\_code scan function}
+Other tools only consider x86 architecture to locate architecture-related code for statistical analysis.
+We propose a new idea that explore whether multiple architectures can be selected or if other architectures can be individually targeted.
+Based on this, we conducted comparative experiments using various architectures, including X86, ARM, MIPS, RISCV, SPARC, and PowerPC.
+We performed scanning and counting based on the keyword and function dictionaries specific to each architecture, which were derived from common patterns summarized from official websites.
+By analyzing the correlation coefficient (Pearson's) between the keyword coverage line statistics of the six architectures and the score representing the porting complexity, we found that the correlation ranged from 0.44 to 0.58, indicating an average correlation across all architectures.
+Additionally, the correlation between the total values for all architectures and score was only 0.49.
+Based on these results, analyze that our tool try to effectively designed to assess the porting difficulty between two architectures.
+It is not as simple as adding up the modification amounts for different architectures, as it may only reflect an increase in code volume.
+Moreover, Due to the large differences in row\_based statistical results caused by the differences in code structure reflected by each architecture, this approach that easily considers all architectures simultaneously without considering the code structure cannot improve the accuracy of classification results and may lead to ambiguous outcomes.
+Therefore, based on these experiments, we still selected x86 as the architecture to build Arch\_code scan function, utilizing its keywords and critical function dictionary, given its mainstream position.
+
 we form the Arch\_code dictionary:
-\begin{enumerate}
-  \item Conditional compilation and architecture macros are used as preprocessor macros to enable projects to select execution on different hardware architectures, thus demonstrating the additional workload of architecture porting.
-  Use conditional compilation statements, such as ``if defined'', ``ifdef'', in conjunction with all possible architectur macros,
+\textbf{Conditional compilation and architecture macros} Use conditional compilation statements, such as ``if defined'', ``ifdef'', in conjunction with all possible architectur macros,
   ``\_\_x86\_64\_\_''.
   We use a similar bracket matching algorithm to cover all the code within macros, avoiding the impact of nested layers.
-  Additionally, we only collect the keyword dictionary for x86 architecture.
-  This is because different architectures may reflect varying workloads and difficulties, while considering that multiple architectures blurs the classification performance in practical work.
-  \item Assembly code Leverages the advantages of architecture-specific instructions to enhance performance.
-  Considering that architecture changes inevitably require consideration of the assembly section, we use matching forms such as ``\_\_asm\_\_'' and ``\_\_volatile\_\_''.
-  In future work,we will consider striving to achieve the currently unachievable architecture identification function of assembly code and identify assembly code in the form of instructions;In actual work, the assembly code of different architectures may represent different levels of difficulty.
-  For example, the assembly code of ARM is relatively simple.
-  At the same time,there are also situations where some assembly codes only need to serve a specific architecture and do not need to be fully modified when porting to RISC-V.
-  This is why we cannot achieve Fine-grained evaluation,we simply count the number of lines.
-  \item Intrinsic functions are interfaces provided by compilers that are closely related to the architecture.
-  Calling Intrinsic functions can replace assembly code.
-  We compile dictionaries of Intrinsic functions based on official documentation from x86.
+  \textbf{Assembly} We use matching forms such as ``\_\_asm\_\_'' and ``\_\_volatile\_\_''.
+  In future work,we will consider striving to achieve the currently unachievable architecture identification function of assembly code and identify assembly code in the form of instructions;
+  \textbf{Intrinsic and Builtin} 
+  We compile dictionaries of Intrinsic functions based on official documentation from x86\cite{x86intrin}.
   Builtin function also employ a similar approach;In the future,we may assign difficulty weights to them.
-  Currently,we only perform frequency statistics on them.
-  Additionally,we will continue to supplement the analysis of whether the functions already have corresponding implementation for RISC-V and whether they are truly needed in RISC-V.
-  \item System calls are encapsulated by the operating system kernel to provide hardware calling.
-  Considering glibc's support for system call encapsulation, reorganize the sys-call dictionary.
+  \textbf{System calls} Considering glibc's support for system call encapsulation, reorganize the sys-call dictionary.
   The system calls that do not support RISC-V have been filtered out currently.
-  \item In the porting process, adjustment of build scripts is necessary to ensure smooth compilation.
-  We locate architecture keywords in the build scripts.
-  In the future, architecture-related factors will consider even finer-grained classification.
-  For instance,considering the impact of existing porting auxiliary tools, including intrinsic translation tools and assembly translation tools,on porting complexity assessment.
-\end{enumerate}
+  \textbf{Buildscripts} We locate architecture keywords in the build scripts.
 
 \section{Result and analysis}
-
 To answer research question 2, based on the work of Chen Xiang et al.
@@
 Ultimately, we chose to train four models: Random Forest, Support Vector Machine, Adaboost, and Xgboost.
-By comparing multiple indicators, we select the Random Forest machine learning as the classifier.
+By comparing multiple indicators, we select the Random Forest machine learning as the classifier, as shown in Table \ref{tab:evaluation}
 
 \begin{table}
-  \caption{ Experimental results of models}
+  \caption{Experimental results of models}
   \label{tab:evaluation}
@@
 
-We continued to expand 100 projects as a supplementary data set, of which 87 were able to predict correctly.
-The prediction results were determined through comments from the community and forums.
-Appendix presents a comparative assessment of the porting complexity evaluation tool developed by Du Jiman et al.
-across various projects.Through real-world evaluations within the developer community, our tool has exhibited a significant improvement in accuracy, surpassing other comparable tools by a margin of 15.6\%.
+We continued to expand 100 projects as a supplementary data set, and the prediction results were determined through comments from the community and forums.
+Appendix presents a comparative assessment of the porting complexity evaluation tool developed by Du et al.
+across various projects, the comparison results are shown in Table \ref{tab:effectiveness}.Through real-world evaluations within the developer community, our tool has exhibited a significant improvement in accuracy, surpassing other comparable tools by a margin of 15.6\%.
 In the appendix, we provide a comprehensive compilation of the community's valuable feedback comments, accompanied by the relevant web links for further reference and validation.
@@
 \begin{table}
-  \caption{Effectiveness comparison chart}
+  \caption{Tool effectiveness comparison from community feedback}
   \label{tab:effectiveness}
@@
 After adding the code complexity factor and modifying the original tool design model, RAX's result prediction accuracy is improved.
-This is because code complexity can effectively distinguish projects with low porting complexity from projects with medium and high porting complexity.
+This is because code complexity can clearly distinguish three types of porting difficulty
 Motivation Chapters present the cause analysis.
@@
 Chibios,u-boot are facing such a situation.
-Within this assessment, there are instances of inaccurate predictions.
+Another reason is that we have added more medium or difficult complex samples to the data set to increase robustness and improve the innovativeness of the tool.
 
-In-depth analysis of these variations reveals that certain projects exhibit inherent complexity, entailing a substantial presence of architecture-specific code defined by Arch\_code.
+Within this assessment, there are instances of inaccurate predictions.In-depth analysis of these variations reveals that certain projects exhibit inherent complexity, entailing a substantial presence of architecture-specific code defined by Arch\_code.
 Nevertheless, the practical porting process benefits from an array of auxiliary tools designed to support developers.

### 2024-01-29 Paper/latex2/paper.tex
update

@@
 \begin{abstract}
-  In recent years, the RISC-V’s open-source and reduced features have received active promotion of porting from the industry.Due to the lack of publicly available standards for assessing software portability, the software porting process for the RISC-V architecture has been predominantly reliant on expert experience, presenting obstacles.
-This paper introduces an automated tool, RAX, for assessing the porting complexity specifically for RISC-V by considering architecture-specific code and code Cyclomatic Complexity.RAX provides precise evaluation solutions and establishes a high-quality dataset for porting complexity assessment,enabling recommendations of suitable software difficulty levels for developers of varying skill levels.We continue to expand the dataset and conduct effective evaluations of the tool within the open-source community.We have gathered valuable feedback, including 47 positive responses, from 51 specific open-source projects.Interested users can explore the open-source implementation of RAX at (https://github.com/wangyuliu/R
+Recent years, the RISC-V’s open-source and reduced features have received active promotion of porting from the industry.
+Due to the lack of publicly available standards for assessing software portability, the software porting for the RISC-V architecture has been predominantly reliant on expert experience.\textcolor{red}{RAX is a automated tool which aids the C/C++ programmer in evaluating  complexity of projects during porting for RISC-V.
+} This paper introduces an automated tool, RAX, for assessing the porting complexity specifically for RISC-V by considering architecture-specific code and Cyclomatic Complexity.
+RAX provides precise evaluation solutions and establishes a high-quality dataset for porting complexity assessment, enabling recommendations of suitable software difficulty levels for developers of varying skill levels.We continue to expand the dataset and conduct effective evaluations of the tool within the open-source community.We have gathered valuable feedback, including 47 positive responses, from 51 specific open-source projects.Interested users can explore the open-source implementation of RAX at (https://github.com/wangyuliu/R
   AX-2024), or watch the RAX video demo at (https://github.com/wan
   gyuliu/RAX-2024).
+
 \end{abstract}
@@
 \section{Introduction}
-\textcolor{orange}{In recent years, the RISC-V Instruction Set Architecture (ISA) has garnered significant attention from academia, particularly the industry, due to its open-source and reduced design.\citep{2014The}.OpenEuler has joined RISC-V International organization, and RISC-V has officially become openEuler's official support architecture.The mainline integration of openEuler RISC-V 23.09 was finished by the RISC-V SIG.The main repository of openEuler 23.03 has successfully ported 4,244 software packages to the RISCV64,while the openEuler 23.09 main repository has currently completed the porting work of 5,694 software packages\citep{osti_1560132}.OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\citep{osti_1560133}.}
+Recent years, the RISC-V Instruction Set Architecture (ISA) has garnered significant attention from academia, particularly the industry, due to its open-source and reduced design.\citep{2014The}.OpenEuler has joined RISC-V International organization, and RISC-V has officially become openEuler's official support architecture.The mainline integration of openEuler RISC-V 23.09 was finished by the RISC-V SIG.The main repository of openEuler 23.03 has successfully ported 4,244 software packages to the RISCV64,while the openEuler 23.09 main repository has currently completed the porting work of 5,694 software packages\citep{osti_1560132}.OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\citep{osti_1560133}.
 
-\textcolor{orange}{Despite the rapid development of the RISC-V ISA, which foundational software such as operating systems and compilers are relatively mature, there is still a significant demand for porting a large number of application software.\citep{2019Notary}.To adapt to the RISC-V,efficiently porting software package is greatly depending on domain expertise.
-During the initial planning phase of porting, the lack of standardized evaluation criteria for software portability can lead to misallocation of resources in the development process.Therefore, it is desirable to propose a method that automates the assessment of porting complexity,this will enable different development teams to access software packages that are tailored to their proficiency levels, thus assisting distribution vendors in the porting of RISC-V architecture.}
+Despite the rapid development of the RISC-V ISA, which foundational software such as operating systems and compilers are relatively mature, there is still a significant demand for porting a large number of application software.\citep{2019Notary}.To adapt to the RISC-V,efficiently porting software package is greatly depending on domain expertise.
+During the initial planning phase of porting, the lack of standardized evaluation criteria for software portability can lead to misallocation of resources in the development process.Therefore, it is desirable to propose a method that automates the assessment of porting complexity,this will enable different development teams to access software packages that are tailored to their proficiency levels, thus assisting distribution vendors in the porting of RISC-V architecture.
 
-\textcolor{orange}{Du et al.
-have developed a basic statistical evaluation plan for CPU architecture code in project\citep{2023du},however,their work lacks a thorough validity analysis of factors,and fails to consider the complexity associated with the software operation and maintenance process.}
+\textcolor{red}{Many related works focus on the complexity evaluation of C/C++ projects[XXX,XXX,XXX]}.\textcolor{orange}{Du et al.
+have developed a basic statistical evaluation plan for CPU architecture code in project\citep{2023du}.
+However,their work lacks a thorough validity analysis of factors,and \textcolor{red}{ignore important factors such as XXX, even not considering the complexity associated with the software operation and maintenance process.}}
 
-RAX can provide developers with accurate evaluation, recommend software with different levels of porting difficulty based on their skill levels. The contributions of this paper are as follows:
+\textcolor{red}{ To overall these challenges, we propose RAX, a effective porting complexity evaluation tool.
+RAX can help developers to reasonably assignment according to the difficulty of the software packages efficiently.
+} The contributions of this paper are as follows:
 The contributions of this paper are as follows:

### 2024-01-29 Paper/latex2/paper.tex
update

@@
 \usepackage{xcolor}
+\usepackage{bbding}
 
@@
 Based on the analysis of previous evaluation tools, we selected factors with the greatest potential and that can be extracted through automated methods to define Arch\_code.
-Arch\_code includes assembly code, conditional compilation and macro structure, Intrinsic functions, Builtin functions, architecture-related build scripts, and system calls.
+Arch\_code includes assembly code, conditional compilation and macro(ccm) structure, Intrinsic functions, Builtin functions, architecture-related build scripts, and system calls.
 We use an automated architecture binding code scanning tool to obtain statistics on the number of lines and frequencies of Arch\_code.
@@
    \caption{Tool factors comparison}
+   \resizebox{0.5\textwidth}{!}{
   \label{tab:Tool}
@@
     \toprule
-    & Asm & Intrinsic & Builtin & Conditional compilation and macro & Buildscripts & CC \\
+    & Asm & Intrinsic & Builtin & CCM & Buildscripts & CC \\
     \midrule
-    Toolone & 1 & 1 & 1 & 1 & 1 & 0\\
-    RAX & 1 & 1 & 1 & 1 & 1 & 1 \\
+    Toolone & \Checkmark & \Checkmark  & \Checkmark  & \Checkmark  &\Checkmark  & \XSolid\\
+    RAX & \Checkmark  & \Checkmark  & \Checkmark  & \Checkmark  & \Checkmark & \Checkmark  \\
   \bottomrule
 \end{tabular}
+}
 \end{table}

### 2024-01-29 Paper/latex2/paper.tex
Add files via upload

--- 2024-01-26 Paper/latex2/paper.tex
@@
 \usepackage{xcolor}
+\usepackage{hyperref}
 
@@
 \begin{abstract}
-  In recent years, the RISC-V’s open-source and reduced features have received active promotion of porting from the industry.Due to the lack of publicly available standards for assessing software portability, the software porting process for the RISC-V architecture has been predominantly reliant on expert experience, presenting obstacles.
-This paper introduces an automated tool, RAX, for assessing the porting complexity specifically for RISC-V by considering architecture-specific code and code Cyclomatic Complexity.RAX provides precise evaluation solutions and establishes a high-quality dataset for porting complexity assessment,enabling recommendations of suitable software difficulty levels for developers of varying skill levels.We continue to expand the dataset and conduct effective evaluations of the tool within the open-source community.We have gathered valuable feedback, including 47 positive responses, from 51 specific open-source projects.Interested users can explore the open-source implementation of RAX at (https://github.com/wangyuliu/R
-  AX-2024), or watch the RAX video demo at (https://github.com/wan
-  gyuliu/RAX-2024).
+  In recent years, the open-source and reduced features of the RISC-V have led to active promotion of porting within the industry.Due to the lack of publicly available standards for assessing software portability, the software porting process for the RISC-V architecture has been predominantly reliant on expert experience, presenting obstacles.
+RAX is a automated tool which aids the C/C++ programmer in evaluating  complexity of projects during porting for RISC-V.RAX provides precise evaluation solutions and establishes a high-quality dataset for porting complexity assessment,enabling recommendations of suitable software with difficulty levels for developers of varying skill levels.We continue to expand the dataset and conduct effective evaluations of the tool within the open-source community.We have gathered valuable feedback, including 47 positive responses, from 51 specific open-source projects.Interested users can explore the open-source implementation of RAX at \href{https://github.com/wangyuliu/RAX-2024}{https://github.co\\m/wangyuliu/RAX-2024}, or watch the RAX video demo at \href{https://www.youtube.com/watch?v=SLphW3Ra4WM}{https://w\\ww.youtube.com/watch?v=SLphW3Ra4WM}.
 \end{abstract}
@@
 \section{Introduction}
-\textcolor{orange}{In recent years, the RISC-V Instruction Set Architecture (ISA) has garnered significant attention from academia, particularly the industry, due to its open-source and reduced design.\citep{2014The}.OpenEuler has joined RISC-V International organization, and RISC-V has officially become openEuler's official support architecture.The mainline integration of openEuler RISC-V 23.09 was finished by the RISC-V SIG.The main repository of openEuler 23.03 has successfully ported 4,244 software packages to the RISCV64,while the openEuler 23.09 main repository has currently completed the porting work of 5,694 software packages\citep{osti_1560132}.OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\citep{osti_1560133}.}
-
-\textcolor{orange}{Despite the rapid development of the RISC-V ISA, which foundational software such as operating systems and compilers are relatively mature, there is still a significant demand for porting a large number of application software.\citep{2019Notary}.To adapt to the RISC-V,efficiently porting software package is greatly depending on domain expertise.
-During the initial planning phase of porting, the lack of standardized evaluation criteria for software portability can lead to misallocation of resources in the development process.Therefore, it is desirable to propose a method that automates the assessment of porting complexity,this will enable different development teams to access software packages that are tailored to their proficiency levels, thus assisting distribution vendors in the porting of RISC-V architecture.}
-
-\textcolor{orange}{Du et al.
-have developed a basic statistical evaluation plan for CPU architecture code in project\citep{2023du},however,their work lacks a thorough validity analysis of factors,and fails to consider the complexity associated with the software operation and maintenance process.}
-
-RAX can provide developers with accurate evaluation, recommend software with different levels of porting difficulty based on their skill levels. The contributions of this paper are as follows:
-The contributions of this paper are as follows:
+\textcolor{black}{In recent years, the RISC-V Instruction Set Architecture (ISA) has garnered significant attention from academia, and particularly the industry, due to its open-source and reduced design\citep{2014The}.OpenEuler has joined RISC-V International organization, and RISC-V has officially become openEuler's official support architecture.The mainline integration of openEuler RISC-V 23.09 was finished by the RISC-V SIG.The main repository of openEuler 23.03 has successfully ported 4,244 software packages to the RISCV64,while the openEuler 23.09 main repository has currently completed the porting work of 5,694 software packages\citep{osti_1560132}.OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\citep{osti_1560133}.
+   Despite the rapid development of the RISC-V ISA, which foundational software such as operating systems and compilers are relatively mature, there is still a significant demand for porting a large number of application software\citep{2019Notary}.To adapt to the RISC-V,efficiently porting is greatly depending on domain expertise, and the lack of standardized evaluation criteria for software portability can lead to misallocation of resources.Therefore, it is desirable to propose a method that automates the assessment of porting complexity,this will enable different development teams to access software packages that are tailored to their proficiency levels, thus assisting distribution vendors in the porting of RISC-V architecture.
+Many related works focus on the code complexity and portability evaluation\cite{2016helei},\cite{TAHIR2016101},\cite{Sholiq_2021}.Du et al.
+have developed a basic statistical evaluation plan for CPU architecture code\citep{2023du},however,their work lacks a thorough validity analysis of factors,and fails to consider the complexity factors associated with the software operation and maintenance process.}
+To overall these challenges, we propose RAX, a effective porting
+complexity evaluation tool.The contributions of this paper are as follows:
 \begin{enumerate}
-  \item In recent years, the RISC-V’s open-source and reduced features have received active promotion of porting from the industry.
-  \item Optimization Assessment Tool.Tuning machine learning models to address ambiguous identification of samples of medium and hard complexity.
-  \item We nearly doubled the dataset compared to other tool,and verified the effectiveness of the evaluation of 51 extension projects in real porting scenarios through their respective communities or forums.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of performance and accuracy.
+  \item Discover new factors. Investigate the role of Cyclomatic Complexity in porting scenarios.
+  \item We explore building high-quality datasets that can cover various porting scenarios to solve the problem of imbalanced datasets of existing tools.Tuning machine learning models to address ambiguous identification of samples of medium and hard complexity compared to other studies.
+  \item We nearly doubled the dataset compared to other tool,and verified the effectiveness of the evaluation of 51 extension projects in real porting scenarios through their respective communities or forums.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
 \end{enumerate}
@@
 
-\textbf{RQ 1:} How can we select architecture-relevant actors that is fine-grained to design an automated tool that assesses the porting difficulty?
+\textbf{RQ 1:} How can we select architecture-relevant actors that is fine-grained to design an automated assessment tool of porting complexity?
 
-\textbf{RQ 2:} How to select a classifier to obtain effective classification results for the tool?
-
-To answer research question 1,this section provides a validity analysis of porting-related factors on RAX.
-First,we try to use code complexity metrics to evaluate porting work.
-The software metrics of code Cyclomatic Complexity(CC) can help developers make macro judgments on software complexity and maintenance difficulty, evaluate potential and hidden porting difficulties,which help the tool improve accuracy \cite{2005Exploring}.
-At present, CC indicators are mostly used in project code quality assessment, defect inspection, code reconstruction, etc \cite{1991Cyclomatic}.
-During the porting process, developers will target a large number of project source codes,build scripts,assembly codes,and a macro understanding of the project is required in the early stage of porting.
-This part of the work has a lot of overlap with the scope of code complexity.Through our survey of community, we have discovered that even though architectural code can be separated quite clearly from common code, when faced with complex and large-scale projects, we still require numerous iterative tests to uncover unknown architectural code.
-Building upon this, we delve into the quantification of the significance of cyclomatic complexity in porting work.
-
-\subsubsection{Factor 1: Cyclomatic Complex(CC)}
-\label{sec:factor-1}
-We uses the lizard CC detection tool and optimize its functions,and it will introduce it in Section \ref{sec:method}.
-This study analyzes the relationship between CC and software porting complexity using the Spearman Rank correlation coefficient analysis method.
-We invited five Master's students who are engaged in research on porting auxiliary tools to score the porting complexity(score) of 131 software adapted for RISC-V,collected from the OpenEule list\citep{stage2023} and GitHub.
-According to the collection of Internet events, log analysis, source code dismantling, and similar project analogy \cite{liangguanyu2020}, we form a scoring interval in the range of $[0~5]$.
-The Spearman coefficient of CC and score is 0.608, with a P-value of 1.39e-14, which is less than 0.01.
-The results suggest that CC has a moderate positive correlation with porting difficulty.
-This is because developers need a holistic understanding of the project during the porting process, and CC can represent the overall complexity of the project, potentially reflecting porting barriers, as shown in Figure \ref{fig:figure2}.
-
-Second, we consider the effectiveness of the architecture binding code structure proposed by the other tool and conduct comparative experiments using more potential factors.
+\textbf{RQ 2:} How to solve the problem of vague classification of projects with medium and high porting complexity in existing tools?
 \begin{figure}
@@
 \end{figure}
+
+To answer RQ 1,this section provides a validity analysis of porting-related factors on RAX.
+First,we try to use code complexity metrics to evaluate porting work.
+The software metrics of code Cyclomatic Complexity(CC) can help developers make macro judgments on software complexity and maintenance difficulty, evaluate potential and hidden porting difficulties,which help the tool improve accuracy \cite{2005Exploring}.
+At present, CC indicators are mostly used in project code quality assessment, defect inspection, code reconstruction, etc \cite{1991Cyclomatic}.
+During the porting process, developers will target a large number of project source codes,build scripts,assembly codes,and a macro understanding of the project is required in the early stage of porting.
+This part of the work has a lot of overlap with the scope of code complexity.Through our survey of community, we discovered that even though architectural code can be separated quite clearly from common code, when faced with large-scale projects, we still require numerous iterative tests to uncover unknown architectural code.
+Building upon this, we delve into the quantification of the significance of cyclomatic complexity in porting work.
+\subsubsection{Factor 1: Cyclomatic Complex(CC)}
+\label{sec:factor-1}
+We uses the lizard CC detection tool and optimize its functions,and it will introduce it in Section \ref{sec:method}.
+This study analyzes the relationship between CC and software porting complexity using the Spearman Rank correlation coefficient analysis method.
+We invited five Master's students who are engaged in research on porting auxiliary tools to score the porting complexity(score) of 131 software adapted for RISC-V,collected from the OpenEuler list\citep{stage2023} and GitHub.
+According to the collection of Internet events, log analysis, source code dismantling, and similar project analogy \cite{liangguanyu2020}, we form a scoring interval in the range of $[0,5]$.
+The Spearman coefficient of CC and score is 0.608, with a P-value of 1.39e-14, which is less than 0.01.
+The results suggest that CC has a moderate positive correlation with porting difficulty.
+This is because developers need a holistic understanding of the project during the porting process, and CC can represent the overall complexity of the project, potentially reflecting porting barriers, the relationship of factors shown in Figure \ref{fig:figure2}.
+
+Second, we consider the effectiveness of the architecture binding code structure proposed by the other tool and conduct comparative experiments using more potential factors.
 \subsubsection{Factor2:Arch\_code}
 
-Based on the analysis of previous evaluation tools, we selected factors with the greatest potential and that can be extracted through automated methods to define Arch\_code.
-Arch\_code includes assembly code, conditional compilation and macro structure, Intrinsic functions, Builtin functions, architecture-related build scripts, and system calls.
-We use an automated architecture binding code scanning tool to obtain statistics on the number of lines and frequencies of Arch\_code.
+We select factors with the greatest potential from existing tool and define Arch\_code.
+Arch\_code includes assembly code, conditional compilation and macro structure(CCM), Intrinsic functions, Builtin functions, architecture-related build scripts, and system calls.
+We use an automated tool to obtain statistics of lines and frequencies of Arch\_code.
 
-Continue to collect other factors that may affect the evaluation of porting complexity,and select the following parameters through the Commit analyzer:architecture-related code lines, architecture-related files, and architecture keywords.
-The number of architecture-related code lines and files is located using the keywords of X86, ARM, MIPS, RISCV, SPARC and other architectures.
-%Correlation comparison between Arch\_code and other factors acquired by Commit analyzer,as shown in Table \ref{tab:score}:
+Continue to collect other factors that may reflect the porting complexity,and select the following parameters through the Commit analyzer:architecture-related code lines, architecture-related files, and architecture keywords.architecture-related code lines and files is located using the keywords of the RISC-V architecture, such as riscv, rv32, rv64, RISC-V, RISCV and so on.
+%Correlation comparison between Arch\_code and other factors acquired by Commit analyzer,as shown in Table \ref{tab:Tool}:
 
@@
 %\end{table}
-Correlation comparison between Arch\_code and other factors acquired by Commit analyzer,as shown in Figure \ref{fig:figure3}:
+
+\begin{table*}
+  \caption{Tool factors comparison}
+  \label{tab:Tool}
+  \begin{tabular}{ccccccccc}
+    \toprule
+    & Full Assembly & Inline Assembly & Intrinsic & Builtin & System Call & CCM & Buildscripts & CC \\
+    \midrule
+    Other tool & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \\
+    RAX & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\
+  \bottomrule
+\end{tabular}
+\end{table*}
+
+Correlation comparison between Arch\_code,CC and other factors acquired by Commit analyzer,as shown in Figure \ref{fig:figure3}:
 \begin{figure}
@@
 \end{figure}
-The results indicate that Arch\_code has a higher correlation with score compared to other factors, and it also aligns with the significant results of the Peason correlation test.
-The use of only architecture keywords for statistics yields moderate effectiveness in evaluating tool because keywords can only be detected from comments and macro sections of Commit, while critical porting code may lack these keywords,but the keyword count can reflect the amount of porting modification from the side.
-As shown in the figure 2,the parameters of Arch\_code show a correlation of 0.45 to 0.75 with score, indicating a strong relationship.
+The results indicate that Arch\_code and CC has a higher correlation with score compared to other factors, and we use Peason correlation method to build heat map.
+The use of only architecture keywords for statistics yields moderate effectiveness because keywords can only be detected from comments and macro sections of Commit, while critical porting code may lack these keywords,but the keyword count can reflect the amount of porting modification from the side.
+Arch\_code show a correlation of 0.45 to 0.75 with score, indicating a strong relationship.
 However, using a single factor alone does not result in a significantly strong correlation, as the combined modifications of these factors make up the porting workload.
 
-In the end,our tool selection was CC and the Arch\_code build scanning tool,as shown table 1.
+In the end,our tool selection was CC and the Arch\_code build scanning tool,as shown in Table \ref{tab:Tool}.
 
@@
 \subsection{Dataset}
-We used the project upstream warehouse to build the data set,that projects mainly targeting C and C++ are from the OpenEuler\citep{stage2023} list and GitHub,and invited 5 postgraduate students who are engaged in the research of RISC-V porting auxiliary tools to participate in the experimental evaluation.Specific evaluation methods can be found in 2.1.1.
-The evaluation scores are divided into three categories: low, medium, and high\citep{githuburl}.This includes 139 projects as training, testing, and validation datasets, while more than 80 additional projects were used as a tool evaluation dataset.
+We used the project upstream warehouse to build the data set,that projects mainly targeting C and C++ are from the OpenEuler list and GitHub,and invited 5 postgraduate students who are engaged in the research of RISC-V porting auxiliary tools to participate in the experimental evaluation.Specific evaluation methods can be found in \ref{sec:factor-1}.
+The evaluation scores are divided into three categories: low, medium, and high\citep{githuburl}.This includes 139 projects as training, testing, and validation datasets, while more than 80 additional projects were used as a tool effectiveness evaluation dataset.
 To gather insights from developers, the community, forums, and emails were utilized, resulting in over 51 meaningful feedback responses.
 In order to address the issue of data imbalance caused by collecting datasets solely from the openEuler mailing list, where more than 80\% of the projects were initially evaluated as having low porting complexity, a greater emphasis was placed on projects that had higher numbers of likes on GitHub and were deemed more important and active.
-Additionally, efforts were made to collect projects from the bottom such as operating systems, kernel-level projects,mathematical computation libraries,and machine learning libraries.
+Additionally, efforts were made to collect projects from the system bottom such as operating systems, kernel-level projects,mathematical computation libraries,and machine learning libraries to address RQ 2.
 
@@
 \label{sec:method}
-The RAX combines the CC calculation module and the Arch\_code location module to obtain the porting vector,and the complexity vector and score together form the data set.
+RAX obtains porting complexity vector through the CC calculation method and Arch\_code statistical value.
 
@@
 Lizard's default computing method is basically consistent with McCabe's theory \cite{1702388}.
-However, Lizard tool only detects defects at the function level and uses the average function CC for file-level statistics, which is not suitable for current porting complexity detection requirements \cite{9402593}.
-This paper proposes a new method for evaluating CC specifically for porting assessment work:
-\begin{enumerate}
-  \item First, calculate the function-level CC for all files in the project using McCabe's method.
-  \item Following Liu's mention of System Cyclomatic Complexity (SCC) in software evolution assessment techniques based on code change detection \cite{liuhuihui00}, we define SCC as the total sum of function-level values in the system.
+However, Lizard tool only defects at the function level and uses the average function CC for file-level statistics, which is not suitable for current porting complexity detection requirements \cite{9402593}.
+This paper proposes a new method:
+
+First, calculate the function-level CC for all files in the project using McCabe's method.Following Liu's mention of System Cyclomatic Complexity (SCC) in software evolution assessment techniques based on code change detection \cite{liuhuihui00}, we define SCC as the total sum of function-level values in the system.
   The advantage is that it can avoid the use of overly complex methods, which will cause deviations to affect the classification results.
   Additionally,due to the system's complexity being calculated based on a single function,it eliminates the problem of decreased detection performance caused by the conversion of such a large code structure of all modules into into syntax abstract trees and control flow graphs.
-\end{enumerate}
+  Our CC calculation approach is expressed by the following equation,where lowercase cc represents the cyclomatic complexity at the function or file level.The uppercase CC represents the overall cyclomatic complexity of the software package,serving as a crucial factor in our tool.Here, |E| denotes the number of edges in the function control flow graph,and |N| represents the number of nodes.The function control flow graph is constructed based on branching structures such as if, while, and switch statements.
 
-\subsubsection{Arch\_code location module}
+  \begin{equation}
+    \mathrm{cc}(\mathrm{function}) = \lvert E \rvert - \lvert N \rvert + 2
+    % \sum_{i=1}^{n} x_i
+    \end{equation}
+    \begin{equation}
+      \mathrm{cc}(\mathrm{file}) =  \sum_{i=1}^{n} \mathrm{cc}(\mathrm{function})
+      \end{equation}
+      \begin{equation}
+        \mathrm{CC} =  \sum_{i=1}^{k} \mathrm{cc}(\mathrm{file})
+        \end{equation}
+
+\subsubsection{Arch\_code scan function}
+Other tools only consider x86 architecture to locate architecture-related code for statistical analysis.
+We propose a new idea that explore whether multiple architectures can be selected or if other architectures can be individually targeted.
+Based on this, we conducted comparative experiments using various architectures, including X86, ARM, MIPS, RISCV, SPARC, and PowerPC.
+We performed scanning and counting based on the keyword and function dictionaries specific to each architecture, which were derived from common patterns summarized from official websites.
+By analyzing the correlation coefficient (Pearson's) between the keyword coverage line statistics of the six architectures and the score representing the porting complexity, we found that the correlation ranged from 0.44 to 0.58, indicating an average correlation across all architectures.
+Additionally, the correlation between the total values for all architectures and score was only 0.49.
+Based on these results, analyze that our tool try to effectively assess the porting difficulty between two architectures.
+It is not as simple as adding up the modification amounts for different architectures, as it may only reflect an increase in code volume.
+Moreover, due to the large differences in row\_based statistical results caused by the differences in code structure reflected by each architecture, this approach that easily considers all architectures simultaneously without considering the code structure and architectural weight lead to ambiguous outcomes.Therefore, based on these experiments, we still select x86 to build Arch\_code scan function, given its mainstream position.
+
 we form the Arch\_code dictionary:
-\begin{enumerate}
-  \item Conditional compilation and architecture macros are used as preprocessor macros to enable projects to select execution on different hardware architectures, thus demonstrating the additional workload of architecture porting.
-  Use conditional compilation statements, such as ``if defined'', ``ifdef'', in conjunction with all possible architectur macros,
+\textbf{Conditional compilation and architecture macros} Use conditional compilation statements, such as ``if defined'', ``ifdef'', in conjunction with all possible architecture macros,
   ``\_\_x86\_64\_\_''.
-  We use a similar bracket matching algorithm to cover all the code within macros, avoiding the impact of nested layers.
-  Additionally, we only collect the keyword dictionary for x86 architecture.
-  This is because different architectures may reflect varying workloads and difficulties, while considering that multiple architectures blurs the classification performance in practical work.
-  \item Assembly code Leverages the advantages of architecture-specific instructions to enhance performance.
-  Considering that architecture changes inevitably require consideration of the assembly section, we use matching forms such as ``\_\_asm\_\_'' and ``\_\_volatile\_\_''.
-  In future work,we will consider striving to achieve the currently unachievable architecture identification function of assembly code and identify assembly code in the form of instructions;In actual work, the assembly code of different architectures may represent different levels of difficulty.
-  For example, the assembly code of ARM is relatively simple.
-  At the same time,there are also situations where some assembly codes only need to serve a specific architecture and do not need to be fully modified when porting to RISC-V.
-  This is why we cannot achieve Fine-grained evaluation,we simply count the number of lines.
-  \item Intrinsic functions are interfaces provided by compilers that are closely related to the architecture.
-  Calling Intrinsic functions can replace assembly code.
-  We compile dictionaries of Intrinsic functions based on official documentation from x86.
+  We use an algorithm similar to bracket matching to cover all the code within macros, avoiding the impact of nested layers.
+  \textbf{Assembly} We use matching forms such as ``\_\_asm\_\_'' and ``\_\_volatile\_\_''.
+  In future work,we will consider striving to achieve the currently unachievable architecture identification function of assembly code and identify assembly code in the form of instructions;
+  \textbf{Intrinsic and Builtin} 
+  We compile dictionaries of Intrinsic functions based on official documentation from x86\cite{x86intrin}.
   Builtin function also employ a similar approach;In the future,we may assign difficulty weights to them.
-  Currently,we only perform frequency statistics on them.
-  Additionally,we will continue to supplement the analysis of whether the functions already have corresponding implementation for RISC-V and whether they are truly needed in RISC-V.
-  \item System calls are encapsulated by the operating system kernel to provide hardware calling.
-  Considering glibc's support for system call encapsulation, reorganize the sys-call dictionary.
-  The system calls that do not support RISC-V have been filtered out currently.
-  \item In the porting process, adjustment of build scripts is necessary to ensure smooth compilation.
-  We locate architecture keywords in the build scripts.
-  In the future, architecture-related factors will consider even finer-grained classification.
-  For instance,considering the impact of existing porting auxiliary tools, including intrinsic translation tools and assembly translation tools,on porting complexity assessment.
-\end{enumerate}
+  \textbf{System calls} Considering glibc's support for system call encapsulation, reorganize the sys-call dictionary.
+  The system calls that do not support RISC-V have been filtered and collected currently.
+  \textbf{Buildscripts} We locate architecture keywords in the build scripts.
 
 \section{Result and analysis}
-
-To answer research question 2, based on the work of Chen Xiang et al.
+To answer RQ 2, based on the work of Chen Xiang et al.
 \cite{5128907}, aiming at the status quo of unbalanced datasets and small sample datasets, we try to use ensemble learning methods \cite{6509481}, SMOTE \cite{4271036}, and random oversampling methods for data preprocessing.
 Ultimately, we chose to train four models: Random Forest, Support Vector Machine, Adaboost, and Xgboost.
-By comparing multiple indicators, we select the Random Forest machine learning as the classifier.
+By comparing multiple indicators, we select the Random Forest machine learning as the classifier, as shown in Table \ref{tab:evaluation}.
 
 \begin{table}
-  \caption{ Experimental results of models}
+  \caption{Experimental results of models}
   \label{tab:evaluation}
@@
 
-We continued to expand 100 projects as a supplementary data set, of which 87 were able to predict correctly.
-The prediction results were determined through comments from the community and forums.
-Appendix presents a comparative assessment of the porting complexity evaluation tool developed by Du Jiman et al.
-across various projects.Through real-world evaluations within the developer community, our tool has exhibited a significant improvement in accuracy, surpassing other comparable tools by a margin of 15.6\%.
-In the appendix, we provide a comprehensive compilation of the community's valuable feedback comments, accompanied by the relevant web links for further reference and validation.
+We continued to expand 100 projects as a supplementary data set, and the prediction results were determined through comments from the community and forum.
+Github presents comparison\cite{githubss} with the porting complexity evaluation tool developed by Du et al.
+across various projects, the comparison results are shown in Table \ref{tab:effectiveness}.Through real-world evaluations within the developer community, our tool has exhibited a significant improvement in accuracy, surpassing other comparable tools by a margin of 15.6\%.
+In Github, we provide a comprehensive compilation of the community's valuable feedback comments, accompanied by the relevant web links for further reference and validation.
 
 \begin{table}
-  \caption{Effectiveness comparison chart}
+  \caption{Tool effectiveness comparison from community feedback}
   \label{tab:effectiveness}
@@
 
-After adding the code complexity factor and modifying the original tool design model, RAX's result prediction accuracy is improved.
-This is because code complexity can effectively distinguish projects with low porting complexity from projects with medium and high porting complexity.
+After adding the code complexity factor and modifying the original model, RAX's result prediction accuracy is improved.
+This is because code complexity can clearly distinguish three types of porting difficulty.
 Motivation Chapters present the cause analysis.
@@
 Chibios,u-boot are facing such a situation.
-Within this assessment, there are instances of inaccurate predictions.
+Another reason is that we have added more medium or difficult complex samples to the data set to increase robustness and improve the innovativeness of the tool.
 
-In-depth analysis of these variations reveals that certain projects exhibit inherent complexity, entailing a substantial presence of architecture-specific code defined by Arch\_code.
+Within assessment, there are instances of inaccurate predictions.
+Analysis of some variations reveals that certain projects exhibit inherent complexity, entailing a substantial presence of architecture-specific code defined by Arch\_code.
 Nevertheless, the practical porting process benefits from an array of auxiliary tools designed to support developers.
-In response to valuable suggestions from developers within the OpenEuler community, we conducted an evaluation of the porting difficulty for various versions of the Chromium.Initially, we were able to accurately assess the porting difficulty, yielding promising results.
-However, when it came to evaluating the work involved in iterative updates between versions, existing tools proved insufficient for precise estimation.Sometimes developers design their work has generic code for unknown architecture and CPU architecture parts are well separated from the common code,that just need only to adjust the macro to recognize RISC-V,like nuttx.
+In response to valuable suggestions from developers within the OpenEuler community, we conducted an evaluation of the porting complexity for various versions of the Chromium.Initially, we were able to accurately assess the porting complexity, yielding promising results.
+However, when it came to evaluating the work involved in iterative updates between versions, existing tools proved insufficient for precise estimation.Sometimes developers design their work with generic code for unknown architecture and CPU architecture parts are well separated from the common code,that just need only to adjust the moderate amount of code to recognize RISC-V,like nuttx.
 \section{Related Work}
@@
 \cite{osti_1830102} accomplished the porting of the OpenCL framework to RISC-V through a compiler framework, thereby expanding RISC-V's accessibility to a wider range of scientific computing applications.
-In the context of architectural migration of foundational software and libraries, Cheng Yuanhu et al.
+In the context of architectural porting of foundational software and libraries, Cheng Yuanhu et al.
 \cite{2017Slow} designed an embedded multi-instruction set processor,addressing the software ecosystem challenges present in the RISC-V embedded domain.
-As a result, auxiliary efforts in porting are highlighted as valuable endeavors.
-This tool approaches code complexity from the perspective of its evaluation role in software evolution and maintenance,considering its influence on porting complexity assessment \cite{1993Software}.
+Therefore, auxiliary efforts in porting are highlighted as valuable endeavors.
+Our work consider code complexity from the perspective of its evaluation role in software evolution and maintenance,considering its influence on porting complexity assessment \cite{1993Software}.
 Alvares et al. \cite{7844689} proposed using the development team's ``tolerance'' for code complexity to infer team development capabilities and performance indicators for projects.
-Vard et al. \cite{2017Evaluating} emphasized that the internal quality of software impacts developers' capabilities and maintenance durations.
+Vard et al. \cite{2017Evaluating} emphasized that the internal quality of software impacts developers' capabilities and maintenance duration.
 They conducted a comprehensive study on various existing code complexity metrics' validity and suggested incorporating empirically observed code features as complexity triggers.
@@
 We verified the effectiveness of the evaluation of 51 extension projects in real porting scenarios through their respective communities or forums.
-Observed significant performance improvements compared to previous tools.Moreover, RAX provides developers with the functionality to locate target code segments.Our next steps involve attempting text classification methods to categorize the text results of the scanning tool, designing more granular statistical methods for architecture-related factors.
+Observed significant performance improvements compared to existing tools.Moreover, RAX provides developers with the functionality to locate target code segments.Our next steps involve attempting text classification methods to categorize the text results of the original tool, designing more granular statistical methods for architecture-related factors.
 %%

### 2024-01-29 Paper/latex2/paper.tex
Add files via upload

@@
   In recent years, the open-source and reduced features of the RISC-V have led to active promotion of porting within the industry.Due to the lack of publicly available standards for assessing software portability, the software porting process for the RISC-V architecture has been predominantly reliant on expert experience, presenting obstacles.
-RAX is a automated tool which aids the C/C++ programmer in evaluating  complexity of projects during porting for RISC-V.RAX provides precise evaluation solutions and establishes a high-quality dataset for porting complexity assessment,enabling recommendations of suitable software with difficulty levels for developers of varying skill levels.We continue to expand the dataset and conduct effective evaluations of the tool within the open-source community.We have gathered valuable feedback, including 47 positive responses, from 51 specific open-source projects.Interested users can explore the open-source implementation of RAX at \href{https://github.com/wangyuliu/RAX-2024}{https://github.co\\m/wangyuliu/RAX-2024}, or watch the RAX video demo at \href{https://www.youtube.com/watch?v=SLphW3Ra4WM}{https://w\\ww.youtube.com/watch?v=SLphW3Ra4WM}.
+RAX is a automated tool which aids the C/C++ programmer in evaluating  complexity of projects during porting for RISC-V.RAX provides precise evaluation solutions and establishes a high-quality dataset for porting complexity assessment,enabling recommendations of suitable software with difficulty levels for developers of varying skill levels.We evaluate RAX on 72 popular and typical real-world C/C++ projects.
+The experimental result shows that 51 of them have been confirmed by developers within community.Interested users can explore the open-source implementation of RAX at \href{https://github.com/wangyuliu/RAX-2024}{https://github.com/wangyuliu/RAX-2024}, or watch the RAX video demo at \href{https://www.youtube.com/watch?v=SLphW3Ra4WM}{https://www.youtube.com/watch?v=SLphW3Ra4WM}.
 \end{abstract}
@@
 \begin{enumerate}
-  \item Discover new factors. Investigate the role of Cyclomatic Complexity in porting scenarios.
-  \item We explore building high-quality datasets that can cover various porting scenarios to solve the problem of imbalanced datasets of existing tools.Tuning machine learning models to address ambiguous identification of samples of medium and hard complexity compared to other studies.
-  \item We nearly doubled the dataset compared to other tool,and verified the effectiveness of the evaluation of 51 extension projects in real porting scenarios through their respective communities or forums.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
+  \item Identify the factor of Cyclomatic Complexity(CC) and investigate its value in porting scenarios.
+  % \item We explore building high-quality datasets that can cover various porting scenarios to solve the problem of imbalanced datasets of existing tools.Tuning machine learning models to address ambiguous identification of samples of medium and hard complexity compared to other studies.
+  \item Construct a model to assess the complexity of software porting and implement automated RAX.
+  % \item We nearly doubled the dataset compared to other tool,and verified the effectiveness of the evaluation of 51 extension projects in real porting scenarios through their respective communities or forums.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
+  \item Verify the effectiveness of RAX in real scenarios.We sent out 72 assessment inquiries to the developer community and received 51 valuable feedback responses, out of which 47 confirmed the accurate predictions made by RAX for their respective projects.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
 \end{enumerate}
@@
 
-We continued to expand 100 projects as a supplementary data set, and the prediction results were determined through comments from the community and forum.
+We continued to expand 72 projects as a supplementary data set, and the prediction results were determined through comments from the community and forum.
 Github presents comparison\cite{githubss} with the porting complexity evaluation tool developed by Du et al.

### 2024-01-29 Paper/latex2/paper.tex
Add files via upload

@@
 \section{Introduction}
-\textcolor{black}{In recent years, the RISC-V Instruction Set Architecture (ISA) has garnered significant attention from academia, and particularly the industry, due to its open-source and reduced design\citep{2014The}.OpenEuler has joined RISC-V International organization, and RISC-V has officially become openEuler's official support architecture.The mainline integration of openEuler RISC-V 23.09 was finished by the RISC-V SIG.The main repository of openEuler 23.03 has successfully ported 4,244 software packages to the RISCV64,while the openEuler 23.09 main repository has currently completed the porting work of 5,694 software packages\citep{osti_1560132}.OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\citep{osti_1560133}.
+In recent years, the RISC-V Instruction Set Architecture (ISA) has garnered significant attention from academia, and particularly the industry, due to its open-source and reduced design\citep{2014The}.OpenEuler has joined RISC-V International organization, and RISC-V has officially become openEuler's official support architecture.The mainline integration of openEuler RISC-V 23.09 was finished by the RISC-V SIG.The main repository of openEuler 23.03 has successfully ported 4,244 software packages to the RISCV64,while the openEuler 23.09 main repository has currently completed the porting work of 5,694 software packages\citep{osti_1560132}.OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\citep{osti_1560133}.
+
 Despite the rapid development of the RISC-V ISA, which foundational software such as operating systems and compilers are relatively mature, there is still a significant demand for porting a large number of application software\citep{2019Notary}.To adapt to the RISC-V,efficiently porting is greatly depending on domain expertise, and the lack of standardized evaluation criteria for software portability can lead to misallocation of resources.Therefore, it is desirable to propose a method that automates the assessment of porting complexity,this will enable different development teams to access software packages that are tailored to their proficiency levels, thus assisting distribution vendors in the porting of RISC-V architecture.
+
 Many related works focus on the code complexity and portability evaluation\cite{2016helei},\cite{TAHIR2016101},\cite{Sholiq_2021}.Du et al.
-have developed a basic statistical evaluation plan for CPU architecture code\citep{2023du},however,their work lacks a thorough validity analysis of factors,and fails to consider the complexity factors associated with the software operation and maintenance process.}
+have developed a basic statistical evaluation plan for CPU architecture code\citep{2023du},however,their work lacks a thorough validity analysis of factors,and fails to consider the complexity factors associated with the software operation and maintenance process.
 To overall these challenges, we propose RAX, a effective porting
@@
 \begin{enumerate}
-  \item Identify the factor of Cyclomatic Complexity(CC) and investigate its value in porting scenarios.
+  \item Identify one of the most important factors,Cyclomatic Complexity(CC), and investigate its significant value in porting scenarios.
   % \item We explore building high-quality datasets that can cover various porting scenarios to solve the problem of imbalanced datasets of existing tools.Tuning machine learning models to address ambiguous identification of samples of medium and hard complexity compared to other studies.
-  \item Construct a model to assess the complexity of software porting and implement automated RAX.
+  \item We propose RAX, an automated tool to efficiently assess the complexity of software during porting to the RISC-V.
   % \item We nearly doubled the dataset compared to other tool,and verified the effectiveness of the evaluation of 51 extension projects in real porting scenarios through their respective communities or forums.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
-  \item Verify the effectiveness of RAX in real scenarios.We sent out 72 assessment inquiries to the developer community and received 51 valuable feedback responses, out of which 47 confirmed the accurate predictions made by RAX for their respective projects.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
+  \item Verify the effectiveness of RAX in real scenarios concentrating C/C++ projects. Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
 \end{enumerate}
 
-\section{RAX}
-The following is an introduction to the process of RAX construction, as shown in Figure \ref{fig:figure1}.
-During the analysis phase,architecture-related factors are obtained through the Commit tool for selection while investigating the impact of code complexity metrics on porting.
-A scanning tool is built to get potential modification workload.
-Finally,an appropriate machine learning model is selected as a classification.
+The remainder of this paper is organized as follows.
+Section2 analyze architecture-related factors briefly.
+Section 3 presents the implementation and evaluation of RAX.
+Section 4 and 5 presents related work and conclusions.
+
+% \section{RAX}
+% The following is an introduction to the process of RAX construction, as shown in Figure \ref{fig:figure1}.
+% During the analysis phase,architecture-related factors are obtained through the Commit tool for selection while investigating the impact of code complexity metrics on porting.
+% A scanning tool is built to get potential modification workload.
+% Finally,an appropriate machine learning model is selected as a classification.
 \begin{figure}
@@
 \end{figure}
-\subsection{Motivation}
+\section{Motivation}
 To design RAX that assists developers with porting work,the following research questions are proposed:
@@
 Building upon this, we delve into the quantification of the significance of cyclomatic complexity in porting work.
-\subsubsection{Factor 1: Cyclomatic Complex(CC)}
+\subsection{Factor 1: Cyclomatic Complex(CC)}
 \label{sec:factor-1}
-We uses the lizard CC detection tool and optimize its functions,and it will introduce it in Section \ref{sec:method}.
+We uses the lizard CC detection tool and optimize its functions,and it will introduce it in Section \ref{sec:Implementation}.
 This study analyzes the relationship between CC and software porting complexity using the Spearman Rank correlation coefficient analysis method.
@@
 Second, we consider the effectiveness of the architecture binding code structure proposed by the other tool and conduct comparative experiments using more potential factors.
-\subsubsection{Factor2:Arch\_code}
+\subsection{Factor2:Arch\_code}
 
@@
 
-\subsection{Dataset}
-We used the project upstream warehouse to build the data set,that projects mainly targeting C and C++ are from the OpenEuler list and GitHub,and invited 5 postgraduate students who are engaged in the research of RISC-V porting auxiliary tools to participate in the experimental evaluation.Specific evaluation methods can be found in \ref{sec:factor-1}.
+\section{RAX}
+The following is an introduction to the process of RAX construction, as shown in Figure \ref{fig:figure1}.
+During the analysis phase,architecture-related factors are obtained through the Commit tool for selection while investigating the impact of code complexity metrics on porting.
+A scanning tool is built to get potential modification workload.
+Finally,an appropriate machine learning model is selected as a classification.
+
+% \subsection{Dataset}
+% We used the project upstream warehouse to build the data set,that projects mainly targeting C and C++ are from the OpenEuler list and GitHub,and invited 5 postgraduate students who are engaged in the research of RISC-V porting auxiliary tools to participate in the experimental evaluation.Specific evaluation methods can be found in \ref{sec:factor-1}.
 The evaluation scores are divided into three categories: low, medium, and high\citep{githuburl}.This includes 139 projects as training, testing, and validation datasets, while more than 80 additional projects were used as a tool effectiveness evaluation dataset.
@@
 
-\subsection{Method}
-\label{sec:method}
+\subsection{Implementation}
+\label{sec:Implementation}
 RAX obtains porting complexity vector through the CC calculation method and Arch\_code statistical value.
@@
 
-\section{Result and analysis}
+\subsection{Evaluation}
+\subsubsection{Dataset}
+We used the project upstream warehouse to build the data set,that projects mainly targeting C and C++ are from the OpenEuler list and GitHub,and invited 5 postgraduate students who are engaged in the research of RISC-V porting auxiliary tools to participate in the experimental evaluation.Specific evaluation methods can be found in \ref{sec:factor-1}.
+The evaluation scores are divided into three categories: low, medium, and high\citep{githuburl}.This includes 139 projects as training, testing, and validation datasets, while more than 80 additional projects were used as a tool effectiveness evaluation dataset.
+To gather insights from developers, the community, forums, and emails were utilized, resulting in over 51 meaningful feedback responses.
+In order to address the issue of data imbalance caused by collecting datasets solely from the openEuler mailing list, where more than 80\% of the projects were initially evaluated as having low porting complexity, a greater emphasis was placed on projects that had higher numbers of likes on GitHub and were deemed more important and active.
+Additionally, efforts were made to collect projects from the system bottom such as operating systems, kernel-level projects,mathematical computation libraries,and machine learning libraries to address RQ 2.
+\subsubsection{Result and Analysis}
 To answer RQ 2, based on the work of Chen Xiang et al.

### 2024-01-29 Paper/latex2/paper.tex
Add files via upload
update

@@
 \usepackage{hyperref}
+\usepackage{bbding}
 
@@
   In recent years, the open-source and reduced features of the RISC-V have led to active promotion of porting within the industry.Due to the lack of publicly available standards for assessing software portability, the software porting process for the RISC-V architecture has been predominantly reliant on expert experience, presenting obstacles.
-RAX is a automated tool which aids the C/C++ programmer in evaluating  complexity of projects during porting for RISC-V.RAX provides precise evaluation solutions and establishes a high-quality dataset for porting complexity assessment,enabling recommendations of suitable software with difficulty levels for developers of varying skill levels.We evaluate RAX on 72 popular and typical real-world C/C++ projects.
+RAX is a automated tool which aids the C/C++ programmer in evaluating  complexity of software during porting for RISC-V.RAX provides precise evaluation solutions and establishes a high-quality dataset for porting complexity,enabling recommendations of suitable software with difficulty levels for developers of varying skill levels.We evaluate RAX on 72 popular and typical real-scenario C/C++ projects.
 The experimental result shows that 51 of them have been confirmed by developers within community.Interested users can explore the open-source implementation of RAX at \href{https://github.com/wangyuliu/RAX-2024}{https://github.com/wangyuliu/RAX-2024}, or watch the RAX video demo at \href{https://www.youtube.com/watch?v=SLphW3Ra4WM}{https://www.youtube.com/watch?v=SLphW3Ra4WM}.
@@
 \section{Introduction}
-In recent years, the RISC-V Instruction Set Architecture (ISA) has garnered significant attention from academia, and particularly the industry, due to its open-source and reduced design\citep{2014The}.OpenEuler has joined RISC-V International organization, and RISC-V has officially become openEuler's official support architecture.The mainline integration of openEuler RISC-V 23.09 was finished by the RISC-V SIG.The main repository of openEuler 23.03 has successfully ported 4,244 software packages to the RISCV64,while the openEuler 23.09 main repository has currently completed the porting work of 5,694 software packages\citep{osti_1560132}.OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\citep{osti_1560133}.
+the RISC-V Instruction Set Architecture (ISA) has garnered significant attention from academia, and particularly the industry recently, due to its open-source and reduced design\citep{2014The}.OpenEuler has joined RISC-V International organization, and RISC-V has officially become openEuler's official support architecture.The mainline integration of openEuler RISC-V 23.09 was finished by the RISC-V SIG.The main repository of openEuler 23.03 has successfully ported 4,244 software packages to the RISCV64,while the openEuler 23.09 main repository has currently completed the porting work of 5,694 software packages\citep{osti_1560132}.OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\citep{osti_1560133}.
 
@@
 complexity evaluation tool.The contributions of this paper are as follows:
-\begin{enumerate}
-  \item Identify one of the most important factors,Cyclomatic Complexity(CC), and investigate its significant value in porting scenarios.
+\begin{itemize}
+  \item We identify one of the most important factors,Cyclomatic Complexity(CC), exploring its significant value in porting scenarios.
   % \item We explore building high-quality datasets that can cover various porting scenarios to solve the problem of imbalanced datasets of existing tools.Tuning machine learning models to address ambiguous identification of samples of medium and hard complexity compared to other studies.
@@
   % \item We nearly doubled the dataset compared to other tool,and verified the effectiveness of the evaluation of 51 extension projects in real porting scenarios through their respective communities or forums.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
-  \item Verify the effectiveness of RAX in real scenarios concentrating C/C++ projects. Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
-\end{enumerate}
+  \item We verify the effectiveness of RAX in real scenarios concentrating C/C++ projects.
+Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
+\end{itemize}
 
@@
 % Finally,an appropriate machine learning model is selected as a classification.
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figure1.pdf}
-  \caption{Flow chart for method to build RAX}
-  \label{fig:figure1}
-  \Description{Flow chart for method to build RAX}
-\end{figure}
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=\linewidth]{figure1.pdf}
+%   \caption{Flow chart for method to build RAX}
+%   \label{fig:figure1}
+%   \Description{Flow chart for method to build RAX}
+% \end{figure}
 \section{Motivation}
@@
 \textbf{RQ 2:} How to solve the problem of vague classification of projects with medium and high porting complexity in existing tools?
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figure2.pdf}
-  \caption{The relationship between score and CC}
-  \label{fig:figure2}
-  \Description{The relationship between score and CC}
-\end{figure}
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=\linewidth]{figure2.pdf}
+%   \caption{The relationship between score and CC}
+%   \label{fig:figure2}
+%   \Description{The relationship between score and CC}
+% \end{figure}
 
@@
 Building upon this, we delve into the quantification of the significance of cyclomatic complexity in porting work.
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figure2.pdf}
+  \caption{The relationship between score and CC}
+  \label{fig:figure2}
+  \Description{The relationship between score and CC}
+\end{figure}
 \subsection{Factor 1: Cyclomatic Complex(CC)}
@@
     \midrule
-    Other tool & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \\
-    RAX & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\
+   Other tool & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \XSolidBrush \\
+    RAX & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold \\
   \bottomrule
@@
 The following is an introduction to the process of RAX construction, as shown in Figure \ref{fig:figure1}.
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figure1.pdf}
+  \caption{Flow chart for method to build RAX}
+  \label{fig:figure1}
+  \Description{Flow chart for method to build RAX}
+\end{figure}
 During the analysis phase,architecture-related factors are obtained through the Commit tool for selection while investigating the impact of code complexity metrics on porting.
@@
 In the realm of scientific computing, Tine Blaise et al.
-\cite{osti_1830102} accomplished the porting of the OpenCL framework to RISC-V through a compiler framework, thereby expanding RISC-V's accessibility to a wider range of scientific computing applications.
-In the context of architectural porting of foundational software and libraries, Cheng Yuanhu et al.
-\cite{2017Slow} designed an embedded multi-instruction set processor,addressing the software ecosystem challenges present in the RISC-V embedded domain.
+\cite{osti_1830102} accomplished the porting of the OpenCL framework to commodity RISC-V CPU, thereby expanding RISC-V's accessibility to a wider range of scientific computing applications.
+Cheng Yuanhu et al. \cite{2017Slow} designed an embedded multi-instruction set processor,addressing the software ecosystem challenges present in the RISC-V embedded domain.
 Therefore, auxiliary efforts in porting are highlighted as valuable endeavors.
-Our work consider code complexity from the perspective of its evaluation role in software evolution and maintenance,considering its influence on porting complexity assessment \cite{1993Software}.
+Our work consider code complexity from the perspective of its evaluation role in software evolution and maintenance,mapping its influence on porting complexity assessment \cite{1993Software}.
 Alvares et al. \cite{7844689} proposed using the development team's ``tolerance'' for code complexity to infer team development capabilities and performance indicators for projects.
@@
 \section{Conclusion}
-We propose RAX, with the aim of recommending projects of varying porting difficulties to developers.
-We incorporate the code complexity to reflect developers' actual workload.
+The software porting work for RISC-V is being actively promoted, but it still faces the challenge of over-reliance on expert knowledge.We propose RAX, with the aim of recommending projects of varying porting difficulties to developers.
+Incorporate the code complexity to reflect developers' actual workload.
 We verified the effectiveness of the evaluation of 51 extension projects in real porting scenarios through their respective communities or forums.

### 2024-01-29 Paper/latex1-27/paper.tex
Add files via upload

@@
 \usepackage{xcolor}
+\usepackage{hyperref}
+\usepackage{bbding}
+\usepackage{courier}
+\usepackage{inconsolata}
 
@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{RAX: A porting complexity evaluation tool for RISC-V}
+\title{RAX:Efficiently Evaluating the Complexity of Porting for RISC-V}
 
@@
 \begin{abstract}
-  In recent years, the RISC-V’s open-source and reduced features have received active promotion of porting from the industry.Due to the lack of publicly available standards for assessing software portability, the software porting process for the RISC-V architecture has been predominantly reliant on expert experience, presenting obstacles.
-This paper introduces an automated tool, RAX, for assessing the porting complexity specifically for RISC-V by considering architecture-specific code and code Cyclomatic Complexity.RAX provides precise evaluation solutions and establishes a high-quality dataset for porting complexity assessment,enabling recommendations of suitable software difficulty levels for developers of varying skill levels.We continue to expand the dataset and conduct effective evaluations of the tool within the open-source community.We have gathered valuable feedback, including 47 positive responses, from 51 specific open-source projects.Interested users can explore the open-source implementation of RAX at (https://github.com/wangyuliu/R
-  AX-2024), or watch the RAX video demo at (https://github.com/wan
-  gyuliu/RAX-2024).
+  In recent years, the open-source and the advantages of reduced ISA of the RISC-V architecture are attracting active promotion of porting within the industry.Due to the lack of public available standards for assessing software portability, the software porting process for the RISC-V architecture has been predominantly reliant on expert experience, which is inefficient and time consuming.
+RAX is a automated tool which aids the C/C++ programmer in evaluating  complexity of software during porting for RISC-V.RAX provides precise evaluation solutions and builds a high-quality dataset for porting complexity,enabling recommendations of suitable software with difficulty levels for developers of varying skill levels.We evaluate RAX on 72 popular and typical real-scenario C/C++ projects.
+The experimental result shows that 51 of them have been confirmed by developers within community.Interested users can explore the open-source implementation of RAX at \href{https://github.com/wangyuliu/RAX-2024}{https://github.com/wangyuliu/RAX-2024}, or watch the RAX video demo at \href{https://www.youtube.com/watch?v=SLphW3Ra4WM}{https://www.youtube.com/watch?v\\=SLphW3Ra4WM}.
 \end{abstract}
@@
 \section{Introduction}
-\textcolor{orange}{In recent years, the RISC-V Instruction Set Architecture (ISA) has garnered significant attention from academia, particularly the industry, due to its open-source and reduced design.\citep{2014The}.OpenEuler has joined RISC-V International organization, and RISC-V has officially become openEuler's official support architecture.The mainline integration of openEuler RISC-V 23.09 was finished by the RISC-V SIG.The main repository of openEuler 23.03 has successfully ported 4,244 software packages to the RISCV64,while the openEuler 23.09 main repository has currently completed the porting work of 5,694 software packages\citep{osti_1560132}.OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\citep{osti_1560133}.}
+RISC-V Instruction Set Architecture (ISA) has garnered significant attention from academia, and particularly the industry recently, due to its open-source and reduced design\citep{2014The}.Many distribution manufacturers are actively promoting the porting of the RISC-V, for example,OpenEuler has joined RISC-V International organization, and RISC-V has officially become openEuler's official support architecture.The main repository of openEuler 23.03 has successfully ported 4,244 software packages to the RISCV64,while the openEuler 23.09 main repository has currently completed the porting work of 5,694 software packages\citep{osti_1560132}.OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\citep{osti_1560133}.
 
-\textcolor{orange}{Despite the rapid development of the RISC-V ISA, which foundational software such as operating systems and compilers are relatively mature, there is still a significant demand for porting a large number of application software.\citep{2019Notary}.To adapt to the RISC-V,efficiently porting software package is greatly depending on domain expertise.
-During the initial planning phase of porting, the lack of standardized evaluation criteria for software portability can lead to misallocation of resources in the development process.Therefore, it is desirable to propose a method that automates the assessment of porting complexity,this will enable different development teams to access software packages that are tailored to their proficiency levels, thus assisting distribution vendors in the porting of RISC-V architecture.}
+Despite the rapid development of the RISC-V ISA, which foundational software such as operating systems and compilers are relatively mature, there is still a significant demand for porting a large number of application software\citep{2019Notary}.To adapt to the RISC-V,efficiently porting is greatly depending on prior knowledge of experts, and the lack of standardized evaluation criteria for software portability can lead to unreasonable development planning.Therefore, it is desirable to propose a method that automates the evaluation of porting complexity.This will enable different development teams to access software packages that are tailored to their abilities, thus assisting distribution vendors in the porting of RISC-V architecture.
 
-\textcolor{orange}{Du et al.
-have developed a basic statistical evaluation plan for CPU architecture code in project\citep{2023du},however,their work lacks a thorough validity analysis of factors,and fails to consider the complexity associated with the software operation and maintenance process.}
+Many related works focus on the code complexity and portability evaluation,but studies for CPU architectures are currently lacking in these areas\cite{2016helei},\cite{TAHIR2016101},\cite{Sholiq_2021}.Du et al.
+have developed a basic statistical evaluation plan for CPU architecture code\citep{2023du},however,their work lacks a thorough validity analysis of factors,and may not consider the complexity factors associated with the software operation and maintenance process.
+To overcome these challenges, we propose RAX, an effective porting
+complexity evaluation tool which accurately locates the CPU architecture code and calculates the code complexity of the software.The contributions of this paper are as follows:
+\begin{itemize}
+  \item We analysis the actual porting modifications and figure out one of the most important factors,Cyclomatic Complexity(CC), exploring its significant value in porting scenarios.
+  % \item We explore building high-quality datasets that can cover various porting scenarios to solve the problem of imbalanced datasets of existing tools.Tuning machine learning models to address ambiguous identification of samples of medium and hard complexity compared to other studies.
+  \item Based on architecture-related factors, we propose RAX, to efficiently assess the complexity of software during porting to the RISC-V.
+  % \item We nearly doubled the dataset compared to other tool,and verified the effectiveness of the evaluation of 51 extension projects in real porting scenarios through their respective communities or forums.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
+  \item We build a dataset of real-world C/C++ projects and use it to evaluate the effectiveness of RAX.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of accuracy.
+\end{itemize}
+% The remainder of this paper is organized as follows.In Section 2,we briefly analyze architecture-related factors.
+Section 3 presents the implementation and evaluation of RAX.
+Section 4 and 5 presents related work and conclusions.
 
-RAX can provide developers with accurate evaluation, recommend software with different levels of porting difficulty based on their skill levels. The contributions of this paper are as follows:
-The contributions of this paper are as follows:
-\begin{enumerate}
-  \item In recent years, the RISC-V’s open-source and reduced features have received active promotion of porting from the industry.
-  \item We explore building high-quality datasets that can cover various porting scenarios to solve the problem of imbalanced datasets of previous tools.Tuning machine learning models to address ambiguous identification of samples of medium and hard complexity.
-  \item We nearly doubled the dataset compared to other tool,and verified the effectiveness of the evaluation of 51 extension projects in real porting scenarios through their respective communities or forums.Our findings indicate that RAX outperforms other tool, delivering substantial improvements in terms of performance and accuracy.
-\end{enumerate}
+% \section{RAX}
+% The following is an introduction to the process of RAX construction, as shown in Figure \ref{fig:figure1}.
+% During the analysis phase,architecture-related factors are obtained through the Commit tool for selection while investigating the impact of code complexity metrics on porting.
+% A scanning tool is built to get potential modification workload.
+% Finally,an appropriate machine learning model is selected as a classification.
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=\linewidth]{figure1.pdf}
+%   \caption{Flow chart for method to build RAX}
+%   \label{fig:figure1}
+%   \Description{Flow chart for method to build RAX}
+% \end{figure}
+\section{Motivation}
+We propose the following research questions:
 
-\section{RAX}
-The following is an introduction to the process of RAX construction, as shown in Figure \ref{fig:figure1}.
-During the analysis phase,architecture-related factors are obtained through the Commit tool for selection while investigating the impact of code complexity metrics on porting.
-A scanning tool is built to get potential modification workload.
-Finally,an appropriate machine learning model is selected as a classification.
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figure1.pdf}
-  \caption{Flow chart for method to build RAX}
-  \label{fig:figure1}
-  \Description{Flow chart for method to build RAX}
-\end{figure}
-\subsection{Motivation}
-To design RAX that assists developers with porting work,the following research questions are proposed:
+\textbf{RQ 1:} How can we select architecture-relevant factors that is fine-grained to design an automated evaluation tool of porting complexity?
 
-\textbf{RQ 1:} How can we select architecture-relevant actors that is fine-grained to design an automated tool that assesses the porting difficulty?
+\textbf{RQ 2:} How to solve the problem of fuzzy classification of projects with medium and high porting complexity in existing tools?
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=\linewidth]{figure2.pdf}
+%   \caption{The relationship between score and CC}
+%   \label{fig:figure2}
+%   \Description{The relationship between score and CC}
+% \end{figure}
 
-\textbf{RQ 2:} How to solve the problem of vague classification of projects with medium and high porting difficulty in previous tools?
-
-To answer research question 1,this section provides a validity analysis of porting-related factors on RAX.
+To answer RQ 1,this section provides a validity analysis of porting-related factors on RAX.
 First,we try to use code complexity metrics to evaluate porting work.
-The software metrics of code Cyclomatic Complexity(CC) can help developers make macro judgments on software complexity and maintenance difficulty, evaluate potential and hidden porting difficulties,which help the tool improve accuracy \cite{2005Exploring}.
-At present, CC indicators are mostly used in project code quality assessment, defect inspection, code reconstruction, etc \cite{1991Cyclomatic}.
+The software metrics of code Cyclomatic Complexity(CC) can help developers make macro judgments on software complexity and maintenance difficulty.
+By evaluating potential and hidden porting difficulties,code complexity helps the tool improve accuracy \cite{2005Exploring}.
+At present, CC indicators are mostly used in evaluating code quality, inspecting defect, reconstructing code, etc \cite{1991Cyclomatic}.
 During the porting process, developers will target a large number of project source codes,build scripts,assembly codes,and a macro understanding of the project is required in the early stage of porting.
-This part of the work has a lot of overlap with the scope of code complexity.Through our survey of community, we have discovered that even though architectural code can be separated quite clearly from common code, when faced with complex and large-scale projects, we still require numerous iterative tests to uncover unknown architectural code.
-Building upon this, we delve into the quantification of the significance of cyclomatic complexity in porting work.
-
-\subsubsection{Factor 1: Cyclomatic Complex(CC)}
-\label{sec:factor-1}
-We uses the lizard CC detection tool and optimize its functions,and it will introduce it in Section \ref{sec:method}.
-This study analyzes the relationship between CC and software porting complexity using the Spearman Rank correlation coefficient analysis method.
-We invited five Master's students who are engaged in research on porting auxiliary tools to score the porting complexity(score) of 131 software adapted for RISC-V,collected from the OpenEule list\citep{stage2023} and GitHub.
-According to the collection of Internet events, log analysis, source code dismantling, and similar project analogy \cite{liangguanyu2020}, we form a scoring interval in the range of $[0~5]$.
-The Spearman coefficient of CC and score is 0.608, with a P-value of 1.39e-14, which is less than 0.01.
-The results suggest that CC has a moderate positive correlation with porting difficulty.
-This is because developers need a holistic understanding of the project during the porting process, and CC can represent the overall complexity of the project, potentially reflecting porting barriers, as shown in Figure \ref{fig:figure2}.
-
-Second, we consider the effectiveness of the architecture binding code structure proposed by the other tool and conduct comparative experiments using more potential factors.
+This part of the work has a lot of overlap with the scope of code complexity.Through our survey of community, we discovered that even though architectural code can be separated quite clearly from common code, when faced with large-scale projects, we still require numerous iterative tests to uncover unknown architectural code.
+Building upon this, we study the quantification of the significance of cyclomatic complexity in porting work.
 \begin{figure}
@@
 \end{figure}
-\subsubsection{Factor2:Arch\_code}
+\subsection{Factor 1: Cyclomatic Complex(CC)}
+\label{sec:factor-1}
+We use the lizard CC detection tool and optimize its functions,and it will introduce it in Section \ref{sec:Implementation}.
+this section calculate the correlation coefficient using the Spearman Rank.
+We invited five Master's students who are engaged in research on porting auxiliary tools to score the porting complexity(score) of 131 projects adapted for RISC-V,collected from the OpenEuler list\citep{stage2023} and GitHub.
+According to the collection of Internet events, log analysis, source code dismantling, and similar project analogy \cite{liangguanyu2020}, we form a scoring interval in the range of $[0,5]$.
+The Spearman coefficient of CC and score is 0.608, with a P-value of 1.39e-14, which is less than 0.01.
+The results suggest that CC has a moderate positive correlation with porting difficulty.
+This is because developers need a holistic understanding of the project during the porting process, and CC can represent the overall complexity of the project, potentially reflecting porting barriers, the relationship of factors shown in Figure \ref{fig:figure2}.
 
-Based on the analysis of previous evaluation tools, we selected factors with the greatest potential and that can be extracted through automated methods to define Arch\_code.
-Arch\_code includes assembly code, conditional compilation and macro structure, Intrinsic functions, Builtin functions, architecture-related build scripts, and system calls.
-We use an automated architecture binding code scanning tool to obtain statistics on the number of lines and frequencies of Arch\_code.
+Second, we consider the effectiveness of the architecture-related code structure proposed by other tool and conduct comparative experiments using more potential factors.
+\subsection{Factor2:Arch\_code}
 
-Continue to collect other factors that may affect the evaluation of porting complexity,and select the following parameters through the Commit analyzer:architecture-related code lines, architecture-related files, and architecture keywords.
-The number of architecture-related code lines and files is located using the keywords of the RISC-V architecture, such as riscv, rv32, rv64, RISC-V, RISCV and so on.
-%Correlation comparison between Arch\_code and other factors acquired by Commit analyzer,as shown in Table \ref{tab:score}:
+We select factors with the greatest potential from existing tool and define Arch\_code.
+Arch\_code includes assembly code, conditional compilation and macro structure(CCM), Intrinsic functions, Builtin functions, architecture-related build scripts, and system calls.
+We use an automated tool to obtain statistics of lines and frequencies of Arch\_code.
+
+We further collect other factors that may reflect the porting complexity,and select the following parameters through the Commit analyzer:architecture-related code lines, architecture-related files, and architecture keywords.architecture-related code lines and files is located using the keywords of the RISC-V architecture, such as riscv, rv32, rv64, RISC-V, RISCV and so on.
+%Correlation comparison between Arch\_code and other factors acquired by Commit analyzer,as shown in Table \ref{tab:Tool}:
 
@@
     \toprule
-    & Full Assembly & Inline Assembly & Intrinsic & Builtin & System Call & Conditional compilation and macro & Buildscripts & CC \\
+    & Full Assembly & Inline Assembly & Intrinsic & Builtin & System Call & CCM & Buildscripts & CC \\
     \midrule
-    Other tool & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \\
-    RAX & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\
+   Other tool & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \XSolidBrush \\
+    RAX & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold \\
   \bottomrule
@@
 
-Correlation comparison between Arch\_code and other factors acquired by Commit analyzer,as shown in Figure \ref{fig:figure3}:
+Figure \ref{fig:figure3} shows the correlation comparison between Arch\_code,CC and other factors acquired by Commit analyzer:
 \begin{figure}
@@
 \end{figure}
-The results indicate that Arch\_code has a higher correlation with score compared to other factors, and it also aligns with the significant results of the Peason correlation test.
-The use of only architecture keywords for statistics yields moderate effectiveness in evaluating tool because keywords can only be detected from comments and macro sections of Commit, while critical porting code may lack these keywords,but the keyword count can reflect the amount of porting modification from the side.
-As shown in the Figure \ref{fig:figure3},the parameters of Arch\_code show a correlation of 0.45 to 0.75 with score, indicating a strong relationship.
+The results indicate that Arch\_code and CC has a higher correlation with score compared to other factors, and we use Peason correlation method to build the heat map.
+The use of only architecture keywords for statistics yields moderate effectiveness because keywords can only be detected from comments and macro sections of Git commits, while critical porting code may lack these keywords,but the number of keywords can reflect the amount of porting modification from the side.
+Arch\_code show a correlation of 0.45 to 0.75 with score, indicating a strong relationship.
 However, using a single factor alone does not result in a significantly strong correlation, as the combined modifications of these factors make up the porting workload.
 
-In the end,our tool selection was CC and the Arch\_code build scanning tool,as shown in Table \ref{tab:score}.
+In the end,our tool selection was CC and the Arch\_code build scanning tool,as shown in Table \ref{tab:Tool}.
 
@@
 
-\subsection{Dataset}
-We used the project upstream warehouse to build the data set,that projects mainly targeting C and C++ are from the OpenEuler\citep{stage2023} list and GitHub,and invited 5 postgraduate students who are engaged in the research of RISC-V porting auxiliary tools to participate in the experimental evaluation.Specific evaluation methods can be found in 2.1.1.
-The evaluation scores are divided into three categories: low, medium, and high\citep{githuburl}.This includes 139 projects as training, testing, and validation datasets, while more than 80 additional projects were used as a tool evaluation dataset.
+\section{RAX}
+The following is an introduction to the process of RAX construction, as shown in Figure \ref{fig:figure1}.
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figure1.pdf}
+  \caption{Flow chart for method to build RAX}
+  \label{fig:figure1}
+  \Description{Flow chart for method to build RAX}
+\end{figure}
+During the analysis phase,architecture-related factors are obtained through the Commit tool for selection while investigating the impact of code complexity metrics on porting.
+A scanning tool is built to get potential modification workload.
+Finally,an appropriate machine learning model is selected as a classification.
+
+% \subsection{Dataset}
+% We used the project upstream warehouse to build the data set,that projects mainly targeting C and C++ are from the OpenEuler list and GitHub,and invited 5 postgraduate students who are engaged in the research of RISC-V porting auxiliary tools to participate in the experimental evaluation.Specific evaluation methods can be found in \ref{sec:factor-1}.
+The evaluation scores are divided into three categories: low, medium, and high\citep{githuburl}.This includes 139 projects as training, testing, and validation datasets, while more than 80 additional projects were used as a tool effectiveness evaluation dataset.
 To gather insights from developers, the community, forums, and emails were utilized, resulting in over 51 meaningful feedback responses.
 In order to address the issue of data imbalance caused by collecting datasets solely from the openEuler mailing list, where more than 80\% of the projects were initially evaluated as having low porting complexity, a greater emphasis was placed on projects that had higher numbers of likes on GitHub and were deemed more important and active.
-Additionally, efforts were made to collect projects from the bottom such as operating systems, kernel-level projects,mathematical computation libraries,and machine learning libraries.
+Additionally, efforts were made to collect projects from the system bottom such as operating systems, kernel-level projects,mathematical computation libraries,and machine learning libraries to address RQ 2.
 
-\subsection{Method}
-\label{sec:method}
-The RAX combines the CC calculation module and the Arch\_code location module to obtain the porting vector,and the complexity vector and score together form the data set.
+\subsection{Implementation}
+\label{sec:Implementation}
+RAX obtains porting complexity vector through the CC calculation method and Arch\_code statistical value.
 
@@
 Lizard's default computing method is basically consistent with McCabe's theory \cite{1702388}.
-However, Lizard tool only detects defects at the function level and uses the average function CC for file-level statistics, which is not suitable for current porting complexity detection requirements \cite{9402593}.
-This paper proposes a new method for evaluating CC specifically for porting assessment work:
-\begin{enumerate}
-  \item First, calculate the function-level CC for all files in the project using McCabe's method.
-  \item Following Liu's mention of System Cyclomatic Complexity (SCC) in software evolution assessment techniques based on code change detection \cite{liuhuihui00}, we define SCC as the total sum of function-level values in the system.
-  The advantage is that it can avoid the use of overly complex methods, which will cause deviations to affect the classification results.
-  Additionally,due to the system's complexity being calculated based on a single function,it eliminates the problem of decreased detection performance caused by the conversion of such a large code structure of all modules into into syntax abstract trees and control flow graphs.
-  Our CC calculation approach is expressed by the following equation,where lowercase cc represents the cyclomatic complexity at the function or file level.The uppercase CC represents the overall cyclomatic complexity of the software package,serving as a crucial factor in our tool.Here, |E| denotes the number of edges in the function control flow graph,and |N| represents the number of nodes.The function control flow graph is constructed based on branching structures such as if, while, and switch statements.
+However, Lizard tool only defects at the function level and uses the average function CC for file-level statistics, which is not suitable for current porting complexity detection requirements \cite{9402593}.
+This paper proposes a new method:
+
+First, we calculate the function-level CC for all files in the project using McCabe's method.Following Liu's mention of System Cyclomatic Complexity (SCC) in software evolution assessment techniques based on code change detection \cite{liuhuihui00}, we define SCC as the total sum of function-level values in the system.
+  The advantage is that it can avoid the use of complex methods, which will cause deviations to affect the classification results.
+  Additionally,due to the system's complexity being calculated based on a single function,it eliminates the problem of decreased detection performance caused by the conversion of such a large code structure of all modules into into abstract syntax tree and control flow graphs.
+  Our CC calculation approach is expressed by equation (1) to (3),where lowercase cc represents the cyclomatic complexity at the function or file level.The uppercase CC represents the overall cyclomatic complexity of the software package,serving as a crucial factor in our tool.Here, |E| denotes the number of edges in the function control flow graph,and |N| represents the number of nodes.The function control flow graph is constructed based on branching structures such as if, while, and switch statements.
 
@@
 
-\end{enumerate}
-
 \subsubsection{Arch\_code scan function}
@@
 Additionally, the correlation between the total values for all architectures and score was only 0.49.
-Based on these results, analyze that our tool try to effectively designed to assess the porting difficulty between two architectures.
+Based on these results, analyze that our tool try to effectively assess the porting difficulty between two architectures.
 It is not as simple as adding up the modification amounts for different architectures, as it may only reflect an increase in code volume.
-Moreover, Due to the large differences in row\_based statistical results caused by the differences in code structure reflected by each architecture, this approach that easily considers all architectures simultaneously without considering the code structure cannot improve the accuracy of classification results and may lead to ambiguous outcomes.
-Therefore, based on these experiments, we still selected x86 as the architecture to build Arch\_code scan function, utilizing its keywords and critical function dictionary, given its mainstream position.
+Moreover, due to the large differences in row\_based statistical results caused by the differences in code structure reflected by each architecture, this approach that easily considers all architectures simultaneously without considering the code structure and architectural weight lead to ambiguous outcomes.Therefore, based on these experiments, we still select x86 to build Arch\_code scan function, given its mainstream position.
 
-we form the Arch\_code dictionary:
-\textbf{Conditional compilation and architecture macros} Use conditional compilation statements, such as ``if defined'', ``ifdef'', in conjunction with all possible architectur macros,
-  ``\_\_x86\_64\_\_''.
-  We use a similar bracket matching algorithm to cover all the code within macros, avoiding the impact of nested layers.
-  \textbf{Assembly} We use matching forms such as ``\_\_asm\_\_'' and ``\_\_volatile\_\_''.
+We form the Arch\_code dictionary:
+(1)\emph{Conditional compilation and architecture macros} Use conditional compilation statements, such as ``\texttt{if defined}'', ``\texttt{ifdef}'', in conjunction with all possible architecture macros,
+  ``\texttt{\_\_x86\_64\_\_}''.
+  We use an algorithm similar to bracket matching to cover all the code within macros, avoiding the impact of nested layers.
+  (2)\emph{Assembly} We use matching forms such as ``\texttt{\_\_asm\_\_}'' and ``\texttt{\_\_volatile\_\_}''.
   In future work,we will consider striving to achieve the currently unachievable architecture identification function of assembly code and identify assembly code in the form of instructions;
-  \textbf{Intrinsic and Builtin} 
+  (3)\emph{Intrinsic and Builtin} 
   We compile dictionaries of Intrinsic functions based on official documentation from x86\cite{x86intrin}.
   Builtin function also employ a similar approach;In the future,we may assign difficulty weights to them.
-  \textbf{System calls} Considering glibc's support for system call encapsulation, reorganize the sys-call dictionary.
-  The system calls that do not support RISC-V have been filtered out currently.
-  \textbf{Buildscripts} We locate architecture keywords in the build scripts.
+  (4)\emph{System calls} Considering glibc's support for system call encapsulation, reorganize the sys-call dictionary.
+  The system calls that do not support RISC-V have been filtered and collected currently.
+  (5)\emph{Buildscripts} We locate architecture keywords in the build scripts.
 
-\section{Result and analysis}
-To answer research question 2, based on the work of Chen Xiang et al.
+\subsection{Evaluation}
+\subsubsection{Dataset}
+We used the project upstream warehouse to build the data set,which mainly targeting C and C++ are from the OpenEuler list and GitHub,and invited 5 postgraduate students who are engaged in the research of RISC-V porting auxiliary tools to participate in the experimental evaluation.Specific evaluation methods can be found in \ref{sec:factor-1}.
+The evaluation scores are divided into three categories: low, medium, and high\citep{githuburl}.This includes 139 projects as training, testing, and validation datasets, while more than 80 additional projects were used as a tool effectiveness evaluation dataset.
+To gather insights from developers, the community, forums, and emails were utilized, resulting in over 51 meaningful feedback responses.
+In order to address the issue of data imbalance caused by collecting datasets solely from the openEuler mailing list, where more than 80\% of the projects were initially evaluated as having low porting complexity, a greater emphasis was placed on projects that had higher numbers of likes on GitHub and were deemed more important and active.
+Additionally, efforts were made to collect projects from the system bottom such as operating systems, kernel-level projects,mathematical computation libraries,and machine learning libraries to address RQ 2.
+\subsubsection{Result and Analysis}
+To answer RQ 2, based on the work of Chen Xiang et al.
 \cite{5128907}, aiming at the status quo of unbalanced datasets and small sample datasets, we try to use ensemble learning methods \cite{6509481}, SMOTE \cite{4271036}, and random oversampling methods for data preprocessing.
 Ultimately, we chose to train four models: Random Forest, Support Vector Machine, Adaboost, and Xgboost.
-By comparing multiple indicators, we select the Random Forest machine learning as the classifier, as shown in Table \ref{tab:evaluation}
+By comparing multiple indicators, we select the Random Forest machine learning as the classifier, as shown in Table \ref{tab:evaluation}.
 
@@
 
-We continued to expand 100 projects as a supplementary data set, and the prediction results were determined through comments from the community and forums.
-Appendix presents a comparative assessment of the porting complexity evaluation tool developed by Du et al.
+We continued to expand 72 projects as a supplementary data set, and the prediction results were determined through comments from the community and forum.
+Github presents comparison\cite{githubss} with the porting complexity evaluation tool developed by Du et al.
 across various projects, the comparison results are shown in Table \ref{tab:effectiveness}.Through real-world evaluations within the developer community, our tool has exhibited a significant improvement in accuracy, surpassing other comparable tools by a margin of 15.6\%.
-In the appendix, we provide a comprehensive compilation of the community's valuable feedback comments, accompanied by the relevant web links for further reference and validation.
+In Github, we provide a comprehensive compilation of the community's valuable feedback comments, accompanied by the relevant web links for further reference and validation.
 
@@
 
-After adding the code complexity factor and modifying the original tool design model, RAX's result prediction accuracy is improved.
-This is because code complexity can clearly distinguish three types of porting difficulty
+After adding the code complexity factor and modifying the original model, RAX's result prediction accuracy is improved.
+This is because code complexity can clearly distinguish three types of porting difficulty.
 Motivation Chapters present the cause analysis.
@@
 
-Within this assessment, there are instances of inaccurate predictions.In-depth analysis of these variations reveals that certain projects exhibit inherent complexity, entailing a substantial presence of architecture-specific code defined by Arch\_code.
+Within evaluation, there are instances of inaccurate predictions.
+Analysis of some variations reveals that certain projects exhibit inherent complexity, entailing a substantial presence of architecture-specific code defined by Arch\_code.
 Nevertheless, the practical porting process benefits from an array of auxiliary tools designed to support developers.
-In response to valuable suggestions from developers within the OpenEuler community, we conducted an evaluation of the porting difficulty for various versions of the Chromium.Initially, we were able to accurately assess the porting difficulty, yielding promising results.
-However, when it came to evaluating the work involved in iterative updates between versions, existing tools proved insufficient for precise estimation.Sometimes developers design their work has generic code for unknown architecture and CPU architecture parts are well separated from the common code,that just need only to adjust the macro to recognize RISC-V,like nuttx.
+In response to valuable suggestions from developers within the OpenEuler community, we conducted an evaluation of the porting complexity for various versions of the Chromium.Initially, we were able to accurately assess the porting complexity, yielding promising results.
+However, when it came to evaluating the work involved in iterative updates between versions, existing tools proved insufficient for precise estimation.Sometimes developers design their work with generic code for unknown architecture and CPU architecture parts are well separated from the common code,that just need only to adjust the moderate amount of code to recognize RISC-V,like nuttx.
 \section{Related Work}
@@
 In the realm of scientific computing, Tine Blaise et al.
-\cite{osti_1830102} accomplished the porting of the OpenCL framework to RISC-V through a compiler framework, thereby expanding RISC-V's accessibility to a wider range of scientific computing applications.
-In the context of architectural migration of foundational software and libraries, Cheng Yuanhu et al.
-\cite{2017Slow} designed an embedded multi-instruction set processor,addressing the software ecosystem challenges present in the RISC-V embedded domain.
-As a result, auxiliary efforts in porting are highlighted as valuable endeavors.
-This tool approaches code complexity from the perspective of its evaluation role in software evolution and maintenance,considering its influence on porting complexity assessment \cite{1993Software}.
+\cite{osti_1830102} accomplished the porting of the OpenCL framework to commodity RISC-V CPU, thereby expanding RISC-V's accessibility to a wider range of scientific computing applications.
+Cheng Yuanhu et al. \cite{2017Slow} designed an embedded multi-instruction set processor,addressing the software ecosystem challenges present in the RISC-V embedded domain.
+Therefore, auxiliary efforts in porting are highlighted as valuable endeavors.
+Our work consider code complexity from the perspective of its evaluation role in software evolution and maintenance,mapping its influence on porting complexity evaluation \cite{1993Software}.
 Alvares et al. \cite{7844689} proposed using the development team's ``tolerance'' for code complexity to infer team development capabilities and performance indicators for projects.
-Vard et al. \cite{2017Evaluating} emphasized that the internal quality of software impacts developers' capabilities and maintenance durations.
+Vard et al. \cite{2017Evaluating} emphasized that the internal quality of software impacts developers' capabilities and maintenance duration.
 They conducted a comprehensive study on various existing code complexity metrics' validity and suggested incorporating empirically observed code features as complexity triggers.
 \section{Conclusion}
-We propose RAX, with the aim of recommending projects of varying porting difficulties to developers.
-We incorporate the code complexity to reflect developers' actual workload.
+The software porting work for RISC-V is being actively promoted, but it still faces the challenge of over-reliance on expert knowledge.We propose RAX, with the aim of recommending projects of varying porting difficulties to developers.
+Incorporate the code complexity to reflect developers' actual workload.
 We verified the effectiveness of the evaluation of 51 extension projects in real porting scenarios through their respective communities or forums.
-Observed significant performance improvements compared to previous tools.Moreover, RAX provides developers with the functionality to locate target code segments.Our next steps involve attempting text classification methods to categorize the text results of the scanning tool, designing more granular statistical methods for architecture-related factors.
+Observed significant performance improvements compared to existing tools.Moreover, RAX provides developers with the functionality to locate target code segments.Our next steps involve attempting text classification methods to categorize the text results of the original tool, designing more granular statistical methods for architecture-related factors.
 %%

### 2024-01-29 Paper/latex1-27/paper.tex
Add files via upload

@@
 Many related works focus on the code complexity and portability evaluation,but studies for CPU architectures are currently lacking in these areas\cite{2016helei},\cite{TAHIR2016101},\cite{Sholiq_2021}.Du et al.
-have developed a basic statistical evaluation plan for CPU architecture code\citep{2023du},however,their work lacks a thorough validity analysis of factors,and may not consider the complexity factors associated with the software operation and maintenance process.
+have developed a basic statistical evaluation plan for CPU architecture code\citep{2023du}.However,their work lacks a thorough validity analysis of factors,and may not consider the complexity factors associated with the software operation and maintenance process.
 To overcome these challenges, we propose RAX, an effective porting
@@
   (3)\emph{Intrinsic and Builtin} 
-  We compile dictionaries of Intrinsic functions based on official documentation from x86\cite{x86intrin}.
-  Builtin function also employ a similar approach;In the future,we may assign difficulty weights to them.
+  We compile dictionaries of Intrinsic and Builtin functions based on official documentation from x86\cite{x86intrin}.In the future,we may assign difficulty weights to them.
   (4)\emph{System calls} Considering glibc's support for system call encapsulation, reorganize the sys-call dictionary.
@@
 \section{Related Work}
-The development of the RISC-V ecosystem is rapidly progressing.
-In the realm of scientific computing, Tine Blaise et al.
-\cite{osti_1830102} accomplished the porting of the OpenCL framework to commodity RISC-V CPU, thereby expanding RISC-V's accessibility to a wider range of scientific computing applications.
-Cheng Yuanhu et al. \cite{2017Slow} designed an embedded multi-instruction set processor,addressing the software ecosystem challenges present in the RISC-V embedded domain.
-Therefore, auxiliary efforts in porting are highlighted as valuable endeavors.
-Our work consider code complexity from the perspective of its evaluation role in software evolution and maintenance,mapping its influence on porting complexity evaluation \cite{1993Software}.
+The development of the RISC-V ecosystem is rapidly progressing,and numerous studies also advance the RISC-V porting.
+Tine Blaise et al.\cite{osti_1830102} accomplished the porting of the OpenCL framework to commodity RISC-V CPU, thereby expanding RISC-V's accessibility to a wider range of scientific computing applications.
+Cheng Yuanhu et al.\cite{2017Slow}designed an automated porting framework to solve the problem of efficient porting of basic mathematics libraries.
+However,there is still a lack of fine-grained assistance tools for architecture portability evaluation.
+% Our work consider code complexity from the perspective of its evaluation role in software evolution and maintenance,mapping its influence on porting complexity evaluation\cite{1993Software}.
 Alvares et al. \cite{7844689} proposed using the development team's ``tolerance'' for code complexity to infer team development capabilities and performance indicators for projects.
 Vard et al. \cite{2017Evaluating} emphasized that the internal quality of software impacts developers' capabilities and maintenance duration.
-They conducted a comprehensive study on various existing code complexity metrics' validity and suggested incorporating empirically observed code features as complexity triggers.
+They conducted a comprehensive study on various existing code complexity metrics' validity and suggested incorporating empirically observed code features as complexity triggers.We have pioneered the application of code complexity metrics in the domain of porting assessment, while existing research primarily focuses on code refactoring and defect detection\cite{1993Software}.
 \section{Conclusion}

### 2024-01-29 Paper/latex1-27/paper.tex
Add files via upload

@@
 \usepackage{courier}
-\usepackage{inconsolata}
 
@@
 The following is an introduction to the process of RAX construction, as shown in Figure \ref{fig:figure1}.
+During the analysis phase,architecture-related factors are obtained through the Commit tool for selection while investigating the impact of code complexity metrics on porting.
+A scanning tool is built to get potential modification workload.
+Finally,an appropriate machine learning model is selected as a classification.
 \begin{figure}
@@
 \end{figure}
-During the analysis phase,architecture-related factors are obtained through the Commit tool for selection while investigating the impact of code complexity metrics on porting.
-A scanning tool is built to get potential modification workload.
-Finally,an appropriate machine learning model is selected as a classification.
 
@@
   \begin{equation}
-    \mathrm{cc}(\mathrm{function}) = \lvert E \rvert - \lvert N \rvert + 2
+    {cc}({function}) = \lvert E \rvert - \lvert N \rvert + 2
     % \sum_{i=1}^{n} x_i
@@
     \begin{equation}
-      \mathrm{cc}(\mathrm{file}) =  \sum_{i=1}^{n} \mathrm{cc}(\mathrm{function})
+      {cc}({file}) =  \sum_{i=1}^{n} 
+      {cc}({function})
       \end{equation}
       \begin{equation}
-        \mathrm{CC} =  \sum_{i=1}^{k} \mathrm{cc}(\mathrm{file})
+        {CC} =  \sum_{i=1}^{k} {cc}({file})
         \end{equation}
@@
 Based on this, we conducted comparative experiments using various architectures, including X86, ARM, MIPS, RISCV, SPARC, and PowerPC.
-We performed scanning and counting based on the keyword and function dictionaries specific to each architecture, which were derived from common patterns summarized from official websites.
-By analyzing the correlation coefficient (Pearson's) between the keyword coverage line statistics of the six architectures and the score representing the porting complexity, we found that the correlation ranged from 0.44 to 0.58, indicating an average correlation across all architectures.
+We performed scanning and counting based on the keyword and function dictionaries specific to each architecture, which were derived from common patterns summarized by official websites.
+By analyzing the correlation coefficient (Pearson's) between the keyword coverage line statistics of the six architectures and the score representing the porting complexity, we found that the correlation ranged from 0.44 to 0.58, indicating all correlation results are not significant.
 Additionally, the correlation between the total values for all architectures and score was only 0.49.
@@
 It is not as simple as adding up the modification amounts for different architectures, as it may only reflect an increase in code volume.
-Moreover, due to the large differences in row\_based statistical results caused by the differences in code structure reflected by each architecture, this approach that easily considers all architectures simultaneously without considering the code structure and architectural weight lead to ambiguous outcomes.Therefore, based on these experiments, we still select x86 to build Arch\_code scan function, given its mainstream position.
+Moreover, due to the large differences in row-based statistical results caused by the differences in code structure reflected by each architecture, this approach that easily considers all architectures simultaneously without considering the code structure and architectural weight lead to ambiguous outcomes.Therefore, based on these experiments, we still select x86 to build Arch\_code scan function, given its mainstream position.
 
 We form the Arch\_code dictionary:
-(1)\emph{Conditional compilation and architecture macros} Use conditional compilation statements, such as ``\texttt{if defined}'', ``\texttt{ifdef}'', in conjunction with all possible architecture macros,
+(1)\textit{Conditional compilation and architecture macros} Use conditional compilation statements, such as ``\texttt{if defined}'', ``\texttt{ifdef}'', in conjunction with all possible architecture macros,
   ``\texttt{\_\_x86\_64\_\_}''.
   We use an algorithm similar to bracket matching to cover all the code within macros, avoiding the impact of nested layers.
-  (2)\emph{Assembly} We use matching forms such as ``\texttt{\_\_asm\_\_}'' and ``\texttt{\_\_volatile\_\_}''.
+  (2)\textit{Assembly} We use matching forms such as ``\texttt{\_\_asm\_\_}'' and ``\texttt{\_\_volatile\_\_}''.
   In future work,we will consider striving to achieve the currently unachievable architecture identification function of assembly code and identify assembly code in the form of instructions;
-  (3)\emph{Intrinsic and Builtin} 
+  (3)\textit{Intrinsic and Builtin} 
   We compile dictionaries of Intrinsic and Builtin functions based on official documentation from x86\cite{x86intrin}.In the future,we may assign difficulty weights to them.
-  (4)\emph{System calls} Considering glibc's support for system call encapsulation, reorganize the sys-call dictionary.
+  (4)\textit{System calls} Considering glibc's support for system call encapsulation, reorganize the sys-call dictionary.
   The system calls that do not support RISC-V have been filtered and collected currently.
-  (5)\emph{Buildscripts} We locate architecture keywords in the build scripts.
+  (5)\textit{Buildscripts} We locate architecture keywords in the build scripts.
 
@@
 \subsubsection{Dataset}
-We used the project upstream warehouse to build the data set,which mainly targeting C and C++ are from the OpenEuler list and GitHub,and invited 5 postgraduate students who are engaged in the research of RISC-V porting auxiliary tools to participate in the experimental evaluation.Specific evaluation methods can be found in \ref{sec:factor-1}.
-The evaluation scores are divided into three categories: low, medium, and high\citep{githuburl}.This includes 139 projects as training, testing, and validation datasets, while more than 80 additional projects were used as a tool effectiveness evaluation dataset.
+We used the project upstream warehouse to build the data set,which mainly targeting C and C++ are from the OpenEu-ler list and GitHub,and invited 5 postgraduate students who are engaged in the research of RISC-V porting auxiliary tools to participate in the experimental evaluation.Specific evaluation methods can be found in \ref{sec:factor-1}.
+The evaluation scores are divided into three categories: low, medium, and high\citep{githuburl}.This includes 139 projects as training, testing, and validation datasets, while more than 70 additional projects were used as a tool effectiveness evaluation dataset.
 To gather insights from developers, the community, forums, and emails were utilized, resulting in over 51 meaningful feedback responses.
@@
 Ultimately, we chose to train four models: Random Forest, Support Vector Machine, Adaboost, and Xgboost.
-By comparing multiple indicators, we select the Random Forest machine learning as the classifier, as shown in Table \ref{tab:evaluation}.
+By comparing multiple indicators, we select the Random Forest machine learning model as the classifier, as shown in Table \ref{tab:evaluation}.
 
@@
 \section{Related Work}
-The development of the RISC-V ecosystem is rapidly progressing,and numerous studies also advance the RISC-V porting.
-Tine Blaise et al.\cite{osti_1830102} accomplished the porting of the OpenCL framework to commodity RISC-V CPU, thereby expanding RISC-V's accessibility to a wider range of scientific computing applications.
-Cheng Yuanhu et al.\cite{2017Slow}designed an automated porting framework to solve the problem of efficient porting of basic mathematics libraries.
+With the development of the RISC-V ecosystem,  projects of porting for RISC-V has attracted much attention in both academia and industry.
+For example,Tine Blaise et al.\cite{osti_1830102} accomplished the porting of the OpenCL framework to commodity RISC-V, thereby expanding RISC-V's accessibility to a wider range of scientific computing applications.
+Cao Hao et al.\cite{2017Slow}designed an automated porting framework to solve the problem of efficient porting of basic mathematics libraries.
 However,there is still a lack of fine-grained assistance tools for architecture portability evaluation.
@@
 The software porting work for RISC-V is being actively promoted, but it still faces the challenge of over-reliance on expert knowledge.We propose RAX, with the aim of recommending projects of varying porting difficulties to developers.
-Incorporate the code complexity to reflect developers' actual workload.
+Our method incorporate the code complexity and architectural code to reflect developers' actual workload.
 We verified the effectiveness of the evaluation of 51 extension projects in real porting scenarios through their respective communities or forums.

### 2024-01-29 Paper/latex1-27/paper.tex
update

@@
 \section{Motivation}
-We propose the following research questions:
+\textcolor{red}{To help developers more accurately assess the complexity of C/C++ projects, we aim to answer the following research questions:}
 
-\textbf{RQ 1:} How can we select architecture-relevant factors that is fine-grained to design an automated evaluation tool of porting complexity?
+\textbf{RQ 1:} How can we identify architecture-relevant important factors affecting porting efficiency?
 
-\textbf{RQ 2:} How to solve the problem of fuzzy classification of projects with medium and high porting complexity in existing tools?
+\textbf{RQ 2:} \textcolor{red}{ How to implement fine-grained and automated tools to help developers accurately assess the complexity of their projects in real world.
+} \textcolor{blue}{How to solve the problem of fuzzy classification of projects with medium and high porting complexity in existing tools?}
 % \begin{figure}
@@
 % \end{figure}
+\textcolor{red}{As we all known, the metrics of projects complexity is influenced by many factors, such as XXX,XXX. To answer RQ 1, we introduce the code Cyclomatic Complexity(CC) and Arch\_code.}
 
-To answer RQ 1,this section provides a validity analysis of porting-related factors on RAX.
-First,we try to use code complexity metrics to evaluate porting work.
+\textcolor{blue}{To answer RQ 1, First, we try to use code complexity metrics to evaluate porting work.
 The software metrics of code Cyclomatic Complexity(CC) can help developers make macro judgments on software complexity and maintenance difficulty.
@@
 This part of the work has a lot of overlap with the scope of code complexity.Through our survey of community, we discovered that even though architectural code can be separated quite clearly from common code, when faced with large-scale projects, we still require numerous iterative tests to uncover unknown architectural code.
-Building upon this, we study the quantification of the significance of cyclomatic complexity in porting work.
+Building upon this, we study the quantification of the significance of cyclomatic complexity in porting work.}
 \begin{figure}

### 2024-01-29 Paper/latex1-27/paper.tex
Add files via upload

--- 2024-01-29 Paper/latex1-27/paper.tex
@@
 \end{itemize}
-% The remainder of this paper is organized as follows.In Section 2,we briefly analyze architecture-related factors.
+The remainder of this paper is organized as follows.In Section 2,we briefly analyze architecture-related factors.
 Section 3 presents the implementation and evaluation of RAX.
@@
 \section{Motivation}
-We propose the following research questions:
+To help developers more accurately assess the porting complexity of C/C++ projects, we aim to answer the following research questions:
 
@@
 
-\textbf{RQ 2:} How to solve the problem of fuzzy classification of projects with medium and high porting complexity in existing tools?
+\textbf{RQ 2:} How to implement fine-grained and automated tools to help developers accurately assess the complexity of their projects in real world?\\
+As we all known, the metrics of projects porting complexity is influenced by many factors, such as the scale of projects,the logical structure of the architectural code.
+To answer RQ 1, we introduce the code Cyclomatic Complexity(CC) and Arch\_code.
 % \begin{figure}
@@
 
-To answer RQ 1,this section provides a validity analysis of porting-related factors on RAX.
-First,we try to use code complexity metrics to evaluate porting work.
-The software metrics of code Cyclomatic Complexity(CC) can help developers make macro judgments on software complexity and maintenance difficulty.
+% To answer RQ 1,this section provides a validity analysis of porting-related factors on RAX.
+% First,we try to use code complexity metrics to evaluate porting work.
+% The software metrics of code Cyclomatic Complexity(CC) can help developers make macro judgments on software complexity and maintenance difficulty.
 By evaluating potential and hidden porting difficulties,code complexity helps the tool improve accuracy \cite{2005Exploring}.
-At present, CC indicators are mostly used in evaluating code quality, inspecting defect, reconstructing code, etc \cite{1991Cyclomatic}.
-During the porting process, developers will target a large number of project source codes,build scripts,assembly codes,and a macro understanding of the project is required in the early stage of porting.
-This part of the work has a lot of overlap with the scope of code complexity.Through our survey of community, we discovered that even though architectural code can be separated quite clearly from common code, when faced with large-scale projects, we still require numerous iterative tests to uncover unknown architectural code.
+% At present, CC indicators are mostly used in evaluating code quality, inspecting defect, reconstructing code, etc \cite{1991Cyclomatic}.
+% During the porting process, developers will target a large number of project source codes,build scripts,assembly codes,and a macro understanding of the project is required in the early stage of porting.
+% This part of the work has a lot of overlap with the scope of code complexity.Through our survey of community, we discovered that even though architectural code can be separated quite clearly from common code, when faced with large-scale projects, we still require numerous iterative tests to uncover unknown architectural code.
 Building upon this, we study the quantification of the significance of cyclomatic complexity in porting work.
@@
 \label{sec:factor-1}
-We use the lizard CC detection tool and optimize its functions,and it will introduce it in Section \ref{sec:Implementation}.
+First,we try to use code complexity metrics to evaluate porting work.
+CC can help developers make macro judgments on software complexity and maintenance difficulty.
+By evaluating potential porting difficulties,code complexity metrics helps the tool improve accuracy \cite{2005Exploring}.At present, CC indicators are mostly used in evaluating code quality, inspecting defect, reconstructing code, etc \cite{1991Cyclomatic}.
+During the porting process, developers will target a large number of project source codes,build scripts,assembly codes,and a macro understanding of the project is required in the early stage of porting.This part of the work has a lot of overlap with the scope of code complexity.Through our survey of community, we discovered that even though architectural code can be separated quite clearly from common code, when faced with large-scale projects, we still require numerous iterative tests to uncover unknown architectural code.
+Based on the above, we use the lizard CC detection tool and optimize its functions,and it will introduce it in Section \ref{sec:Implementation}.
 this section calculate the correlation coefficient using the Spearman Rank.

### 2024-01-29 Paper/latex1-27/paper.tex
update

@@
 \begin{table*}
-  \caption{Tool factors comparison}
+  \centering
+  \caption{Factors Among Different Tools}
+ %% \resizebox{0.48\textwidth}{!}{
   \label{tab:Tool}
@@
     \midrule
-   Other tool & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \XSolidBrush \\
+   Tool\textcolor{red}{\citep{2023du}} & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \XSolidBrush \\
     RAX & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold \\
@@
 \end{tabular}
+ %% }
 \end{table*}
@@
 \section{RAX}
-The following is an introduction to the process of RAX construction, as shown in Figure \ref{fig:figure1}.
-During the analysis phase,architecture-related factors are obtained through the Commit tool for selection while investigating the impact of code complexity metrics on porting.
-A scanning tool is built to get potential modification workload.
-Finally,an appropriate machine learning model is selected as a classification.
+\textcolor{red}{Since we identify architecture-relevant important
+factors affecting porting efficiency, we implement a fine-grained and automated tool to evaluate complexity.
+Figure \ref{fig:figure1} shows the entire technology roadmap in three parts such as Analysis, Data Collection and Evaluation.
+RAX can be deployed }
+\textcolor{blue}{The following is an introduction to the process of RAX construction, as shown in Figure \ref{fig:figure1}.
+During the analysis phase,architecture\-related factors are obtained through the Commit tool for selection while investigating the impact of code complexity metrics on porting.
+A scanning tool is built to get potential modification workload. Finally,an appropriate machine learning model is selected as a classification.}
+
 \begin{figure}
@@
   \includegraphics[width=\linewidth]{figure1.pdf}
-  \caption{Flow chart for method to build RAX}
+  \caption{Flow Chart of RAX}
   \label{fig:figure1}

### 2024-01-29 Paper/latex1-27/paper.tex
Add files via upload

@@
 \section{RAX}
-\textcolor{red}{Since we identify architecture-relevant important
+Since we identify architecture-relevant important
 factors affecting porting efficiency, we implement a fine-grained and automated tool to evaluate complexity.
 Figure \ref{fig:figure1} shows the entire technology roadmap in three parts such as Analysis, Data Collection and Evaluation.
-RAX can be deployed }
-\textcolor{blue}{The following is an introduction to the process of RAX construction, as shown in Figure \ref{fig:figure1}.
-During the analysis phase,architecture\-related factors are obtained through the Commit tool for selection while investigating the impact of code complexity metrics on porting.
-A scanning tool is built to get potential modification workload. Finally,an appropriate machine learning model is selected as a classification.}
+RAX can be deployed easily by installing dependencies, highlighting its convenience and user-friendliness.
+% \textcolor{blue}{The following is an introduction to the process of RAX construction, as shown in Figure \ref{fig:figure1}.
+% During the analysis phase,architecture\-related factors are obtained through the Commit tool for selection while investigating the impact of code complexity metrics on porting.
+% A scanning tool is built to get potential modification workload. Finally,an appropriate machine learning model is selected as a classification.}
 
@@
 \label{sec:Implementation}
-RAX obtains porting complexity vector through the CC calculation method and Arch\_code statistical value.
+% RAX obtains porting complexity vector through the CC calculation method and Arch\_code statistical value.
+\subsubsection{Analysis}
+We intend to use the Lizard tool, which employs a methodology consistent with the McCabe's method\cite{1702388}, to obtain CC metrics.
+However, Lizard tool only defects at the function level and uses the average function CC for file-level statistics, which is not suitable for current porting complexity detection requirements \cite{9402593}.We need to redefine the CC method to avoid the use of complex methods, which will cause deviations to affect the classification results.Additionally, we must address the potential performance overhead problem caused by converting the entire project into abstract syntax tree.\\
+Other tools only consider x86 architecture to locate architecture-related code for statistical analysis.
+We propose a new idea that explore whether multiple architectures can be selected or if other architectures can be individually targeted.
+Based on this, we conducted comparative experiments using various architectures, including X86, ARM, MIPS, RISCV, SPARC, and PowerPC.
+We performed scanning and counting based on the keyword and function dictionaries specific to each architecture, which were derived from common patterns summarized by official websites.
+By analyzing the correlation coefficient (Pearson's) between the keyword coverage line statistics of the six architectures and the score representing the porting complexity, we found that the correlation ranged from 0.44 to 0.58, indicating all correlation results are not significant.
+Additionally, the correlation between the total values for all architectures and score was only 0.49.
+Based on these results, analyze that our tool try to effectively assess the porting difficulty between two architectures.
+It is not as simple as adding up the modification amounts for different architectures, as it may only reflect an increase in code volume.
+Moreover, due to the large differences in row-based statistical results caused by the differences in code structure reflected by each architecture, this approach that easily considers all architectures simultaneously without considering the code structure and architectural weight lead to ambiguous outcomes.Therefore, based on these experiments, we still select x86 to build Arch\_code scan function, given its mainstream position.
+\subsubsection{Dataset Collection}
+We used the project upstream warehouse to build the data set,which mainly targeting C and C++ are from the OpenEu-ler list and GitHub,and invited 5 postgraduate students who are engaged in the research of RISC-V porting auxiliary tools to participate in the experimental evaluation.Specific evaluation methods can be found in \ref{sec:factor-1}.
+The evaluation scores are divided into three categories: low, medium, and high\citep{githuburl}.This includes 139 projects as training, testing, and validation datasets, while 72 additional projects were used as a tool effectiveness evaluation dataset.
+To gather insights from developers, the community, forums, and emails were utilized, resulting in over 51 meaningful feedback responses.
+In order to address the issue of data imbalance caused by collecting datasets solely from the openEuler mailing list, where more than 80\% of the projects were initially evaluated as having low porting complexity, a greater emphasis was placed on projects that had higher numbers of likes on GitHub and were deemed more important and active.
+Additionally, efforts were made to collect projects from the system bottom such as operating systems, kernel-level projects,mathematical computation libraries,and machine learning libraries.
 
-\subsubsection{Lizard CC calculation scan function}
-Lizard's default computing method is basically consistent with McCabe's theory \cite{1702388}.
-However, Lizard tool only defects at the function level and uses the average function CC for file-level statistics, which is not suitable for current porting complexity detection requirements \cite{9402593}.
-This paper proposes a new method:
-
-First, we calculate the function-level CC for all files in the project using McCabe's method.Following Liu's mention of System Cyclomatic Complexity (SCC) in software evolution assessment techniques based on code change detection \cite{liuhuihui00}, we define SCC as the total sum of function-level values in the system.
-  The advantage is that it can avoid the use of complex methods, which will cause deviations to affect the classification results.
-  Additionally,due to the system's complexity being calculated based on a single function,it eliminates the problem of decreased detection performance caused by the conversion of such a large code structure of all modules into into abstract syntax tree and control flow graphs.
+\subsubsection{Implementation of RAX Tool}
+RAX obtains porting complexity vector through the CC calculation method and Arch\_code statistical value.\\
+This paper proposes a new CC method:
+ First, we calculate the function-level CC for all files in the project using McCabe's method.
+Following Liu's mention of System Cyclomatic Complexity (SCC) in software evolution assessment techniques based on code change detection \cite{liuhuihui00}, we define SCC as the total sum of function-level values in the system.
   Our CC calculation approach is expressed by equation (1) to (3),where lowercase cc represents the cyclomatic complexity at the function or file level.The uppercase CC represents the overall cyclomatic complexity of the software package,serving as a crucial factor in our tool.Here, |E| denotes the number of edges in the function control flow graph,and |N| represents the number of nodes.The function control flow graph is constructed based on branching structures such as if, while, and switch statements.
@@
         \end{equation}
-
-\subsubsection{Arch\_code scan function}
-Other tools only consider x86 architecture to locate architecture-related code for statistical analysis.
-We propose a new idea that explore whether multiple architectures can be selected or if other architectures can be individually targeted.
-Based on this, we conducted comparative experiments using various architectures, including X86, ARM, MIPS, RISCV, SPARC, and PowerPC.
-We performed scanning and counting based on the keyword and function dictionaries specific to each architecture, which were derived from common patterns summarized by official websites.
-By analyzing the correlation coefficient (Pearson's) between the keyword coverage line statistics of the six architectures and the score representing the porting complexity, we found that the correlation ranged from 0.44 to 0.58, indicating all correlation results are not significant.
-Additionally, the correlation between the total values for all architectures and score was only 0.49.
-Based on these results, analyze that our tool try to effectively assess the porting difficulty between two architectures.
-It is not as simple as adding up the modification amounts for different architectures, as it may only reflect an increase in code volume.
-Moreover, due to the large differences in row-based statistical results caused by the differences in code structure reflected by each architecture, this approach that easily considers all architectures simultaneously without considering the code structure and architectural weight lead to ambiguous outcomes.Therefore, based on these experiments, we still select x86 to build Arch\_code scan function, given its mainstream position.
-
 We form the Arch\_code dictionary:
@@
   (5)\textit{Buildscripts} We locate architecture keywords in the build scripts.
+
+% \subsubsection{Arch\_code scan function}
+% Other tools only consider x86 architecture to locate architecture-related code for statistical analysis.
+We propose a new idea that explore whether multiple architectures can be selected or if other architectures can be individually targeted.
+Based on this, we conducted comparative experiments using various architectures, including X86, ARM, MIPS, RISCV, SPARC, and PowerPC.
+We performed scanning and counting based on the keyword and function dictionaries specific to each architecture, which were derived from common patterns summarized by official websites.
+% By analyzing the correlation coefficient (Pearson's) between the keyword coverage line statistics of the six architectures and the score representing the porting complexity, we found that the correlation ranged from 0.44 to 0.58, indicating all correlation results are not significant.
+Additionally, the correlation between the total values for all architectures and score was only 0.49.
+% Based on these results, analyze that our tool try to effectively assess the porting difficulty between two architectures.
+It is not as simple as adding up the modification amounts for different architectures, as it may only reflect an increase in code volume.
+Moreover, due to the large differences in row-based statistical results caused by the differences in code structure reflected by each architecture, this approach that easily considers all architectures simultaneously without considering the code structure and architectural weight lead to ambiguous outcomes.Therefore, based on these experiments, we still select x86 to build Arch\_code scan function, given its mainstream position.
+
+% We form the Arch\_code dictionary:
+% (1)\textit{Conditional compilation and architecture macros} Use conditional compilation statements, such as ``\texttt{if defined}'', ``\texttt{ifdef}'', in conjunction with all possible architecture macros,
+%   ``\texttt{\_\_x86\_64\_\_}''.
+%   We use an algorithm similar to bracket matching to cover all the code within macros, avoiding the impact of nested layers.
+%   (2)\textit{Assembly} We use matching forms such as ``\texttt{\_\_asm\_\_}'' and ``\texttt{\_\_volatile\_\_}''.
+%   In future work,we will consider striving to achieve the currently unachievable architecture identification function of assembly code and identify assembly code in the form of instructions;
+%   (3)\textit{Intrinsic and Builtin} 
+%   We compile dictionaries of Intrinsic and Builtin functions based on official documentation from x86\cite{x86intrin}.In the future,we may assign difficulty weights to them.
+%   (4)\textit{System calls} Considering glibc's support for system call encapsulation, reorganize the sys-call dictionary.
+%   The system calls that do not support RISC-V have been filtered and collected currently.
+%   (5)\textit{Buildscripts} We locate architecture keywords in the build scripts.
 

### 2024-01-29 Paper/latex1-27/paper.tex
Add files via upload

@@
     \midrule
-   Tool\textcolor{red}{\citep{2023du}} & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \XSolidBrush \\
+   Tool\citep{2023du} & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \XSolidBrush \\
     RAX & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold \\
@@
 \subsubsection{Dataset Collection}
-We used the project upstream warehouse to build the data set,which mainly targeting C and C++ are from the OpenEu-ler list and GitHub,and invited 5 postgraduate students who are engaged in the research of RISC-V porting auxiliary tools to participate in the experimental evaluation.Specific evaluation methods can be found in \ref{sec:factor-1}.
+% We used the project upstream warehouse to build the data set,which mainly targeting C and C++ are from the OpenEu-ler list and GitHub,and invited 5 postgraduate students who are engaged in the research of RISC-V porting auxiliary tools to participate in the experimental evaluation.Specific evaluation methods can be found in \ref{sec:factor-1}.
 The evaluation scores are divided into three categories: low, medium, and high\citep{githuburl}.This includes 139 projects as training, testing, and validation datasets, while 72 additional projects were used as a tool effectiveness evaluation dataset.
 To gather insights from developers, the community, forums, and emails were utilized, resulting in over 51 meaningful feedback responses.
-In order to address the issue of data imbalance caused by collecting datasets solely from the openEuler mailing list, where more than 80\% of the projects were initially evaluated as having low porting complexity, a greater emphasis was placed on projects that had higher numbers of likes on GitHub and were deemed more important and active.
+We used the project upstream warehouse to build the data set,which mainly targeting C and C++ are from the OpenEuler list and GitHub\citep{stage2023}.In order to address the issue of data imbalance caused by collecting datasets solely from the openEuler mailing list, where more than 80\% of the projects were initially evaluated as having low porting complexity, a greater emphasis was placed on projects that had higher numbers of likes on GitHub and were deemed more important and active.
 Additionally, efforts were made to collect projects from the system bottom such as operating systems, kernel-level projects,mathematical computation libraries,and machine learning libraries.
@@
 \subsubsection{Dataset}
-We used the project upstream warehouse to build the data set,which mainly targeting C and C++ are from the OpenEu-ler list and GitHub,and invited 5 postgraduate students who are engaged in the research of RISC-V porting auxiliary tools to participate in the experimental evaluation.Specific evaluation methods can be found in \ref{sec:factor-1}.
-The evaluation scores are divided into three categories: low, medium, and high\citep{githuburl}.This includes 139 projects as training, testing, and validation datasets, while more than 70 additional projects were used as a tool effectiveness evaluation dataset.
-To gather insights from developers, the community, forums, and emails were utilized, resulting in over 51 meaningful feedback responses.
-In order to address the issue of data imbalance caused by collecting datasets solely from the openEuler mailing list, where more than 80\% of the projects were initially evaluated as having low porting complexity, a greater emphasis was placed on projects that had higher numbers of likes on GitHub and were deemed more important and active.
-Additionally, efforts were made to collect projects from the system bottom such as operating systems, kernel-level projects,mathematical computation libraries,and machine learning libraries to address RQ 2.
+ To evaluate RAX, We chose typical and popular C and C++ projects from upstream warehouse of the OpenEuler and GitHub\citep{stage2023}.
+First, we searched keywords "rv" or "riscv" and collected 139 projects as our training and testing dataset.
+Then, five postgraduate students are invited to tag the porting auxiliary for these projects.
+The evaluation scores are divided into three categories:low, medium, and high\citep{githubss}.
+Second, models are trained and tested based on the 139 projects.
+Third, to evaluate the RAX, additional 72 projects are collected and evaluated from GitHub.
+To gather response from developers, the community, forums, and emails were utilized.
 \subsubsection{Result and Analysis}

### 2024-01-29 Paper/latex1-27/paper.tex
Add files via upload

@@
 \section{Motivation}
+\label{sec:factor}
 To help developers more accurately assess the porting complexity of C/C++ projects, we aim to answer the following research questions:
@@
   \includegraphics[width=\linewidth]{figure2.pdf}
-  \caption{The relationship between score and CC}
+  \caption{The Relationship between Score and CC}
   \label{fig:figure2}
-  \Description{The relationship between score and CC}
+  \Description{The Relationship between Score and CC}
 \end{figure}
@@
 First,we try to use code complexity metrics to evaluate porting work.
-CC can help developers make macro judgments on software complexity and maintenance difficulty.
-By evaluating potential porting difficulties,code complexity metrics helps the tool improve accuracy \cite{2005Exploring}.At present, CC indicators are mostly used in evaluating code quality, inspecting defect, reconstructing code, etc \cite{1991Cyclomatic}.
-During the porting process, developers will target a large number of project source codes,build scripts,assembly codes,and a macro understanding of the project is required in the early stage of porting.This part of the work has a lot of overlap with the scope of code complexity.Through our survey of community, we discovered that even though architectural code can be separated quite clearly from common code, when faced with large-scale projects, we still require numerous iterative tests to uncover unknown architectural code.
-Based on the above, we use the lizard CC detection tool and optimize its functions,and it will introduce it in Section \ref{sec:Implementation}.
+CC can help developers make macro judgments on software complexity and maintenance difficulty,and helps the tool improve accuracy \cite{2005Exploring}.
+% At present, CC indicators are mostly used in evaluating code quality, inspecting defect, reconstructing code, etc \cite{1991Cyclomatic}.
+During the porting process, developers will target a large number of project source codes,and a macro understanding of the project is required in the early stage of porting.This part of the work has a lot of overlap with the scope of code complexity.Through our survey of community, we discovered that even though architectural code can be separated quite clearly from common code, when faced with large-scale projects, we still require numerous iterative tests to uncover unknown architectural code.
+Based on the above, we use the lizard CC detection tool and optimize its functions.This paper proposes a new CC method:
+ First, we calculate the function-level CC for all files in the project using McCabe's method.
+Following Liu's mention of System Cyclomatic Complexity (SCC) in software evolution assessment techniques based on code change detection \cite{liuhuihui00}, we define SCC as the total sum of function-level values in the system.
+  Our CC calculation approach is expressed by equation (1) to (3),where lowercase cc represents the cyclomatic complexity at the function or file level.The uppercase CC represents the overall cyclomatic complexity of the software package,serving as a crucial factor in our tool.Here, |E| denotes the number of edges in the function control flow graph,and |N| represents the number of nodes.The function control flow graph is constructed based on branching structures such as if, while, and switch statements.
+
+  \begin{equation}
+    {cc}({function}) = \lvert E \rvert - \lvert N \rvert + 2
+    % \sum_{i=1}^{n} x_i
+    \end{equation}
+    \begin{equation}
+      {cc}({file}) =  \sum_{i=1}^{n} 
+      {cc}({function})
+      \end{equation}
+      \begin{equation}
+        {CC} =  \sum_{i=1}^{k} {cc}({file})
+        \end{equation}
 this section calculate the correlation coefficient using the Spearman Rank.
@@
 Second, we consider the effectiveness of the architecture-related code structure proposed by other tool and conduct comparative experiments using more potential factors.
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figure3.pdf}
+  \caption{The Heat Map of Pearson Correlation}
+  \label{fig:figure3}
+  \Description{The Correlation}
+\end{figure}
 \subsection{Factor2:Arch\_code}
@@
 We use an automated tool to obtain statistics of lines and frequencies of Arch\_code.
+We form the Arch\_code dictionary:
+(1)\textit{Conditional compilation and architecture macros} Use conditional compilation statements, such as ``\texttt{if defined}'', ``\texttt{ifdef}'', in conjunction with all possible architecture macros,
+  ``\texttt{\_\_x86\_64\_\_}''.
+  We use an algorithm similar to bracket matching to cover all the code within macros, avoiding the impact of nested layers.
+  (2)\textit{Assembly} We use matching forms such as ``\texttt{\_\_asm\_\_}'' and ``\texttt{\_\_volatile\_\_}''.
+  In future work,we will consider striving to achieve the currently unachievable architecture identification function of assembly code;
+  (3)\textit{Intrinsic and Builtin} 
+  We compile dictionaries of Intrinsic and Builtin functions based on official documentation from x86\cite{x86intrin}.In the future,we may assign difficulty weights to them.
+  (4)\textit{System calls} The system calls that do not support RISC-V have been filtered and collected currently.
+  (5)\textit{Buildscripts} We locate architecture keywords in the build scripts.
 
@@
 
-Figure \ref{fig:figure3} shows the correlation comparison between Arch\_code,CC and other factors acquired by Commit analyzer:
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figure3.pdf}
-  \caption{The heat map of pearson correlation}
-  \label{fig:figure3}
-  \Description{The Correlation}
-\end{figure}
-The results indicate that Arch\_code and CC has a higher correlation with score compared to other factors, and we use Peason correlation method to build the heat map.
+Figure \ref{fig:figure3} shows the correlation comparison between Arch\_code,CC and other factors acquired by Commit analyzer:The results indicate that Arch\_code and CC has a higher correlation with score compared to other factors, and we use Peason correlation method to build the heat map.
 The use of only architecture keywords for statistics yields moderate effectiveness because keywords can only be detected from comments and macro sections of Git commits, while critical porting code may lack these keywords,but the number of keywords can reflect the amount of porting modification from the side.
@@
 factors affecting porting efficiency, we implement a fine-grained and automated tool to evaluate complexity.
-Figure \ref{fig:figure1} shows the entire technology roadmap in three parts such as Analysis, Data Collection and Evaluation.
+Figure \ref{fig:figure1} shows the entire technology roadmap in three parts such as Analysis, Data Collection and {Evaluation.
 RAX can be deployed easily by installing dependencies, highlighting its convenience and user-friendliness.
@@
   \label{fig:figure1}
-  \Description{Flow chart for method to build RAX}
+  \Description{Flow Chart for Method to Build RAX}
 \end{figure}
@@
 To gather insights from developers, the community, forums, and emails were utilized, resulting in over 51 meaningful feedback responses.
-We used the project upstream warehouse to build the data set,which mainly targeting C and C++ are from the OpenEuler list and GitHub\citep{stage2023}.In order to address the issue of data imbalance caused by collecting datasets solely from the openEuler mailing list, where more than 80\% of the projects were initially evaluated as having low porting complexity, a greater emphasis was placed on projects that had higher numbers of likes on GitHub and were deemed more important and active.
+We used the project upstream warehouse to build the data set,which mainly targeting C and C++ are from the OpenEuler list and GitHub\citep{stage2023}.We obtain the complexity vector through the designed method \ref{sec:factor}.In order to address the issue of data imbalance caused by collecting datasets solely from the openEuler mailing list, where more than 80\% of the projects were initially evaluated as having low porting complexity, a greater emphasis was placed on projects that had higher numbers of likes on GitHub and were deemed more important and active.
 Additionally, efforts were made to collect projects from the system bottom such as operating systems, kernel-level projects,mathematical computation libraries,and machine learning libraries.
 
-\subsubsection{Implementation of RAX Tool}
-RAX obtains porting complexity vector through the CC calculation method and Arch\_code statistical value.\\
-This paper proposes a new CC method:
- First, we calculate the function-level CC for all files in the project using McCabe's method.
+\subsubsection{Evaluation}
+% RAX obtains porting complexity vector through the CC calculation method and Arch\_code statistical value.\\
+% This paper proposes a new CC method:
+%  First, we calculate the function-level CC for all files in the project using McCabe's method.
 Following Liu's mention of System Cyclomatic Complexity (SCC) in software evolution assessment techniques based on code change detection \cite{liuhuihui00}, we define SCC as the total sum of function-level values in the system.
-  Our CC calculation approach is expressed by equation (1) to (3),where lowercase cc represents the cyclomatic complexity at the function or file level.The uppercase CC represents the overall cyclomatic complexity of the software package,serving as a crucial factor in our tool.Here, |E| denotes the number of edges in the function control flow graph,and |N| represents the number of nodes.The function control flow graph is constructed based on branching structures such as if, while, and switch statements.
+%   Our CC calculation approach is expressed by equation (1) to (3),where lowercase cc represents the cyclomatic complexity at the function or file level.The uppercase CC represents the overall cyclomatic complexity of the software package,serving as a crucial factor in our tool.Here, |E| denotes the number of edges in the function control flow graph,and |N| represents the number of nodes.The function control flow graph is constructed based on branching structures such as if, while, and switch statements.
 
-  \begin{equation}
-    {cc}({function}) = \lvert E \rvert - \lvert N \rvert + 2
-    % \sum_{i=1}^{n} x_i
-    \end{equation}
-    \begin{equation}
-      {cc}({file}) =  \sum_{i=1}^{n} 
-      {cc}({function})
-      \end{equation}
-      \begin{equation}
-        {CC} =  \sum_{i=1}^{k} {cc}({file})
-        \end{equation}
-We form the Arch\_code dictionary:
-(1)\textit{Conditional compilation and architecture macros} Use conditional compilation statements, such as ``\texttt{if defined}'', ``\texttt{ifdef}'', in conjunction with all possible architecture macros,
-  ``\texttt{\_\_x86\_64\_\_}''.
-  We use an algorithm similar to bracket matching to cover all the code within macros, avoiding the impact of nested layers.
-  (2)\textit{Assembly} We use matching forms such as ``\texttt{\_\_asm\_\_}'' and ``\texttt{\_\_volatile\_\_}''.
-  In future work,we will consider striving to achieve the currently unachievable architecture identification function of assembly code and identify assembly code in the form of instructions;
-  (3)\textit{Intrinsic and Builtin} 
-  We compile dictionaries of Intrinsic and Builtin functions based on official documentation from x86\cite{x86intrin}.In the future,we may assign difficulty weights to them.
-  (4)\textit{System calls} Considering glibc's support for system call encapsulation, reorganize the sys-call dictionary.
-  The system calls that do not support RISC-V have been filtered and collected currently.
-  (5)\textit{Buildscripts} We locate architecture keywords in the build scripts.
+%   \begin{equation}
+%     {cc}({function}) = \lvert E \rvert - \lvert N \rvert + 2
+%     % \sum_{i=1}^{n} x_i
+%     \end{equation}
+%     \begin{equation}
+%       {cc}({file}) =  \sum_{i=1}^{n} 
+%       {cc}({function})
+%       \end{equation}
+%       \begin{equation}
+%         {CC} =  \sum_{i=1}^{k} {cc}({file})
+%         \end{equation}
+% We form the Arch\_code dictionary:
+% (1)\textit{Conditional compilation and architecture macros} Use conditional compilation statements, such as ``\texttt{if defined}'', ``\texttt{ifdef}'', in conjunction with all possible architecture macros,
+%   ``\texttt{\_\_x86\_64\_\_}''.
+%   We use an algorithm similar to bracket matching to cover all the code within macros, avoiding the impact of nested layers.
+%   (2)\textit{Assembly} We use matching forms such as ``\texttt{\_\_asm\_\_}'' and ``\texttt{\_\_volatile\_\_}''.
+%   In future work,we will consider striving to achieve the currently unachievable architecture identification function of assembly code and identify assembly code in the form of instructions;
+%   (3)\textit{Intrinsic and Builtin} 
+%   We compile dictionaries of Intrinsic and Builtin functions based on official documentation from x86\cite{x86intrin}.In the future,we may assign difficulty weights to them.
+%   (4)\textit{System calls} Considering glibc's support for system call encapsulation, reorganize the sys-call dictionary.
+%   The system calls that do not support RISC-V have been filtered and collected currently.
+%   (5)\textit{Buildscripts} We locate architecture keywords in the build scripts.
+In our study, we opted to utilize Random Forest machine learning model for conducting training and testing to obtain the final classifier model.
+The extended dataset was used as an additional input for the classifier to acquire evaluation results.
+We subsequently performed evaluations on 72 projects and sought community feedback during the tool's effectiveness evaluation phase.
 
@@
 \subsubsection{Result and Analysis}
-To answer RQ 2, based on the work of Chen Xiang et al.
-\cite{5128907}, aiming at the status quo of unbalanced datasets and small sample datasets, we try to use ensemble learning methods \cite{6509481}, SMOTE \cite{4271036}, and random oversampling methods for data preprocessing.
-Ultimately, we chose to train four models: Random Forest, Support Vector Machine, Adaboost, and Xgboost.
+We used ensemble learning methods \cite{6509481}, SMOTE \cite{4271036}, and random oversampling methods for data preprocessing\cite{5128907} addressing the problem of unbalanced datasets and small sample datasets.
+% Ultimately, we chose to train four models:Random Forest, Support Vector Machine, Adaboost, and Xgboost.
 By comparing multiple indicators, we select the Random Forest machine learning model as the classifier, as shown in Table \ref{tab:evaluation}.
@@
 \begin{table}
-  \caption{Experimental results of models}
+  \caption{Experimental Results of Models}
   \label{tab:evaluation}
@@
 \begin{table}
-  \caption{Tool effectiveness comparison from community feedback}
+  \caption{Tool Effectiveness Comparison from Community Feedback}
   \label{tab:effectiveness}
@@
 Vard et al. \cite{2017Evaluating} emphasized that the internal quality of software impacts developers' capabilities and maintenance duration.
-They conducted a comprehensive study on various existing code complexity metrics' validity and suggested incorporating empirically observed code features as complexity triggers.We have pioneered the application of code complexity metrics in the domain of porting assessment, while existing research primarily focuses on code refactoring and defect detection\cite{1993Software}.
+They conducted a comprehensive study on various existing code complexity metrics' validity and suggested incorporating empirically observed code features as complexity triggers.We have pioneered the application of code complexity metrics in the domain of porting assessment, while existing research primarily focuses on code refactoring and defect detection\cite{1993Software},\cite{1991Cyclomatic}.
 \section{Conclusion}

### 2024-01-29 Paper/latex1-27/paper.tex
update

@@
 \section{RAX}
-Since we identify architecture-relevant important
-factors affecting porting efficiency, we implement a fine-grained and automated tool to evaluate complexity.
+Since we identify architecture-relevant important factors affecting porting efficiency, we implement a fine-grained and automated tool to evaluate complexity.
 Figure \ref{fig:figure1} shows the entire technology roadmap in three parts such as Analysis, Data Collection and {Evaluation.
 RAX can be deployed easily by installing dependencies, highlighting its convenience and user-friendliness.
+
 % \textcolor{blue}{The following is an introduction to the process of RAX construction, as shown in Figure \ref{fig:figure1}.
@@
 To gather insights from developers, the community, forums, and emails were utilized, resulting in over 51 meaningful feedback responses.
-We used the project upstream warehouse to build the data set,which mainly targeting C and C++ are from the OpenEuler list and GitHub\citep{stage2023}.We obtain the complexity vector through the designed method \ref{sec:factor}.In order to address the issue of data imbalance caused by collecting datasets solely from the openEuler mailing list, where more than 80\% of the projects were initially evaluated as having low porting complexity, a greater emphasis was placed on projects that had higher numbers of likes on GitHub and were deemed more important and active.
+
+We used the project upstream warehouse to build the data set,which mainly targeting C and C++ are from the OpenEuler list and GitHub\citep{stage2023}.In order to address the issue of data imbalance caused by collecting datasets solely from the openEuler mailing list, where more than 80\% of the projects were initially evaluated as having low porting complexity, a greater emphasis was placed on projects that had higher numbers of likes on GitHub and were deemed more important and active.
 Additionally, efforts were made to collect projects from the system bottom such as operating systems, kernel-level projects,mathematical computation libraries,and machine learning libraries.
+It is worth emphasizing that, all these projects' complexity evaluated by RAX hoped to be verified  by the own developer of projects.
 
@@
 \subsubsection{Result and Analysis}
-We used ensemble learning methods \cite{6509481}, SMOTE \cite{4271036}, and random oversampling methods for data preprocessing\cite{5128907} addressing the problem of unbalanced datasets and small sample datasets.
+To solve the problem of unbalanced datasets and small sample datasets, we used ensemble learning methods \cite{6509481}, SMOTE \cite{4271036}, and random oversampling methods for data preprocessing\cite{5128907} addressing.
 % Ultimately, we chose to train four models:Random Forest, Support Vector Machine, Adaboost, and Xgboost.
-By comparing multiple indicators, we select the Random Forest machine learning model as the classifier, as shown in Table \ref{tab:evaluation}.
+%By comparing multiple indicators, we select the Random Forest machine learning model as the classifier, as shown in Table \ref{tab:evaluation}.
+
+%To answer RQ 2, based on the work of Chen Xiang et al.
+\cite{5128907}, aiming at the status quo of unbalanced datasets and small sample datasets, we try to use ensemble learning methods \cite{6509481}, SMOTE \cite{4271036}, and random oversampling methods for data preprocessing.
+%Ultimately, we chose to train four models: Random Forest, Support Vector Machine, Adaboost, and Xgboost.
+By comparing multiple indicators, we select the Random Forest\textcolor{red}{, which had the highest accuracy of 0.857} as the classifier, as shown in Table \ref{tab:evaluation}.
 
@@
 
-We continued to expand 72 projects as a supplementary data set, and the prediction results were determined through comments from the community and forum.
-Github presents comparison\cite{githubss} with the porting complexity evaluation tool developed by Du et al.
-across various projects, the comparison results are shown in Table \ref{tab:effectiveness}.Through real-world evaluations within the developer community, our tool has exhibited a significant improvement in accuracy, surpassing other comparable tools by a margin of 15.6\%.
-In Github, we provide a comprehensive compilation of the community's valuable feedback comments, accompanied by the relevant web links for further reference and validation.
+We provide a comprehensive compilation of the community's valuable feedback comments, accompanied by the relevant web links for further reference and validation \textcolor{red}{ shown in \cite{githubss} and Table \ref{tab:effectiveness}.
+Our experiments shows that, compared with other tool, RAX is more accurately to evaluate projects' complexity.
+In detail, the true positive (TP) of other tool is 39/51, while the RAX is 47/51.
+At the same time, the RAX has a lower rate of false positive (FN) than other tools.
+The values are 4/51 and 12/51, respectively.
+} Through real-world evaluations within the developer community, our tool has exhibited a significant improvement in accuracy, surpassing other comparable tools by a margin of 15.6\%.
 

### 2024-01-29 Paper/latex1-27/paper.tex
update
Add files via upload

@@
 \subsubsection{Result and Analysis}
-To solve the problem of unbalanced datasets and small sample datasets, we used ensemble learning methods \cite{6509481}, SMOTE \cite{4271036}, and random oversampling methods for data preprocessing\cite{5128907} addressing.
-% Ultimately, we chose to train four models:Random Forest, Support Vector Machine, Adaboost, and Xgboost.
-%By comparing multiple indicators, we select the Random Forest machine learning model as the classifier, as shown in Table \ref{tab:evaluation}.
-
-%To answer RQ 2, based on the work of Chen Xiang et al.
-\cite{5128907}, aiming at the status quo of unbalanced datasets and small sample datasets, we try to use ensemble learning methods \cite{6509481}, SMOTE \cite{4271036}, and random oversampling methods for data preprocessing.
-%Ultimately, we chose to train four models: Random Forest, Support Vector Machine, Adaboost, and Xgboost.
-By comparing multiple indicators, we select the Random Forest\textcolor{red}{, which had the highest accuracy of 0.857} as the classifier, as shown in Table \ref{tab:evaluation}.
+To solve the problem of unbalanced datasets and small sample datasets, we used ensemble learning methods \cite{6509481}, SMOTE \cite{4271036}, and random oversampling methods for data preprocessing\cite{5128907} addressing.By comparing multiple indicators, we select the Random Forest, which had the highest accuracy of 0.857 as the classifier, as shown in Table \ref{tab:evaluation}.
 
@@
 
-We provide a comprehensive compilation of the community's valuable feedback comments, accompanied by the relevant web links for further reference and validation \textcolor{red}{ shown in \cite{githubss} and Table \ref{tab:effectiveness}.
+We provide a comprehensive compilation of the community's valuable feedback comments, accompanied by the relevant web links for further reference and validation shown in \cite{githubss} and Table \ref{tab:effectiveness}.
 Our experiments shows that, compared with other tool, RAX is more accurately to evaluate projects' complexity.
@@
 The values are 4/51 and 12/51, respectively.
-} Through real-world evaluations within the developer community, our tool has exhibited a significant improvement in accuracy, surpassing other comparable tools by a margin of 15.6\%.
+Through real-world evaluations within the developer community, our tool has exhibited a significant improvement in accuracy, surpassing other comparable tools by a margin of 15.6\%.
 
@@
 Another reason is that we have added more medium or difficult complex samples to the data set to increase robustness and improve the innovativeness of the tool.
-
 Within evaluation, there are instances of inaccurate predictions.
@@
 In response to valuable suggestions from developers within the OpenEuler community, we conducted an evaluation of the porting complexity for various versions of the Chromium.Initially, we were able to accurately assess the porting complexity, yielding promising results.
-However, when it came to evaluating the work involved in iterative updates between versions, existing tools proved insufficient for precise estimation.Sometimes developers design their work with generic code for unknown architecture and CPU architecture parts are well separated from the common code,that just need only to adjust the moderate amount of code to recognize RISC-V,like nuttx.
+However, when it came to evaluating the work involved in iterative updates between versions, existing tools proved insufficient for precise estimation.Sometimes CPU architecture parts in projects are well separated from the common code,that just need only to adjust the moderate amount of code to recognize RISC-V,like nuttx.
 \section{Related Work}
@@
 We verified the effectiveness of the evaluation of 51 extension projects in real porting scenarios through their respective communities or forums.
-Observed significant performance improvements compared to existing tools.Moreover, RAX provides developers with the functionality to locate target code segments.Our next steps involve attempting text classification methods to categorize the text results of the original tool, designing more granular statistical methods for architecture-related factors.
+Observed significant performance improvements compared to existing tools.Moreover, RAX provides developers with the functionality to locate target code segments.Our next steps involve attempting text classification methods and designing more granular statistical methods for architecture-related factors.
 %%

### 2024-01-29 Paper/latex1-27/paper.tex
Add files via upload

@@
 complexity evaluation tool which accurately locates the CPU architecture code and calculates the code complexity of the software.The contributions of this paper are as follows:
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figure2.pdf}
+  \caption{The Relationship between Score and CC}
+  \label{fig:figure2}
+  \Description{The Relationship between Score and CC}
+\end{figure}
 \begin{itemize}
@@
 Building upon this, we study the quantification of the significance of cyclomatic complexity in porting work.
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figure2.pdf}
-  \caption{The Relationship between Score and CC}
-  \label{fig:figure2}
-  \Description{The Relationship between Score and CC}
-\end{figure}
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=\linewidth]{figure2.pdf}
+%   \caption{The Relationship between Score and CC}
+%   \label{fig:figure2}
+%   \Description{The Relationship between Score and CC}
+% \end{figure}
 \subsection{Factor 1: Cyclomatic Complex(CC)}
@@
 \end{figure}
-\subsection{Factor2:Arch\_code}
+\subsection{Factor 2:Arch\_code}
 
@@
 \begin{table}
-  \caption{Experimental Results of Models}
+  \caption{Results of Different Evaluation Tool}
   \label{tab:evaluation}
@@
 
-After adding the code complexity factor and modifying the original model, RAX's result prediction accuracy is improved.
-This is because code complexity can clearly distinguish three types of porting difficulty.
-Motivation Chapters present the cause analysis.
-Adding factors also makes RAX more robust and more friendly to projects with unbalanced complexity vectors.
+We conducted an in-depth analysis of the essential reasons for the improvement in accuracy after adding CC factors.This is because code complexity can clearly distinguish three types of porting difficulty.Adding factors also makes RAX more robust and more friendly to projects with unbalanced complexity vectors.
 For example, kernel-level projects, boot layers, hardware drivers and other projects may involve a large amount of assembly code,corresponding to larger porting complexity,but other factors of the original tool design are at low values,which is not conducive to distinguishing complexity.
@@
 Within evaluation, there are instances of inaccurate predictions.
-Analysis of some variations reveals that certain projects exhibit inherent complexity, entailing a substantial presence of architecture-specific code defined by Arch\_code.
-Nevertheless, the practical porting process benefits from an array of auxiliary tools designed to support developers.
-In response to valuable suggestions from developers within the OpenEuler community, we conducted an evaluation of the porting complexity for various versions of the Chromium.Initially, we were able to accurately assess the porting complexity, yielding promising results.
-However, when it came to evaluating the work involved in iterative updates between versions, existing tools proved insufficient for precise estimation.Sometimes CPU architecture parts in projects are well separated from the common code,that just need only to adjust the moderate amount of code to recognize RISC-V,like nuttx.
+(1)In cgal project, developers believe that some functions or performance improvements are only worth the effort in scenarios where users need them, and cgal can be made to work properly with a small amount of modifications.Since our tool traverses the global code,and optional information cannot be identified.(2)In PortAudio project, the improved portability is attributed to the existence of equivalent C language implementations for the assembly code.
+This has a significant impact on our evaluation results because RAX can not recognize the semantic meaning of the code.(3)Developers believe that dlib project has implemented distribution versions of multiple architectures, and the porting experience reduces the difficulty of porting.(4)Sometimes CPU architecture parts in projects are well separated from the common code,that just need only to adjust the moderate amount of code to recognize RISC-V,like nuttx project.
 \section{Related Work}

### 2024-01-30 Paper/paper.tex
Add files via upload

--- 2024-01-29 Paper/latex1-27/paper.tex
@@
 RAX is a automated tool which aids the C/C++ programmer in evaluating  complexity of software during porting for RISC-V.RAX provides precise evaluation solutions and builds a high-quality dataset for porting complexity,enabling recommendations of suitable software with difficulty levels for developers of varying skill levels.We evaluate RAX on 72 popular and typical real-scenario C/C++ projects.
-The experimental result shows that 51 of them have been confirmed by developers within community.Interested users can explore the open-source implementation of RAX at \href{https://github.com/wangyuliu/RAX-2024}{https://github.com/wangyuliu/RAX-2024}, or watch the RAX video demo at \href{https://www.youtube.com/watch?v=SLphW3Ra4WM}{https://www.youtube.com/watch?v\\=SLphW3Ra4WM}.
+The experimental result shows that 51 of them have been confirmed by developers within community.Interested users can explore the open-source implementation of RAX at \href{https://github.com/wangyuliu/RAX-2024}{https://github.com/wangyuliu/RAX-2024}, or watch the RAX video demo at \href{https://youtu.be/g_e4VhG4kkM}{https://youtu.be/g_e4VhG4kkM}.
 \end{abstract}
@@
 First, we searched keywords "rv" or "riscv" and collected 139 projects as our training and testing dataset.
-Then, five postgraduate students are invited to tag the porting auxiliary for these projects.
+Then, five postgraduate students are invited to tag the porting complexity for these projects.
 The evaluation scores are divided into three categories:low, medium, and high\citep{githubss}.

### 2024-01-30 Paper/latex1-27/paper.tex
update

@@
 RAX is a automated tool which aids the C/C++ programmer in evaluating  complexity of software during porting for RISC-V.RAX provides precise evaluation solutions and builds a high-quality dataset for porting complexity,enabling recommendations of suitable software with difficulty levels for developers of varying skill levels.We evaluate RAX on 72 popular and typical real-scenario C/C++ projects.
-The experimental result shows that 51 of them have been confirmed by developers within community.Interested users can explore the open-source implementation of RAX at \href{https://github.com/wangyuliu/RAX-2024}{https://github.com/wangyuliu/RAX-2024}, or watch the RAX video demo at \href{https://www.youtube.com/watch?v=SLphW3Ra4WM}{https://www.youtube.com/watch?v\\=SLphW3Ra4WM}.
+The experimental result shows that 51 of them have been confirmed by developers within community.Interested users can explore the open-source implementation of RAX at \href{https://github.com/wangyuliu/RAX-2024}{https://github.com/wangyuliu/RAX-2024}, or watch the RAX video demo at \href{https://youtu.be/g\_e4VhG4kkM}{https://youtu.be/g\_e4VhG4kkM}.
 \end{abstract}
@@
     \toprule
-    & Full Assembly & Inline Assembly & Intrinsic & Builtin & System Call & CCM & Buildscripts & CC \\
+    & CC & Full Assembly & Inline Assembly & Intrinsic & Builtin & System Call & CCM & Buildscripts  \\
     \midrule
-   Tool\citep{2023du} & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \XSolidBrush \\
+   Tool\citep{2023du} & \XSolidBrush & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold  \\
     RAX & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold & \CheckmarkBold \\

### 2024-01-30 Paper/latex1-27/paper.tex
Add files via upload

@@
 \section{Introduction}
-RISC-V Instruction Set Architecture (ISA) has garnered significant attention from academia, and particularly the industry recently, due to its open-source and reduced design\citep{2014The}.Many distribution manufacturers are actively promoting the porting of the RISC-V, for example,OpenEuler has joined RISC-V International organization, and RISC-V has officially become openEuler's official support architecture.The main repository of openEuler 23.03 has successfully ported 4,244 software packages to the RISCV64,while the openEuler 23.09 main repository has currently completed the porting work of 5,694 software packages\citep{osti_1560132}.OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\citep{osti_1560133}.
+RISC-V Instruction Set Architecture (ISA) has garnered significant attention from academia, and particularly the industry recently, due to its open-source and reduced design\citep{2014The}.Many distribution manufacturers are actively promoting the porting of the RISC-V, for example,OpenEuler has joined RISC-V International organization, while the openEuler 23.09 main repository has currently completed the porting work of 5,694 software packages for RISCV64\citep{osti_1560132}.OpenCloudOS Kernel Stream 2207.2 kernel version adds support for the RISC-V 64 architecture\citep{osti_1560133}.
 
-Despite the rapid development of the RISC-V ISA, which foundational software such as operating systems and compilers are relatively mature, there is still a significant demand for porting a large number of application software\citep{2019Notary}.To adapt to the RISC-V,efficiently porting is greatly depending on prior knowledge of experts, and the lack of standardized evaluation criteria for software portability can lead to unreasonable development planning.Therefore, it is desirable to propose a method that automates the evaluation of porting complexity.This will enable different development teams to access software packages that are tailored to their abilities, thus assisting distribution vendors in the porting of RISC-V architecture.
+Despite the rapid development of the RISC-V ISA, which foundational software such as operating systems and compilers are relatively mature, there is still a significant demand for porting a large number of application software\citep{2019Notary}.To adapt to the RISC-V,efficiently porting is greatly depending on prior knowledge of experts, and the lack of standardized evaluation criteria for software portability can lead to unreasonable development planning.Even the developer is very familiar with the architectural code, it is impossible to accurately assess the overall workload.Therefore, it is desirable to propose a method that automates the evaluation of porting complexity.This will enable different development teams to access software packages that are tailored to their abilities, thus assisting distribution vendors in the porting of RISC-V architecture.
 
-Many related works focus on the code complexity and portability evaluation,but studies for CPU architectures are currently lacking in these areas\cite{2016helei},\cite{TAHIR2016101},\cite{Sholiq_2021}.Du et al.
+Many related works focus on the code complexity and portability evaluation,but studies for CPU architectures are currently lacking in these areas\cite{2016helei}\cite{TAHIR2016101}\cite{Sholiq_2021}.However,code complexity metrics such as Cyclomatic Complexity are important measurements for software development and maintenance.Du et al.
 have developed a basic statistical evaluation plan for CPU architecture code\citep{2023du}.However,their work lacks a thorough validity analysis of factors,and may not consider the complexity factors associated with the software operation and maintenance process.
 To overcome these challenges, we propose RAX, an effective porting
-complexity evaluation tool which accurately locates the CPU architecture code and calculates the code complexity of the software.The contributions of this paper are as follows:
+complexity evaluation tool which accurately locates the CPU architecture code and calculates the code complexity of the software.The contributions are as follows:
 \begin{figure}
@@
 \begin{table}
-  \caption{Tool Effectiveness Comparison from Community Feedback}
+  \caption{Tool Effectiveness Comparison Based on Feedback}
   \label{tab:effectiveness}
@@
 Within evaluation, there are instances of inaccurate predictions.
-(1)In cgal project, developers believe that some functions or performance improvements are only worth the effort in scenarios where users need them, and cgal can be made to work properly with a small amount of modifications.Since our tool traverses the global code,and optional information cannot be identified.(2)In PortAudio project, the improved portability is attributed to the existence of equivalent C language implementations for the assembly code.
-This has a significant impact on our evaluation results because RAX can not recognize the semantic meaning of the code.(3)Developers believe that dlib project has implemented distribution versions of multiple architectures, and the porting experience reduces the difficulty of porting.(4)Sometimes CPU architecture parts in projects are well separated from the common code,that just need only to adjust the moderate amount of code to recognize RISC-V,like nuttx project.
+(1)In \href{https://github.com/CGAL/cgal}{cgal project}, developers believe that some functions or performance improvements are only worth the effort in scenarios where users need them, and cgal can be made to work properly with a small amount of modifications.Since our tool traverses the global code,and optional information cannot be identified.(2)In \href{https://github.com/PortAudio/portaudio}{PortAudio project}, the improved portability is attributed to the existence of equivalent C language implementations for the assembly code.
+This has a significant impact on our evaluation results because RAX can not recognize the semantic meaning of the code.(3)Developers believe that \href{https://github.com/davisking/dlib}{dlib project} has implemented distribution versions of multiple architectures, and the porting experience reduces the difficulty of porting.(4)Sometimes CPU architecture parts in projects are well separated from the common code,that just need only to adjust the moderate amount of code to recognize RISC-V,like \href{https://github.com/apache/nuttx}{nuttx project}.
 \section{Related Work}
@@
 Vard et al. \cite{2017Evaluating} emphasized that the internal quality of software impacts developers' capabilities and maintenance duration.
-They conducted a comprehensive study on various existing code complexity metrics' validity and suggested incorporating empirically observed code features as complexity triggers.We have pioneered the application of code complexity metrics in the domain of porting assessment, while existing research primarily focuses on code refactoring and defect detection\cite{1993Software},\cite{1991Cyclomatic}.
+They conducted a comprehensive study on various existing code complexity metrics' validity and suggested incorporating empirically observed code features as complexity triggers.We have pioneered the application of code complexity metrics in the domain of porting assessment, while existing research primarily focuses on code refactoring and defect detection\cite{1993Software}\cite{1991Cyclomatic}.
 \section{Conclusion}
